---
title: "Growth rates in A. cervicornis under elevated N and N+P and subsequent heat stress"
author: "Ana Palacio"
date: "Feb 13, 2020"
output:
  html_document:
    fig_height: 3.5
    fig_width: 6
    df_print: paged
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

# 1. General project set-up 

```{r libraries, results="hide"}

# Load all libraries and sources required to run the script
    library(tidyverse)
    library(ggthemes)
    library(lmerTest)
    library(emmeans)
    library(multcomp)
    library(gridExtra)
    library(rstatix)

# Default ggplot settings

    Fill.colour<-scale_colour_manual(values = c ("#4A6CAA", "#469B53", "#AA4A74"))

    ggthe_bw<-theme_bw() + theme(panel.grid.major = element_blank(), 
                    panel.grid.minor = element_blank(),
                    #panel.background = element_blank(), 
                    axis.line = element_line(colour = "black"),
                    plot.background=element_blank(),
                    legend.title = element_blank(), 
                    legend.box.background = element_rect(),
                    panel.background =element_rect(fill = NA, color = "white"),
                    legend.position=c(0.2, 0.5),
                    strip.background =element_rect(fill=NA))
```

# 2. Import and clean growth data

```{r}
# Import data: 

  ## Growth long
    BW.Tall<-read.csv("Growth_corrected.csv", header = TRUE)
    
  ## Genotype information
    MOTE<-read.csv("Genotype_Info.csv", header = TRUE)
    BW.Tall<-merge(BW.Tall, MOTE, by="Gen", all.x=TRUE)
    
  ## Data type  
    BW.Tall$Initial.Date<-as.Date(BW.Tall$Initial.Date, "%m/%d/%y")
    BW.Tall$Final.Date<-as.Date(BW.Tall$Final.Date, "%m/%d/%y")
    BW.Tall$Days<-(as.numeric(as.Date(BW.Tall$Final.Date))-17485)
    BW.Tall$DayF<-(as.factor(BW.Tall$Days))
 
    BW.Tall$TimePoint[BW.Tall$DayF=="-28"]<-"1"
    BW.Tall$TimePoint[BW.Tall$DayF=="-7"]<-"NA"
    BW.Tall$TimePoint[BW.Tall$DayF=="28"]<-"2"
    BW.Tall$TimePoint[BW.Tall$DayF=="62"]<-"3"
    BW.Tall$TimePoint[BW.Tall$DayF=="75"]<-"4"
    BW.Tall$TimePoint[BW.Tall$DayF=="91"]<-"5"
    BW.Tall$TimePoint[BW.Tall$DayF=="100"]<-"6"
    BW.Tall$TimePoint[BW.Tall$DayF=="113"]<-"7"
    BW.Tall$TimePoint<-as.numeric(as.character(BW.Tall$TimePoint))
    
    
    BW.Tall$Treatment <- as.character(BW.Tall$Treatment)
    BW.Tall$Treatment[BW.Tall$Treatment == "Control"] <- "Ambient"
    BW.Tall$Treatment[BW.Tall$Treatment == "N"] <- "NH4"
    BW.Tall$Treatment[BW.Tall$Treatment == "NP"] <- "NH4+PO4"
    BW.Tall$Treatment <- as.factor(BW.Tall$Treatment)
    
    BW.Tall$Nutrients <- "Nutrients"
    BW.Tall$Nutrients[BW.Tall$Treatment == "Ambient"] <- "Ambient"
    
    BW.Tall$Colony <- as.factor(BW.Tall$Gen)
    BW.Tall$MoteGen<-factor(BW.Tall$MoteGen, 
                                   levels=c("G_48", "G_62","G_31", "G_08","G_07", "G_50"))
    BW.Tall$SampleID <- paste("Ac", BW.Tall$Fra, BW.Tall$TimePoint, sep = "_")
  
    
  ## Remove recovery data points
    BW.Tall<-subset(BW.Tall, Initial.Date!="2017-10-18")
    BW.Tall<-subset(BW.Tall, Initial.Date!="2018-02-23") # After heat stress
    
```

```{r}

 N.fragments<-BW.Tall %>% 
     group_by(MoteGen) %>% count(DayF)
 N.fragments
```


# 3. Growth over time (control, ramp-up and heat stress phases) by nutrient treatment

## Figure 3a

```{r, fig.height=3.5, fig.width=3.5}

# Treatment effect over time
    BW_Treat<- ggplot(BW.Tall, aes (Days, dAW.gd, fill=Treatment, shape=factor(Treatment))) + 
      scale_shape_manual(values=c(21, 22, 24), labels=c("Ambient", "NH4", "NH4+PO4"))+
      ggthe_bw + Fill.colour + ggtitle("a")+
  
      stat_summary(fun.data = "mean_cl_boot", geom = "errorbar",
                   position=position_dodge(width=5))+
      stat_summary(fun.y=mean, geom="line", 
                   position=position_dodge(width=5), linetype=1) +
      stat_summary(fun.y=mean, geom="point", size =2,  alpha=0.8,
                   position=position_dodge(width=5))  + 
  
      scale_x_continuous(name="Days in the experiment", 
                         breaks = seq(-30, 115, by=15)) +
      scale_y_continuous(name="Growth (mg  g-1 d-1)", 
                         breaks = seq(-1, 4, by=1)) +
  
      annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
                colour = "gray35")+
      annotate("text", x = -16, y = -1.2, label = "Baseline", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray35", linetype="dashed")+
      annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 91, y = -1.4, yend = 3.5,
                colour = "gray35", linetype="dotted")+
    
      annotate("segment", x = 91, xend = 110, y = 3.5, yend = 3.5,
                colour = "gray35", linetype="dotted")+
      annotate("text", x = 99, y = -1.2, label = "Heat", size=3)
  BW_Treat
  
# ggsave(file="Outputs/Figure3_BW_corrected.svg", plot=BW_Treat, dpi = 300, units="in", width=3.5, height=3.0)
```

## Figure 3b

```{r, echo =FALSE}

BW.Tall$TreatmentG<-BW.Tall$Treatment
BW.Tall$TreatmentG[BW.Tall$DayF==-28] <-"Ambient"

Colour.colour<-scale_colour_manual(values = c ("#4A6CAA", "#469B53", "#AA4A74"))
Fill.colour<-scale_fill_manual(values = c ("#4A6CAA", "#469B53", "#AA4A74"))

BW_Col <- ggplot(BW.Tall, aes(Days, dAW.gd, fill=Treatment,
                              shape=factor(Treatment))) +
  
     annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
                colour = "gray35")+
      # annotate("text", x = -16, y = -1.2, label = "BL", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray35", linetype="dashed")+
      # annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 91, y = -1.4, yend = 4.5,
                colour = "gray35", linetype="dotted")+
    
      annotate("segment", x = 91, xend = 110, y = 4.5, yend = 4.5,
                colour = "gray35",  linetype="dotted")+
      # annotate("text", x = 99, y = 3.5, label = "H", size=4)+
  
           stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                        position=position_dodge(width=5), width = 10)+
           stat_summary(fun.y=mean, geom="point", size =2,
                        position=position_dodge(width=5), alpha=0.8) +
           stat_summary(fun.y=mean, geom="line", 
                        position=position_dodge(width=5), linetype=1) + 
    scale_shape_manual(values=c(21, 22, 24),
                     labels=c("Ambient", "NH4", "NH4+PO4"))+
    ggthe_bw + Colour.colour + Fill.colour + ggtitle("b") +
    scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(-30, 113, 30),  
                           expand = c(0, 0))+
    scale_y_continuous(name=" ", 
                      breaks = seq(-1, 5, by=1)) +
   #geom_hline(yintercept = 0, linetype=3)+
  
    theme(legend.position="none",
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +

     facet_wrap(~MoteGen)
BW_Col

#ggsave(file="Outputs/S2a_Growth_genotype.svg", plot=BW_Col, width=6.0, height=3.5)

```

## Figure 3

```{r}
Figure.3<-grid.arrange(BW_Treat, BW_Col,
          ncol = 2,  widths = c(1.5,2))
#ggsave(file="Outputs/Figure3.svg", plot=Figure.3, width=6.5, height=4.5)
```


## Figure S2a: All genotypes by nutrient treatment over time (differrence)

```{r}

# Claculate relative changes (1 - Control)
      
BW.Tall$Nutrients2<-BW.Tall$Nutrients
BW.Tall$Nutrients2[BW.Tall$DayF=="-28"]<-"Ambient"
          
    BW.Summary <-BW.Tall %>%
          group_by(MoteGen, Nutrients2, DayF) %>%
          get_summary_stats(dAW.gd, type = "mean_sd")
    BW.Summary
    
    BW.Summary<-subset(BW.Summary, Nutrients2=="Ambient" )
    BW.Summary<-BW.Summary[, -3]
    BW.Summary<-BW.Summary[, -3]
    BW.Summary<-BW.Summary[, -3]
    
    BW.Tall<-merge(BW.Tall, BW.Summary,  by=c("MoteGen", "DayF"), all.x = T)
    BW.Tall$Difference<-BW.Tall$dAW.gd-BW.Tall$mean
    

Colour.colour<-scale_colour_manual(values = c("black", "gray70"))
Fill.colour<-scale_fill_manual(values = c("black", "gray70"))

BW_Diff_Col <- ggplot(BW.Tall, aes(Days, Difference, fill=Nutrients2,
                              shape=factor(Nutrients2))) +
  
     #annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
      #          colour = "gray90")+
      # annotate("text", x = -16, y = -1.2, label = "BL", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -3.5, yend = -3.5,
                colour = "gray90")+
       annotate("text", x = 45, y = -3.9, label = "Nutrients", size=4, colour="gray")+
    
      annotate("segment", x = 79, xend = 91, y = -3.5, yend = 1,
                colour = "gray90")+
    
      annotate("segment", x = 91, xend = 110, y =1, yend =1,
                colour = "gray90")+
       annotate("text", x = 99, y = 0.8, label = "H", size=4, colour="gray")+
  
           stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                        position=position_dodge(width=5), width = 10)+
           stat_summary(fun.y=mean, geom="point", size =2,
                        position=position_dodge(width=5), alpha=0.8) +
           stat_summary(fun.y=mean, geom="line", 
                        position=position_dodge(width=5), linetype=1) + 
    scale_shape_manual(values=c(21, 14),
                     labels=c("A", "N and N+P"))+
           ggthe_bw + Colour.colour + Fill.colour +
    scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(0, 113, 30),  
                           expand = c(0, 0))+
    scale_y_continuous(name="Difference in growth (mg/ g d) respecto to Ambient", 
                         breaks = seq(-4, 1.5, by=1)) +
   geom_hline(yintercept = 0, linetype=3)+
  
    theme(text=element_text(size=14),
          legend.position=c(0.1, 0.2),
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +

     facet_wrap(~MoteGen)
BW_Diff_Col
        
#ggsave(file="Outputs/S_3_BW_Diff_Col.svg", plot=BW_Diff_Col, width=5.0, height=5)
          
```

* Percantages 

```{r}
# Claculate percentajes changes (1 - Control)
  BW.Tall$percentage<-(BW.Tall$Difference/BW.Tall$mean)*100
    

Colour.colour<-scale_colour_manual(values = c("black", "gray70"))
Fill.colour<-scale_fill_manual(values = c("black", "gray70"))

BW_perent_Col <- ggplot(BW.Tall, aes(Days, percentage, fill=Nutrients2,
                              shape=factor(Nutrients2))) +
  
     #annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
      #          colour = "gray90")+
      # annotate("text", x = -16, y = -1.2, label = "BL", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -140, yend = -140,
                colour = "gray90")+
       annotate("text", x = 45, y = -135, label = "Nutrients", size=4, colour="gray")+
    
      annotate("segment", x = 79, xend = 91, y = -139, yend = 28,
                colour = "gray90")+
    
      annotate("segment", x = 91, xend = 110, y =28, yend =28,
                colour = "gray90")+
       annotate("text", x = 99, y = 33, label = "H", size=4, colour="gray")+
  
           stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                        position=position_dodge(width=5), width = 10)+
           stat_summary(fun.y=mean, geom="point", size =2,
                        position=position_dodge(width=5), alpha=0.8) +
           stat_summary(fun.y=mean, geom="line", 
                        position=position_dodge(width=5), linetype=1) + 
    scale_shape_manual(values=c(21, 14),
                     labels=c("A", "N and N+P"))+
           ggthe_bw + Colour.colour + Fill.colour +
    scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(0, 113, 30),  
                           expand = c(0, 0))+
    scale_y_continuous(name="Percentage of growth change respecto to Ambient", 
                         breaks = seq(-140, 100, by=20)) +
   geom_hline(yintercept = 0, linetype=3)+
  
    theme(text=element_text(size=14),
          legend.position=c(0.1, 0.2),
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +

     facet_wrap(~MoteGen)
BW_perent_Col

#ggsave(file="Outputs/S_3_BW_Percentaje_Col.svg", plot=BW_perent_Col, width=5.0, height=5)

```


# Figure 3b: By genotype, but N and N+P pooled

```{r, echo =FALSE}

BW.Tall$Nutrients[BW.Tall$DayF==-28] <-"Ambient"

Colour.colour<-scale_colour_manual(values = c("black", "gray70"))
Fill.colour<-scale_fill_manual(values = c("black", "gray70"))

BW_Col <- ggplot(BW.Tall, aes(Days, dAW.gd, fill=Nutrients,
                              shape=factor(Nutrients))) +
  
     #annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
      #          colour = "gray90")+
      # annotate("text", x = -16, y = -1.2, label = "BL", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray90")+
      # annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 91, y = -1.4, yend = 4.5,
                colour = "gray90")+
    
      annotate("segment", x = 91, xend = 110, y = 4.5, yend = 4.5,
                colour = "gray90")+
      # annotate("text", x = 99, y = 3.5, label = "H", size=4)+
  
           stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                        position=position_dodge(width=5), width = 10)+
           stat_summary(fun.y=mean, geom="point", size =2,
                        position=position_dodge(width=5), alpha=0.8) +
           stat_summary(fun.y=mean, geom="line", 
                        position=position_dodge(width=5), linetype=1) + 
    scale_shape_manual(values=c(21, 14),
                     labels=c("A", "N+P"))+
           ggthe_bw + Colour.colour + Fill.colour +
  
    scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(0, 113, 30),  
                           expand = c(0, 0))+
    scale_y_continuous(name="Growth rate (mg / g d) ", 
                         breaks = seq(-1, 5, by=1)) +
   geom_hline(yintercept = 0, linetype=3)+
  
    ylab("Growth rate (mg/ g d) ") + 
    theme(text=element_text(size=14),
          legend.position="none",
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +

     facet_wrap(~MoteGen)
BW_Col

#ggsave(file="Outputs/S2a_Growth_genotype.svg", plot=BW_Col, width=6.0, height=3.5)

```

```{r}
# sample means
BW.nutrients1 <- aggregate(dAW.gd~Nutrients+Days+MoteGen, data=BW.Tall, mean, na.rm=TRUE)
          names(BW.nutrients1)[4] <- "mean"
      
# sample SDs
BW.nutrientssd1 <- aggregate(dAW.gd~Nutrients+Days+MoteGen, data=BW.Tall, sd, na.rm=TRUE)
          names(BW.nutrientssd1)[4] <- "sd"
          
          
# Collect the summary statistics in a dataframe
    BW.nutrients1<-merge(BW.nutrients1, BW.nutrientssd1)
    BW.nutrients1<-BW.nutrients1[order(BW.nutrients1$Days, BW.nutrients1$MoteGen),]
    BW.nutrients1
```

## Other figures 

### All genotypes (colour) by nutrient treatment over time

Compare individual genotypes inside each nutrient treatment
* Growth declined in G50, G07 and G08 in A, but increased in G48, G62 and G31

```{r}
BW_ColonyT<- ggplot(BW.Tall, aes (Days, dAW.gd, colour=MoteGen)) +   
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.8)+
  stat_summary(fun.y=mean, geom="point", size =2, alpha=0.5) +
   ylab("Growth (mg/ g d)") +
  
     annotate("segment", x = 2, xend = 91, y = -1, yend = -1,
                   colour = "gray90", linetype=1)+
     annotate("segment", x = 79, xend = 91, y = -1, yend = -0.5,
                   colour = "gray90", linetype=1)+
     annotate("segment", x = 91, xend = 110, y = -0.5, yend = -0.5,
                   colour = "gray90", linetype=1)+
     annotate("text", x = 45, y = -1.5, label = "Nutrients", size=3)+
     annotate("text", x = 99, y = -1.5, label = "H", size=3)+
  stat_summary(fun.y=mean, geom="line") + ggthe_bw + facet_grid (~Treatment)  
BW_ColonyT
```

### Compare individual fragments inside each nutrient treatment

```{R}
BW_ColonyTF<- ggplot(BW.Tall, aes (Days, dAW.gd, colour=factor(Fra), group=Fra)) +    stat_summary(fun.y=mean, geom="line") + ggthe_bw + facet_grid (MoteGen~Treatment)+  geom_point()+ theme(legend.position = "none")
BW_ColonyTF

```

### Initial performance vs ambient per genotype: some genotypes declined in growth even without nutrients

```{r, , fig.height=4, fig.width=6}

BW_Init<- ggplot(BW.Initial, aes (MoteGen, dAW.gd, colour=MoteGen)) +
  ggtitle("(a) Baseline")+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2) +
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) + ggthe_bw +
  scale_y_continuous(name=("Growth (mg/ g d) "),
                     limits = c(0,6),
                     breaks = seq(0, 6, by=0.5))+
  theme(legend.position=c(0.3, 0.3),
        legend.title = element_blank(), 
        strip.background =element_rect(fill=NA))

BW_Final<- ggplot(BW.FinalAC, aes (MoteGen, dAW.gd, colour=MoteGen)) +
   ggtitle("(a) Ambient (day 75)")+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2) +
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) + ggthe_bw +
  scale_y_continuous(name=("Growth (mg/ g d) "),
                     limits = c(0,6),
                     breaks = seq(0, 6, by=0.5))+
   ylab("Growth (mg/ g d) ")+
  theme(legend.position="none",
        legend.title = element_blank(), 
        strip.background =element_rect(fill=NA))

BW_Colony_Control<- ggplot(BW.Control, aes (Days, dAW.gd, colour=MoteGen)) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               width = 10, position=position_dodge(width=5)) +
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5,
               position=position_dodge(width=5)) +
  stat_summary(fun.y=mean, geom="line", position=position_dodge(width=5)) +
  
  ggthe_bw + # geom_jitter()+
  ggtitle("(b) Ambient - Control") +
  scale_y_continuous(name=("Growth (mg/ g d) "),
                     limits = c(0,6),
                     breaks = seq(0, 6, by=0.5))+
  theme(legend.position="none")


Captivityeffect<-grid.arrange(BW_Init,BW_Final, nrow=1)
Captivityeffect2<-grid.arrange(BW_Init,BW_Colony_Control, nrow=1)
#ggsave(file="Outputs/S_Genotypes.svg", plot=Captivityeffect, width=6, height=3.5)

```

```{r}
BW_Colony_Control<-ggplot(BW.Control, aes (Days, dAW.gd, colour=factor(Fra), group=Fra)) +   
  #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.8)+
  #stat_summary(fun.y=mean, geom="point", size =2, alpha=0.5) +
  stat_summary(fun.y=mean, geom="line") + ggthe_bw + 
  facet_wrap (~MoteGen)+  geom_point()+ theme(legend.position = "none")
BW_Colony_Control
```


# LMER model selection and pairwise comparisons

## Treatment 

### LMER4

```{r}
# Complex to simple models 
  
  LM_1 <- lmer(dAW.gd ~ Treatment*DayF +
                               (1 + Treatment|Genotype) + (1|Replicate), REML=TRUE, data= BW.Tall)
  
  LM_2 <- lmer(dAW.gd ~ Treatment * DayF +
                               (Treatment|Genotype), REML=TRUE,  data= BW.Tall)
   
  LM_3 <- lmer(dAW.gd ~ Treatment  * DayF +
                               (1|Genotype), REML=TRUE, data= BW.Tall)
 

# Select model
  AIC(LM_1, LM_2, LM_3) # 1=2, but 3 has lower AIC
  
  anova(LM_1, LM_2, refit=FALSE)
  anova(LM_2, LM_3, refit=FALSE)
  anova(LM_1, LM_3, refit=FALSE)
 
# Final model 
  LM_Treatment_Days<-lmer(dAW.gd ~ Treatment * DayF +
                             (1|Genotype) + (1|Fra),  data= BW.Tall) 
  # Removed (1|Replicate) since it was not significant (p=0.1642)
  isSingular(LM_Treatment_Days)
  
  anova(LM_Treatment_Days)
  ranova(LM_Treatment_Days)
  #summary(LM_Treatment_Days)

par(mfrow=c(1,2))
  plot(fitted(LM_Treatment_Days), residuals(LM_Treatment_Days, type="pearson"))
  abline(h=0)
  qqnorm(residuals(LM_Treatment_Days, type="pearson"))
abline(0,1)
  
# Pairwise comparisons
  BW.emmc<-emmeans(LM_Treatment_Days, ~Treatment*DayF)
  #contrast(BW.emmc, "tukey")
  BW_groups<-cld(BW.emmc)
  #BW.emmc<-emmeans(LM_Treatment_Days, ~Treatment|DayF)
  #contrast(BW.emmc, "tukey")
  #BW_groups<-cld(BW.emmc)
  
  #BW_groups<-as.data.frame(BW_groups[complete.cases(BW_groups),])
  BW_groups<-BW_groups[order(BW_groups$DayF,BW_groups$Treatment),]
  BW_groups
  
#write.csv(BW_groups, "Outputs/BW_groups_corrected.csv", row.names = F)

```

### nlme

```{r}
#library(nlme)
# 
# fit1 <- gls(dAW.gd ~ DayF *Treatment, data=BW.Tall,
#   correlation=corSymm(form=~TimePoint|Fra),
#   weights=varIdent(form=~1|TimePoint),
#   na.action=na.exclude,
#   control=glsControl(opt="optim"))
```

Only Ambient summary model 

```{r}
# summary(fit1)
# 
# intervals(fit1)
# anova(fit1, type="marginal")
# getVarCov(fit1)
# residuals(fit1, type="pearson")
# 
# par(mfrow=c(1,2))
# plot(fitted(fit1), residuals(fit1, type="pearson"))
# abline(h=0)
# qqnorm(residuals(fit1, type="pearson"))
# abline(0,1)
```

Predictions 

```{r}
# library(rms)
# clda_Gls_1 <- Gls(dAW.gd ~ DayF * Treatment, 
#                   correlation=corSymm (form = ~TimePoint|Fra),
#         weights=varIdent(form=~1|TimePoint),
#         na.action=na.exclude,
#         control=glsControl(opt="optim"),
#         data=BW.Tall)
# 
# data1<-expand.grid(DayF=unique(BW.Tall$DayF),
#                    Treatment=unique(BW.Tall$Treatment))
# 
# predictions_1 <- cbind(data1, 
# predict (clda_Gls_1, data1, conf.int=0.95))
# 
# predictions_1$Days<-as.numeric(as.character(predictions_1$DayF))

```

Model prediction by treatment

```{r}
# pd <- position_dodge(2)
# limits <- aes(ymax = upper , ymin=lower, shape=Treatment)
# 
# pCI1 <- ggplot(predictions_1, aes(y=linear.predictors, x=Days, 
#                                 fill=Treatment)) + 
#       geom_errorbar(limits, width= 2 , position=pd) + 
#       geom_line(aes(group=Treatment, y=linear.predictors), position=pd, size=0.1) + 
#       geom_point(aes(fill=Treatment), shape=21, position=pd, size=4, alpha=0.8) +
#         
#       ggthe_bw+
#         
#       geom_hline(yintercept = 0, linetype=3)+
#       
#       scale_x_continuous(name="Days in the experiment", 
#                          breaks = seq(0, 115, by=15)) +
#       scale_y_continuous(name="Estimated growth (mg / g d) ", 
#                          breaks = seq(-1, 4, by=1)) +
#     
#       theme(text=element_text(size=14),
#           legend.position="right",
#           legend.title = element_blank(), 
#           strip.background =element_rect(fill=NA)) +
#     
#       annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
#                 colour = "gray90")+
#       annotate("text", x = -16, y = -1.2, label = "Baseline", size=3)+
#     
#       annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
#                 colour = "gray90")+
#       annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
#     
#       annotate("segment", x = 79, xend = 91, y = -1.4, yend = -1,
#                 colour = "gray90")+
#     
#       annotate("segment", x = 91, xend = 110, y = -1, yend = -1,
#                 colour = "gray90")+
#       annotate("text", x = 99, y = -1.2, label = "Heat", size=3)
#  
# pCI1
```

## Genets

### No nutrients

#### lmer4

* Baseline differences

```{r}
# ANOVA
  LM_bl <- lmer(dAW.gd ~ MoteGen + (1|Replicate), data= BW.Initial)
  anova(LM_bl)
  ranova(LM_bl)
  
    LM_bl <- lm(dAW.gd ~ MoteGen, data= BW.Initial)
    anova(LM_bl)
    summary(LM_bl)
  
# Pairwise comparisons
  BW_bl.emmc<-emmeans(LM_bl, ~MoteGen)
  #contrast(BW_bl.emmc, "tukey")
  
#Tukey groups
  BW_bl_groups<-cld(BW_bl.emmc)
  #write.csv(BW_bl_groups, "Outputs/BW_baseline_groups.csv", row.names = F)

# Summary stats
  # library(rstatix)
  
  Stats_BL<-BW.Initial %>%
    group_by(MoteGen) %>%
    get_summary_stats(dAW.gd, type = "mean_sd")
  Stats_BL

```

* Ambient and Control evolution

```{r}
summary(BW.Control)

# Model
  LM_A_C.0 <- lmer(dAW.gd ~ MoteGen * DayF + (1|Replicate), data= BW.Control)
  anova(LM_A_C.0) # Day alone is not significant, but Day:Genet is 
  ranova(LM_A_C.0) # Replicate is not significant

  LM_A_C <-lmer(dAW.gd ~ MoteGen * DayF + (1|Fra), data= BW.Control)
  anova(LM_A_C) # Day alone is not significant, but Day:Genet is 
  ranova(LM_A_C)
  
# Pairwise comparisons
  BW_A_C.emmc<-emmeans(LM_A_C, ~MoteGen | DayF)
  #contrast(BW_A_C.emmc, "tukey")
  
  #BW_A_C.emmc<-emmeans(LM_A_C, ~DayF|MoteGen)
  #contrast(BW_A_C.emmc, "tukey")
  
#Tukey groups
  BW_A_C_groups<-cld(BW_A_C.emmc)
  
  BW_A_C_groups<-BW_A_C_groups[order(BW_A_C_groups$MoteGen,BW_A_C_groups$Day),]
  BW_A_C_groups
  
  #write.csv(BW_A_C_groups, "Outputs/BW_A_C_groups.csv", row.names = F)

# Summary stats
  # library(rstatix)
  
  Stats_Control<-BW.Control %>%
    group_by(MoteGen) %>%
    get_summary_stats(dAW.gd, type = "mean_sd")
  Stats_Control

```

* Ambient final day

```{r}
summary(BW.FinalAC)

# Model
  LM_A_C.75 <- lmer(dAW.gd ~ MoteGen + (1|Replicate), data= BW.FinalAC)
  isSingular(LM_A_C.75)
  anova(LM_A_C.75) # Day alone is not significant, but Day:Genet is 
  ranova(LM_A_C.75) # Replicate is not significant

  LM_A_C.75 <-lm(dAW.gd ~ MoteGen , data=BW.FinalAC)
  anova(LM_A_C.75) # Day alone is not significant, but Day:Genet is 
  summary(LM_A_C.75)
  
# Pairwise comparisons
  BW_A_C75.emmc<-emmeans(LM_A_C.75, ~MoteGen)
  #contrast(BW_A_C.emmc, "tukey")
  
#Tukey groups
  BW_A_C75_groups<-cld(BW_A_C75.emmc)
  BW_A_C75_groups
  #write.csv(BW_A_C75_groups, "Outputs/BW_A_C75_groups.csv", row.names = F)

  Stats_75_a<-BW.FinalAC %>%
    group_by(MoteGen) %>%
    get_summary_stats(dAW.gd, type = "mean_sd")
  Stats_75_a
```


* Baseline + Ambient-Control overtime 

```{r}
BW.AC<-subset(BW.Tall, Days<80)
  BW.AC$Treatment[BW.AC$DayF=="-28"]<-"A"
  BW.AC<-subset(BW.AC, Treatment=="A") # Only Ambient
  BW.AC<-droplevels(BW.AC)

  Stats_Con_BL<-BW.AC %>%
    group_by(MoteGen, DayF) %>%
    get_summary_stats(dAW.gd, type = "mean_sd")
  Stats_Con_BL

  summary(BW.AC)

# Model
  LM_AC_BL <- lmer(dAW.gd ~ MoteGen * DayF + (1|Replicate), data= BW.AC)
  isSingular(LM_AC_BL)
  anova(LM_AC_BL) # Day alone is not significant, but Day:Genet is 
  ranova(LM_AC_BL) # Replicate is not significant

  LM_AC_BL <-lmer(dAW.gd ~ MoteGen * DayF + (1|Fra), data= BW.AC)
  anova(LM_AC_BL) # Day alone is not significant, but Day:Genet is 
  ranova(LM_AC_BL)
  
# Pairwise comparisons
  BW_AC_BL.emmc<-emmeans(LM_AC_BL, ~MoteGen | DayF)
  #contrast(BW_AC_BL.emmc, "tukey")
  
  BW_AC_BL.emmc<-emmeans(LM_AC_BL, ~DayF|MoteGen)
  #contrast(BW_AC_BL.emmc, "tukey")
  
#Tukey groups
  BW_AC_BL.emmc<-emmeans(LM_AC_BL, ~MoteGen * DayF)
  BW_AC_BL_groups<-cld(BW_AC_BL.emmc)
  
  BW_AC_BL_groups<-BW_AC_BL_groups[order(BW_AC_BL_groups$DayF,BW_AC_BL_groups$MoteGen),]
  BW_AC_BL_groups
  
  #write.csv(BW_AC_BL_groups, "Outputs/BW_AC_BL_groups", row.names = F)

```

* Ambient heat stress (day 100)

```{r}

summary(BW.100)

BW.100.C<-subset(BW.100, Treatment=="A")
summary(BW.100.C)

# Model
  LM_A_H.100 <- lmer(dAW.gd ~ MoteGen + (1|Replicate), data= BW.100.C)
  anova(LM_A_H.100) 
  ranova(LM_A_H.100) # Replicate is not significant

# Pairwise comparisons
  BW_A_H100.emmc<-emmeans(LM_A_H.100, ~MoteGen)
  #contrast(BW_A_H100.emmc, "tukey")
  
#Tukey groups
  BW_A_H100_groups<-cld(BW_A_H100.emmc)
  BW_A_H100_groups
  #write.csv(BW_A_H100_groups, "Outputs/BW_A_H100_groups.csv", row.names = F)

  Stats_100_a<-BW.100.C %>%
    group_by(MoteGen) %>%
    get_summary_stats(dAW.gd, type = "mean_sd")
  Stats_100_a
  
```

```{r}
  
BW_91<- ggplot(subset(BW.91, Treatment=="A"), aes (MoteGen, dAW.gd, colour=MoteGen)) +
  ggtitle("(c) Heat (day 91)")+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2) +
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) + ggthe_bw +
  scale_y_continuous(name=("Growth (mg/ g d) "),
                     limits = c(0,6),
                     breaks = seq(0, 6, by=0.5))+
  theme(legend.position="none",
        legend.title = element_blank(), 
        strip.background =element_rect(fill=NA)) #+
  facet_grid(Treatment~.)


BW_100<- ggplot(subset(BW.100, Treatment=="A"), aes (MoteGen, dAW.gd, colour=MoteGen)) +
  ggtitle("(d) Heat (day 100)")+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2) +
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) + ggthe_bw +
  scale_y_continuous(name=("Growth (mg/ g d) "),
                     limits = c(0,6),
                     breaks = seq(0, 6, by=0.5))+
  theme(legend.position="none",
        legend.title = element_blank(), 
        strip.background =element_rect(fill=NA)) #+facet_grid(Treatment~.)

HeatEffect<-grid.arrange(BW_91, BW_100, nrow=1)

```

## Figure S2

```{r}
All_ambient<-grid.arrange(BW_Init,BW_Final, BW_91, BW_100, nrow=1)

#ggsave(file="Outputs/S_Genotypes_Ambient.svg", plot=All_ambient, width=8, height=5.5)
```

* Selected timepoints = BL + Ambient 75 (Control) and 100 (Heat) 

```{r}

# Subset_data
  BW.A<-BW.Tall
    BW.A$Treatment[BW.A$DayF=="-28"]<-"A"
    BW.A<-subset(BW.A, Treatment=="A")  
    BW.A<-subset(BW.A, DayF!="28")
    BW.A<-subset(BW.A, DayF!="62")  
    # BW.A<-subset(BW.A, DayF!="91")
    BW.A<-droplevels(BW.A)

# Summary    
  summary(BW.A)
  
  Stats_Ambient<-BW.A %>%
    group_by(MoteGen, DayF) %>%
    get_summary_stats(dAW.gd, type = "mean_sd")
  Stats_Ambient
  
# Model
  LM_Ambinet <- lmer(dAW.gd ~ MoteGen * DayF + (1|Replicate), data= BW.A)
  isSingular(LM_Ambinet)
  anova(LM_Ambinet) 
  ranova(LM_Ambinet) # Replicate is not significant

  LM_Ambinet <-lmer(dAW.gd ~ MoteGen * DayF + (1|Fra), data= BW.A)
  anova(LM_Ambinet) # Day alone is not significant, but Day:Genet is 
  ranova(LM_Ambinet)
  
# Pairwise comparisons
  BW_Ambient.emmc<-emmeans(LM_Ambinet, ~MoteGen | DayF)
  #contrast(BW_Ambient.emmc, "tukey")
  
  BW_Ambient.emmc<-emmeans(LM_Ambinet, ~DayF|MoteGen)
  #contrast(BW_Ambient.emmc, "tukey")
  
#Tukey groups
  BW_AC_BL.emmc<-emmeans(LM_Ambinet, ~MoteGen * DayF)
  BW_AC_BL_groups<-cld(BW_AC_BL.emmc)
  
  BW_AC_BL_groups<-BW_AC_BL_groups[
    order(BW_AC_BL_groups$DayF,BW_AC_BL_groups$MoteGen),]
  BW_AC_BL_groups
  
  #write.csv(BW_AC_BL_groups, "Outputs/BW_AC_BL_groups", row.names = F)

```


## Treatment and genets

### Control all treatments

```{r}
# 1. Model
  
  LM_4 <- lmer(dAW.gd ~ Treatment*DayF*MoteGen +
                       (1|Fra), REML=TRUE, data=BW.nutrients)

# Select model  
  anova(LM_4)  
  ranova(LM_4)

# 2. Predict values:
  pred_nutrients <- predict(LM_4,re.form = NA)

  #3. Bootstrap CI:
    nutrients.boot1 <- bootMer(LM_4, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(nutrients.boot1$t, 2, sd)
    CI.lo_1 <- pred_nutrients - std.err*1.96
    CI.hi_1 <- pred_nutrients + std.err*1.96

  #Plot
  Model_nutrinets_plot<- ggplot(
    BW.nutrients, aes(x = Days, y = dAW.gd, colour = MoteGen)) +
    geom_line(aes(y = pred_nutrients),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_1, ymax = CI.hi_1),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    scale_y_continuous(name=expression(~italic("Growth")),
                      limits = c(0, 6), 
                      breaks = seq(0, 6, by=1), expand = c(0,0))+
    scale_x_continuous("Days in the experiment", limits = c(-30, 78),
                     breaks = seq(-30, 76, by=15), expand = c(0,0))+
    
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="line", position = position_dodge(1), 
                linetype=1, alpha=0.5) + ggthe_bw
    
  
  Model_nutrinets_plot + facet_grid(~Treatment)
  
# Pairwise comparisons
  BW.emmc<-emmeans(LM_4, ~Treatment|DayF|MoteGen)
  contrast(BW.emmc, "tukey")
  BW_groups<-cld(BW.emmc)
  
  #BW_groups<-as.data.frame(BW_groups[complete.cases(BW_groups),])
  BW_groups<-BW_groups[order(BW_groups$Day,BW_groups$Treatment),]
  BW_groups
  
  #write.csv(BW_groups, "Outputs/BW_groups_corrected.csv", row.names = F)

```

## Pooled N and N+P during Control

```{r}

BW.Tall$Nutrients <- "Nutrients"
BW.Tall$Nutrients[BW.Tall$Treatment == "A"] <- "Ambient"
BW.Nutrients<-subset(BW.Tall, Days<91)
   
# 1. Model
  
  LM_5 <- lmer(dAW.gd ~ Nutrients*DayF*MoteGen +
                       (1|Fra), REML=TRUE, data=BW.Nutrients)

# Select model  
  anova(LM_5)  
  ranova(LM_5)

# 2. Predict values:
  pred_nutrients2 <- predict(LM_5, re.form = NA)

  #3. Bootstrap CI:
    nutrients.boot2 <- bootMer(LM_5, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(nutrients.boot2$t, 2, sd)
    CI.lo_2 <- pred_nutrients2 - std.err*1.96
    CI.hi_2 <- pred_nutrients2 + std.err*1.96

  #Plot
  Model_nutrinets_plot2<- ggplot(BW.Nutrients, 
                                 aes(x = Days, y = dAW.gd, 
                                     colour = MoteGen, shape=Nutrients)) +
    geom_line(aes(y = pred_nutrients2),size=2) +
    #geom_point(aes(fill=factor(Nutrients)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_2, ymax = CI.hi_2),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    scale_y_continuous(name=expression(~italic("Growth")),
                      limits = c(-2, 6), 
                      breaks = seq(-2, 6, by=1), expand = c(0,0))+
    scale_x_continuous("Days in the experiment", limits = c(-30, 110),
                     breaks = seq(-30, 110, by=30), expand = c(0,0))+
    
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="line", position = position_dodge(1), 
                linetype=1, alpha=0.5) + ggthe_bw
    
  
  Model_nutrinets_plot2 + facet_grid(~Nutrients)
  
# Pairwise comparisons
  contrast(BW.emmc, "tukey")
  BW.emmc<-emmeans(LM_5, ~MoteGen|DayF|Nutrients)
  contrast(BW.emmc, "tukey")
  
  BW.emmc<-emmeans(LM_5, ~Nutrients|MoteGen|DayF)
  contrast(BW.emmc, "tukey")
  
  BW.emmc<-emmeans(LM_5, ~MoteGen*DayF*Nutrients)
  BW_groups_genotypes<-cld(BW.emmc)
  
  #BW_groups_genotypes<-as.data.frame(BW_groups_genotypes[complete.cases(BW_groups_genotypes),])
  BW_groups_genotypes<-BW_groups_genotypes[order(BW_groups_genotypes$MoteGen, 
                             BW_groups_genotypes$DayF,
                             BW_groups_genotypes$Nutrients),]
  BW_groups_genotypes
  
  #write.csv(BW_groups_genotypes, "Outputs/BW_groups_genotypes.csv", row.names = F)

```


```{r}

```



