---
title: "Growth rates in A. cervicornis by Genotypes"
author: "Ana Palacio"
date: "Feb 13, 2020"
output:
  html_document:
    fig_height: 3.5
    fig_width: 6
    df_print: paged
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

# 1. General project set-up 

```{r libraries, results="hide"}

# Load all libraries and sources required to run the script
    library(tidyverse)
    library(ggthemes)
    library(lmerTest)
    library(emmeans)
    library(multcomp)
    library(gridExtra)
    library(nlme)
    library(lattice)
    library(rms)
    library(rstatix)

# Default ggplot settings

 ggthe_bw<-theme_bw() + theme(panel.grid.major = element_blank(), 
                    panel.grid.minor = element_blank(),
                    #panel.background = element_blank(), 
                    axis.line = element_line(colour = "black"),
                    plot.background=element_blank(),
                    legend.title = element_blank(), 
                    legend.box.background = element_rect(),
                    panel.background =element_rect(fill = NA, color = "white"),
                    legend.position="bottom",
                    strip.background =element_rect(fill=NA))
```


# 2. Import and clean growth data

```{r}
# Import data: 

  ## Growth long
    BW.Tall<-read.csv("Growth_corrected.csv", header = TRUE)
    
  ## Genotype information
    MOTE<-read.csv("Genotype_Info.csv", header = TRUE)
    BW.Tall<-merge(BW.Tall, MOTE, by="Gen", all.x=TRUE)
    
  ## Data type  
    BW.Tall$Initial.Date<-as.Date(BW.Tall$Initial.Date, "%m/%d/%y")
    BW.Tall$Final.Date<-as.Date(BW.Tall$Final.Date, "%m/%d/%y")
    BW.Tall$Days<-(as.numeric(as.Date(BW.Tall$Final.Date))-17485)
    BW.Tall$DayF<-(as.factor(BW.Tall$Days))
    BW.Tall$DayF<-factor(BW.Tall$DayF, levels = c("-28", "28", "62", "75", "91", "100"))
   
    ## corSymm requires consecutive integers 
    BW.Tall$TimePoint[BW.Tall$DayF=="-28"]<-"1"
    #BW.Tall$TimePoint[BW.Tall$DayF=="-7"]<-"4"
    BW.Tall$TimePoint[BW.Tall$DayF=="28"]<-"2"
    BW.Tall$TimePoint[BW.Tall$DayF=="62"]<-"3"
    BW.Tall$TimePoint[BW.Tall$DayF=="75"]<-"4"
    BW.Tall$TimePoint[BW.Tall$DayF=="91"]<-"5"
    BW.Tall$TimePoint[BW.Tall$DayF=="100"]<-"6"
    BW.Tall$TimePoint[BW.Tall$DayF=="113"]<-"7"
    BW.Tall$TimePoint<-as.numeric(BW.Tall$TimePoint)

    BW.Tall$Treatment <- as.character(BW.Tall$Treatment)
    BW.Tall$Treatment[BW.Tall$Treatment == "Control"] <- "Ambient"
    BW.Tall$Treatment[BW.Tall$Treatment == "N"] <- "NH4"
    BW.Tall$Treatment[BW.Tall$Treatment == "NP"] <- "NH4+PO4"
    BW.Tall$Treatment <- as.factor(BW.Tall$Treatment)
    
    BW.Tall$Nutrients <- "Nutrients"
    BW.Tall$Nutrients[BW.Tall$Treatment == "Ambient"] <- "Ambient"
    BW.Tall$Nutrients<-as.factor(BW.Tall$Nutrients)
    
    BW.Tall$Nutrients2 <- BW.Tall$Nutrients
    BW.Tall$Nutrients2[BW.Tall$DayF == "-28"] <- "Ambient"
    BW.Tall$Nutrients2<-as.factor(BW.Tall$Nutrients2)
    
    BW.Tall$Fra <- as.factor(BW.Tall$Fra)
    
    #BW.Tall$Colony <- as.factor(BW.Tall$Gen)
    BW.Tall$MoteGen<-factor(BW.Tall$MoteGen, 
                                   levels=c("G_48", "G_62","G_31", "G_08","G_07", "G_50"))
    BW.Tall$SampleID <- paste("Ac", BW.Tall$Fra, BW.Tall$TimePoint, sep = "_")
  
  # Remove unused columns    
    BW.Tall$Gen<-NULL
    BW.Tall$Time <-NULL
    BW.Tall$Period<-NULL
    BW.Tall$Original.Collection.Date <-NULL
    BW.Tall$Collection.Habitat <-NULL
    BW.Tall$Lat <-NULL
    BW.Tall$Lon <-NULL
    BW.Tall$WBS <-NULL
    
  # Remove recovery data points
    BW.Tall<-subset(BW.Tall, Initial.Date!="2017-10-18")
    BW.Tall<-subset(BW.Tall, Initial.Date!="2018-02-23") # After heat stress
  
```

### Check Individual fragments behavior

Compare individual fragments inside each nutrient treatment

```{r}
BW_ColonyT<- ggplot(BW.Tall, aes (Days, dAW.gd, colour=MoteGen, group=(Fra))) +   
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.8)+
  stat_summary(fun.y=mean, geom="point", size =2, alpha=0.5) +
   ylab("Growth (mg/ g d)") +
  
     annotate("segment", x = 2, xend = 91, y = -1, yend = -1,
                   colour = "gray90", linetype=1)+
     annotate("segment", x = 79, xend = 91, y = -1, yend = -0.5,
                   colour = "gray90", linetype=1)+
     annotate("segment", x = 91, xend = 110, y = -0.5, yend = -0.5,
                   colour = "gray90", linetype=1)+
     annotate("text", x = 45, y = -1.5, label = "Nutrients", size=3)+
     annotate("text", x = 99, y = -1.5, label = "H", size=3)+
  stat_summary(fun.y=mean, geom="line") + ggthe_bw + facet_grid (~Treatment)  
BW_ColonyT+ facet_grid(Treatment~MoteGen)
```

Fragments measured per time point and genotype 

```{r}
N.fragments<-BW.Tall %>% 
     group_by(MoteGen) %>% dplyr::count(DayF)
N.fragments

```

# 3. Nutrient treatment means overtime

## Figure 3a

```{r, fig.height=3.5, fig.width=3.5}

Fill.colour<-scale_fill_manual(values = c ("#4A6CAA", "#469B53", "#AA4A74"))

# Treatment effect over time

    BW_Treat<- ggplot(BW.Tall, aes (Days, dAW.gd, fill=Treatment, shape=factor(Treatment))) + Fill.colour+
      scale_shape_manual(values=c(21, 22, 24), 
                         labels=c("Ambient", "NH4", "NH4+PO4"))+
      ggthe_bw + ggtitle("a. overall growth by treatment \n")+
      
  
      stat_summary(fun.data = "mean_cl_boot", geom = "errorbar",
                   position=position_dodge(width=5))+
      stat_summary(fun.y=mean, geom="line", 
                   position=position_dodge(width=5), linetype=1) +
      stat_summary(fun.y=mean, geom="point", size =2,  alpha=0.8,
                   position=position_dodge(width=5))  + 
  
      scale_x_continuous(name="Days in the experiment", 
                         breaks = seq(-30, 115, by=15)) +
      scale_y_continuous(name=("Growth (mg g-1 d-1) "),
                           limits = c(-1.8,5),
                           breaks = seq(-1, 5, 1),  
                           expand = c(0, 0))+
  
      annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
                colour = "gray35")+
      annotate("text", x = -16, y = -1.2, label = "Baseline", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray35", linetype="dashed")+
      annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 91, y = -1.4, yend = 3.5,
                colour = "gray35", linetype="dotted")+
    
      annotate("segment", x = 91, xend = 110, y = 3.5, yend = 3.5,
                colour = "gray35", linetype="dotted")+
      annotate("text", x = 99, y = -1.2, label = "Heat", size=3)+
      theme(legend.position = c(0.2,0.25))
  BW_Treat
  
# ggsave(file="Outputs/Figure3_BW_ICRS.svg", plot=BW_Treat, dpi = 300, units="in", width=5, height=4)
```

## Model 1: Overall growth - genotype as random effect and all three nutrient levels

```{r}

# Linear model 
  Model_treatment<-lmer(dAW.gd~Treatment * DayF + (1|Genotype) + (1|Fra) + (1|Replicate),
                        data = BW.Tall)
  anova(Model_treatment)
  ranova(Model_treatment)
  #summary(Model_treatment)

# Pairwise comparisons
  # Day specific comparisons
  BW.emmc<-emmeans(Model_treatment, ~Treatment|DayF)
  BW_groups<-cld(BW.emmc)
  BW_groups
  
  # Across days (temperature) comparisons
  BW.emmc<-emmeans(Model_treatment, ~Treatment*DayF)
  BW_groups<-cld(BW.emmc)
  BW_groups<-BW_groups[order(BW_groups$DayF,BW_groups$Treatment),]
  BW_groups
```

## Summary by nutrient treatment and timepoint

```{r}
summary(BW.Tall)

# Sample means
BW.mean <- aggregate(dAW.gd~Treatment+Days, data=BW.Tall, mean, na.rm=TRUE)
          names(BW.mean)[3] <- "mean"
# sample SDs
BW.sd <- aggregate(dAW.gd~Treatment+Days, data=BW.Tall, sd, na.rm=TRUE)
          names(BW.sd)[3] <- "sd"
# Collect the summary statistics in a dataframe
BW.summaries <- merge(BW.mean, BW.sd)
print(BW.summaries, digits=3)
```

# 4 Genotypes

## 4.1 Genotypes and nutrient treatment means over time

### Figure S2

```{r, echo =FALSE}

BW.Tall$TreatmentG<-BW.Tall$Treatment
BW.Tall$TreatmentG[BW.Tall$DayF==-28] <-"Ambient"

Colour.colour<-scale_colour_manual(values = c ("#4A6CAA", "#469B53", "#AA4A74"))
Fill.colour<-scale_fill_manual(values = c ("#4A6CAA", "#469B53", "#AA4A74"))

BW_Col <- ggplot(BW.Tall, aes(Days, dAW.gd, fill=Treatment,
                              shape=factor(Treatment))) +
      
     annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
                colour = "gray35")+
      # annotate("text", x = -16, y = -1.2, label = "BL", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray35", linetype="dashed")+
      # annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 91, y = -1.4, yend = 5.5,
                colour = "gray35", linetype="dotted")+
    
      annotate("segment", x = 91, xend = 110, y = 5.5, yend = 5.5,
                colour = "gray35",  linetype="dotted")+
      # annotate("text", x = 99, y = 3.5, label = "H", size=4)+
  
           stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                        position=position_dodge(width=5), width = 10)+
           stat_summary(fun.y=mean, geom="point", size =2,
                        position=position_dodge(width=5), alpha=0.8) +
           stat_summary(fun.y=mean, geom="line", 
                        position=position_dodge(width=5), linetype=1) + 
    scale_shape_manual(values=c(21, 22, 24),
                     labels=c("Ambient", "NH4", "NH4+PO4"))+
    ggthe_bw + Colour.colour + Fill.colour+
    scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(-30, 113, 30),  
                           expand = c(0, 0))+
    scale_y_continuous(name="Growth (mg  g-1 d-1)", 
                      breaks = seq(-1, 5, by=1)) +
   #geom_hline(yintercept = 0, linetype=3)+
  theme(legend.position="bottom",
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +

  facet_wrap(~MoteGen)
BW_Col

#ggsave(file="Outputs/S2a_Growth_genotype.svg", plot=BW_Col, width=5.5, height=5)

```

### Summary by genotype, nutrient treatment, and time point

```{r}
# sample means
BW.mean1 <- aggregate(dAW.gd~Treatment+Days+MoteGen, data=BW.Tall, mean, na.rm=TRUE)
          names(BW.mean1)[4] <- "mean"
      
# sample SDs
BW.sd1 <- aggregate(dAW.gd~Treatment+Days+MoteGen, data=BW.Tall, sd, na.rm=TRUE)
          names(BW.sd1)[4] <- "sd"
          
          
# Collect the summary statistics in a dataframe
    BW.summaries1<-merge(BW.mean1, BW.sd1)
    BW.summaries1<-BW.summaries1[order(BW.summaries1$MoteGen,BW.summaries1$Day),]
    BW.summaries1

```


## 4.2 Genotypes with nutrients (pooled) over time model

```{r}
  BW.Tall$Treatment2 <- "Nutrients"
  BW.Tall$Treatment2[BW.Tall$Treatment=="Ambient"] <- "Ambient"
  BW.Tall$Treatment2<-as.factor(BW.Tall$Treatment2)
  summary (BW.Tall$Treatment2)
```

### Figure 3b

```{r, echo =FALSE}

Fig3b <- ggplot(BW.Tall, aes(Days, dAW.gd, colour=MoteGen, fill=MoteGen)) + 
  ggthe_bw + ggtitle("b. growth by genet and treatment")+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                     position = position_dodge(2), alpha=0.8 )+
  stat_summary(fun.y=mean, geom="line", position = position_dodge(2),
               linetype=1, alpha=0.5) + 
  stat_summary(fun.y=mean, geom="point", size =2, shape=21, alpha=0.5,
                   position=position_dodge(width=2))  +
  theme(legend.position=c(0.2,0.3), 
        legend.title = element_blank(),
        strip.background = element_rect(fill="white"))+
  
  scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(-30, 113, 15),  
                           expand = c(0, 0))+
  scale_y_continuous(name=("Growth (mg g-1 d-1) "),
                           limits = c(-1.8,5),
                           breaks = seq(-1, 5, 1),  
                           expand = c(0, 0))+
  
      annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
                colour = "gray35")+
      annotate("text", x = -16, y = -1.2, label = "Baseline", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray35", linetype="dashed")+
      annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 91, y = -1.4, yend = 4.5,
                colour = "gray35", linetype="dotted")+
    
      annotate("segment", x = 91, xend = 110, y = 4.5, yend = 4.5,
                colour = "gray35", linetype="dotted")+
      annotate("text", x = 99, y = -1.2, label = "Heat", size=3)+
  facet_grid(~Treatment2)
Fig3b

#ggsave(file="Outputs/Growth_genotype.svg", plot=BW_Col2, dpi = 300, units="in", width=6.5, height=4.5)

```


## Figure 3

```{r}
Figure.3<-grid.arrange(BW_Treat, Fig3b,
          ncol = 2,  widths = c(1.1,2))
#ggsave(file="Outputs/Figure3ab.svg", plot=Figure.3, width=7.5, height=4.5)
```


```{r}
Colour.colour<-scale_colour_manual(values = c ("#4A6CAA", "#b45274"))
Fill.colour<-scale_fill_manual(values = c ("#4A6CAA",  "#b45274"))

BW_Col <- ggplot(BW.Tall, aes(Days, dAW.gd, fill=Treatment2,
                              shape=factor(Treatment2))) +
  
     annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
            colour = "gray90", linetype=1)+
     annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray35", linetype=2)+
     annotate("segment", x = 79, xend = 91, y = -1.4, yend = 4.5,
                colour = "gray35", linetype=3)+
     annotate("segment", x = 91, xend = 110, y = 4.5, yend = 4.5,
                colour = "gray35", linetype=3)+
     
           stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                        position=position_dodge(width=5), width = 10)+
           stat_summary(fun.y=mean, geom="point", size =2,
                        position=position_dodge(width=5), alpha=0.8) +
           stat_summary(fun.y=mean, geom="line", 
                        position=position_dodge(width=5), linetype=1) + 
    scale_shape_manual(values=c(21, 14),
                     labels=c("A", "N+P"))+
           ggthe_bw + Colour.colour + Fill.colour +
  
    scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(0, 113, 30),  
                           expand = c(0, 0))+
    scale_y_continuous(name="Growth rate (mg g-1 d-1) ", 
                         breaks = seq(-1, 5, by=1)) +
    #geom_hline(yintercept = 0, linetype=3)+
  
    theme(text=element_text(size=14),
          legend.position="none",
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +
     facet_wrap(~MoteGen)
BW_Col
```

## Model 2: Genotype model -N and N+P pooled compared to ambient.

```{r}
# Linear model 
  Model_genotype<-lmer(dAW.gd~MoteGen * Treatment2 *DayF + 
                         (1|Fra) + (1|Replicate),
                        data = BW.Tall)
  anova(Model_genotype)
  ranova(Model_genotype)
  #summary(Model_genotype)

# Pairwise comparisons
  # Day specific comparisons
  BW.emmc<-emmeans(Model_genotype, ~Treatment2|DayF)
  BW_groups<-cld(BW.emmc)
  BW_groups
  
  # Across days (temperature) comparisons
  BW.emmc<-emmeans(Model_genotype, ~Treatment2*DayF)
  BW_groups<-cld(BW.emmc)
  BW_groups<-BW_groups[order(BW_groups$DayF,BW_groups$Treatment),]
  BW_groups
  
  # genets comparisons
  BW.emmc<-emmeans(Model_genotype, ~Treatment2*DayF*MoteGen)
  BW_groups<-cld(BW.emmc)
  BW_groups<-BW_groups[order(BW_groups$DayF,
                             BW_groups$Treatment2, 
                             BW_groups$MoteGen),]
  BW_groups
  #write.csv(BW_groups, "Outputs/genotype_growth.csv", row.names = F)

```

* Growth in ambient declined in G50, G07 and G08 in A, but increased in G48, G62 and G31

## Summary by genotype, nutrient treatment (N and N+P pooled), and time point

```{r}
# sample means
BW.mean2 <- aggregate(dAW.gd~Treatment2+Days+MoteGen, data=BW.Tall, mean, na.rm=TRUE)
          names(BW.mean2)[4] <- "mean"
      
# sample SDs
BW.sd2 <- aggregate(dAW.gd~Treatment2+Days+MoteGen, data=BW.Tall, sd, na.rm=TRUE)
          names(BW.sd2)[4] <- "sd"
          
          
# Collect the summary statistics in a dataframe
    BW.summaries2<-merge(BW.mean2, BW.sd2)
    BW.summaries2<-BW.summaries2[order(BW.summaries2$MoteGen,BW.summaries2$Day),]
    BW.summaries2
```

# 5. Plot relative differences

## 5.1 Compare the treatment effect ambient versus elevated nutrients (N and N+p pooled) inside each genotype

```{r}

# Calculate relative changes (1 - Ambient)
      
BW.Tall$Nutrients2<-BW.Tall$Nutrients
BW.Tall$Nutrients2[BW.Tall$DayF=="-28"]<-"Ambient"
          
    BW.Summary <-BW.Tall %>%
          group_by(MoteGen, Nutrients2, DayF) %>%
          get_summary_stats(dAW.gd, type = "mean_sd")
    BW.Summary
    
    BW.Summary<-subset(BW.Summary, Nutrients2=="Ambient" )
    BW.Summary<-BW.Summary[, -3]
    BW.Summary<-BW.Summary[, -3]
    BW.Summary<-BW.Summary[, -3]
    names(BW.Summary)[3] <- "A_Mean"
    
    BW.Tall<-merge(BW.Tall, BW.Summary,  by=c("MoteGen", "DayF"), all.x = T)
    BW.Tall$Difference<-BW.Tall$dAW.gd-BW.Tall$A_Mean
```


## All genotypes by nutrient treatment over time (difference)

```{r}

Colour.colour<-scale_colour_manual(values = c ("#4A6CAA", "#b45274"))
Fill.colour<-scale_fill_manual(values = c ("#4A6CAA",  "#b45274"))

BW_Diff_Col <- ggplot(BW.Tall, aes(Days, Difference, fill=Nutrients2,
                              shape=factor(Nutrients2))) +
      annotate("segment", x = -30, xend = 0, y = -3.5, yend = -3.5,
                  colour = "gray35", linetype = 1)+  
      annotate("segment", x = 2, xend = 91, y = -3.5, yend = -3.5,
                colour = "gray35", linetype = "dashed")+
      annotate("segment", x = 79, xend = 91, y = -3.5, yend = 1,
                colour = "gray35", linetype = "dotted")+
      annotate("segment", x = 91, xend = 110, y =1, yend =1,
                colour = "gray35",  linetype = "dotted")+
    
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                        position=position_dodge(width=5), width = 10)+
      stat_summary(fun.y=mean, geom="point", size =2,
                        position=position_dodge(width=5), alpha=0.8) +
      stat_summary(fun.y=mean, geom="line", 
                        position=position_dodge(width=5), linetype=1) + 
      
      scale_shape_manual(values=c(21, 14),
                     labels=c("A", "N and N+P"))+ 
      ggthe_bw + Colour.colour + Fill.colour +
      scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(0, 113, 30),  
                           expand = c(0, 0))+
      scale_y_continuous(name="Difference in growth (mg g-1 d-1) respecto to ambient", 
                         breaks = seq(-4, 1.5, by=1)) +
  
    theme(legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +

     facet_wrap(~MoteGen)
BW_Diff_Col
        
#ggsave(file="Outputs/S_3_BW_Diff_Col.svg", plot=BW_Diff_Col, width=5.0, height=5)
          
```

##  All genotypes by nutrient treatment over time (percentage)

```{r}
# Calculate percentages changes (1 - Control)
  BW.Tall$percentage<-(BW.Tall$Difference/BW.Tall$A_Mean)*100

```


```{r}

Colour.colour<-scale_colour_manual(values = c ("#4A6CAA", "#b45274"))
Fill.colour<-scale_fill_manual(values = c ("#4A6CAA",  "#b45274"))

BW_perent_Col <- ggplot(BW.Tall, aes(Days, percentage, fill=Nutrients2,
                              shape=factor(Nutrients2))) +
      annotate("segment", x = -30, xend = 0, y = -140, yend = -140,
                  colour = "gray35", linetype = 1)+  
      annotate("segment", x = 2, xend = 91, y = -140, yend = -140,
                colour = "gray35", linetype = "dashed")+
      annotate("segment", x = 79, xend = 91, y = -139, yend = 28,
                colour = "gray35", linetype = "dotted")+
      annotate("segment", x = 91, xend = 110, y = 28, yend =28,
                colour = "gray35",  linetype = "dotted")+
    
           stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                        position=position_dodge(width=5), width = 10)+
           stat_summary(fun.y=mean, geom="point", size =2,
                        position=position_dodge(width=5), alpha=0.8) +
           stat_summary(fun.y=mean, geom="line", 
                        position=position_dodge(width=5), linetype=1) + 
    scale_shape_manual(values=c(21, 14),
                     labels=c("A", "N and N+P"))+
           ggthe_bw + Colour.colour + Fill.colour +
    scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(0, 113, 30),  
                           expand = c(0, 0))+
    scale_y_continuous(name="Percentage of growth change respecto to ambient", 
                         breaks = seq(-140, 100, by=20)) +
  
      theme(legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +

     facet_wrap(~MoteGen)
BW_perent_Col

#ggsave(file="Outputs/S_3_BW_Percentaje_Col.svg", plot=BW_perent_Col, width=5.0, height=5)

```


## 5.2 Compare among genotypes using treatment means as reference.

```{r}
# Calculate relative changes (mean per treatment - genotype per treatment)
    
    BW.Summary2 <-BW.Tall %>%
          group_by(Nutrients2, DayF) %>%
          get_summary_stats(dAW.gd, type = "mean_sd")
    BW.Summary2
    
    BW.Summary2<-BW.Summary2[, -3]
    BW.Summary2<-BW.Summary2[, -3]
    BW.Summary2<-BW.Summary2[, -4]
    
    BW.Tall<-merge(BW.Tall, BW.Summary2,  by=c("Nutrients2", "DayF"), all.x = T)
    BW.Tall$Difference2<-BW.Tall$dAW.gd-BW.Tall$mean
```

## Relative genotypes performance by nutrient treatment over time (difference)

```{r}

Colour.colour<-scale_colour_manual(values = c ("#4A6CAA", "#b45274"))
Fill.colour<-scale_fill_manual(values = c ("#4A6CAA",  "#b45274"))

BW_Diff_Col2 <- ggplot(BW.Tall, aes(Days, Difference2, fill=Nutrients2,
                              shape=factor(Nutrients2))) +
      annotate("segment", x = -30, xend = 0, y = -2.5, yend = -2.5,
                  colour = "gray35", linetype = 1)+  
      annotate("segment", x = 2, xend = 91, y = -2.5, yend = -2.5,
                colour = "gray35", linetype = "dashed")+
      annotate("segment", x = 79, xend = 91, y = -2.5, yend = 1.5,
                colour = "gray35", linetype = "dotted")+
      annotate("segment", x = 91, xend = 110, y =1.5, yend =1.5,
                colour = "gray35",  linetype = "dotted")+
   annotate("segment", x = -30, xend = 110, y = 0, yend = 0,
                  colour = "gray90", linetype = 1)+  
    
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                        position=position_dodge(width=5), width = 10)+
      stat_summary(fun.y=mean, geom="point", size =2,
                        position=position_dodge(width=5), alpha=0.8) +
      stat_summary(fun.y=mean, geom="line", 
                        position=position_dodge(width=5), linetype=1) + 
      
      scale_shape_manual(values=c(21, 14),
                     labels=c("A", "N and N+P"))+ 
      ggthe_bw + Colour.colour + Fill.colour +
      scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(0, 113, 30),  
                           expand = c(0, 0))+
      scale_y_continuous(name="Difference in growth (mg g-1 d-1) respecto to mean treatment", 
                         breaks = seq(-4, 1.5, by=1)) +
  
    theme(text=element_text(size=12),
          legend.position="bottom",
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +

     facet_wrap(~MoteGen)
BW_Diff_Col2
        
#ggsave(file="Outputs/S_3_BW_Diff_Col.svg", plot=BW_Diff_Col, width=5.0, height=5)
          
```

##  Genets performance percentage

```{r}
# Calculate percentages changes (1 - Control)
  BW.Tall$percentage2<-(BW.Tall$Difference2/BW.Tall$mean)*100

```


```{r}
Colour.colour<-scale_colour_manual(values = c ("#4A6CAA", "#b45274"))
Fill.colour<-scale_fill_manual(values = c ("#4A6CAA",  "#b45274"))

BW_perent_Col3 <- ggplot(BW.Tall, aes(Days, percentage2, fill=Nutrients2,
                              shape=factor(Nutrients2))) +
      annotate("segment", x = -30, xend = 0, y = -140, yend = -140,
                  colour = "gray35", linetype = 1)+  
      annotate("segment", x = 2, xend = 91, y = -140, yend = -140,
                colour = "gray35", linetype = "dashed")+
      annotate("segment", x = 79, xend = 91, y = -139, yend = 28,
                colour = "gray35", linetype = "dotted")+
      annotate("segment", x = 91, xend = 110, y = 28, yend =28,
                colour = "gray35",  linetype = "dotted")+
    
           stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                        position=position_dodge(width=5), width = 10)+
           stat_summary(fun.y=mean, geom="point", size =2,
                        position=position_dodge(width=5), alpha=0.8) +
           stat_summary(fun.y=mean, geom="line", 
                        position=position_dodge(width=5), linetype=1) + 
    scale_shape_manual(values=c(21, 14),
                     labels=c("A", "N and N+P"))+
           ggthe_bw + Colour.colour + Fill.colour +
    scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(0, 113, 30),  
                           expand = c(0, 0))+
    scale_y_continuous(name="Percentage of growth change respecto to ambient", 
                         breaks = seq(-140, 100, by=20)) +
  
      theme(text=element_text(size=12),
          legend.position="bottom",
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +

     facet_wrap(~MoteGen)
BW_perent_Col3

#ggsave(file="Outputs/S_3_BW_Percentaje_Col.svg", plot=BW_perent_Col, width=5.0, height=5)

```


# 6. Visualize individual timepoints?

```{r}
summary(BW.Tall$DayF)
BW.Acer_28<-subset(BW.Tall, DayF=="-28")
BW.Acer75<-subset(BW.Tall, DayF=="75")
BW.Acer92<-subset(BW.Tall, DayF=="91")
BW.Acer110<-subset(BW.Tall, DayF=="100")

BW.AcerTimePoints<-rbind(BW.Acer_28, BW.Acer75, BW.Acer92, BW.Acer110)

BW_Timepoints<- ggplot(BW.AcerTimePoints, aes (DayF, dAW.gd, fill=MoteGen, shape=Nutrients2)) +
  #ggtitle("(a) Baseline")+
  scale_shape_manual(values=c(21, 14),
                     labels=c("A", "N and N+P"))+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2) +
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.9) + ggthe_bw +
    scale_y_continuous(name=("Growth (mg/ g d) "),
                     limits = c(-1,6),
                     breaks = seq(-1, 6, by=1))+
  theme(legend.position="right",
        legend.title = element_blank(), 
        strip.background =element_rect(fill=NA))+ 
  facet_grid(~MoteGen)
BW_Timepoints

BW_Timepoints<- ggplot(BW.AcerTimePoints, aes (MoteGen, dAW.gd, fill=MoteGen, shape=Nutrients2)) +
  #ggtitle("(a) Baseline")+
  scale_shape_manual(values=c(21, 14),
                     labels=c("A", "N and N+P"))+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.9) + ggthe_bw +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2) +
  scale_y_continuous(name=("Growth (mg/ g d) "),
                     limits = c(-1,6),
                     breaks = seq(-1, 6, by=1))+
  theme(legend.position="right",
        legend.title = element_blank(), 
        strip.background =element_rect(fill=NA))+ 
  facet_grid(~DayF)
BW_Timepoints

#ggsave(file="Outputs/S4_YII_Treat_Colo.svg", plot=BW_Timepoints, width=5.5, height=3)
```


# 7. Other models (Non-constrained models)

## Only Ambient (Heat by genotype)


```{r}
A_data<-subset(BW.Tall, Treatment=="Ambient")

fit1 <- gls(dAW.gd ~ DayF *MoteGen, data=A_data,
  correlation=corSymm(form=~TimePoint|Fra),
  weights=varIdent(form=~1|TimePoint),
  na.action=na.exclude,
  control=glsControl(opt="optim"))
```

Only Ambient summary model 

```{r}
summary(fit1)
intervals(fit1)
anova(fit1, type="marginal")
getVarCov(fit1)
residuals(fit1, type="pearson")

par(mfrow=c(1,2))
plot(fitted(fit1), residuals(fit1, type="pearson"))
abline(h=0)
qqnorm(residuals(fit1, type="pearson"))
abline(0,1)
```

Predictions 

```{r}
clda_Gls_1 <- Gls(dAW.gd ~ DayF * MoteGen, 
                  correlation=corSymm (form = ~TimePoint|Fra),
        weights=varIdent(form=~1|TimePoint),
        na.action=na.exclude,
        control=glsControl(opt="optim"),
        data=A_data)

data1<-expand.grid(DayF=unique(BW.Tall$DayF),
                   MoteGen=unique(BW.Tall$MoteGen))

predictions_1 <- cbind(data1, 
predict (clda_Gls_1, data1, conf.int=0.95))

predictions_1$Days<-as.numeric(as.character(predictions_1$DayF))

```

Model prediction Ambient (heat) and genotype (tanks?)

```{r}
pd <- position_dodge(2)
limits <- aes(ymax = upper , ymin=lower, shape=MoteGen)

pCI1 <- ggplot(predictions_1, aes(y=linear.predictors, x=Days, 
                                fill=MoteGen)) + 
        geom_errorbar(limits, width= 2 , position=pd) + 
        geom_line(aes(group=MoteGen, y=linear.predictors), position=pd, size=0.1) + 
        geom_point(aes(fill=MoteGen), shape=21, position=pd, size=4, alpha=0.8) +
        
        ggthe_bw+
        
        geom_hline(yintercept = 0, linetype=3)+
      
        scale_x_continuous(name="Days in the experiment", 
                         breaks = seq(0, 115, by=15)) +
        scale_y_continuous(name="Estimated growth (mg / g d) ", 
                         breaks = seq(-1, 4, by=1)) +
    
        theme(text=element_text(size=14),
          legend.position="right",
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +
    
      annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
                colour = "gray90")+
      annotate("text", x = -16, y = -1.2, label = "Baseline", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray90")+
      annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 91, y = -1.4, yend = -1,
                colour = "gray90")+
    
      annotate("segment", x = 91, xend = 110, y = -1, yend = -1,
                colour = "gray90")+
      annotate("text", x = 99, y = -1.2, label = "Heat", size=3)
 
 
pCI1
```

### Normalized ambient before and after heat 

```{r}
# Calculate relative changes (1 - Ambient)
    D75<-subset(predictions_1, DayF=="75" )
    D75 <- subset(D75, select = c(MoteGen, linear.predictors))
    colnames(D75)<-c("MoteGen", "Day75")
    H_effects<-merge(predictions_1, D75, by=c("MoteGen"), all.x = T)
    summary(H_effects)

H_effects$effects<-(H_effects$linear.predictors-H_effects$Day75)
    H_effects$effects_l<-H_effects$lower-H_effects$Day75          
    H_effects$effects_u<-H_effects$upper-H_effects$Day75          
    
```

Difference Ambient (heat)

```{r}
pd <- position_dodge(3)
limits <- aes(ymax = effects_u , ymin=effects_l, shape=MoteGen)

Gen_heat <- ggplot(H_effects, aes(y=effects, x=Days, 
                                fill=MoteGen)) + 
        geom_errorbar(limits, width= 10 , position=pd) + 
        geom_line(aes(group=MoteGen, y=effects), position=pd, size=0.1) + 
        geom_point(aes(fill=MoteGen), shape=21, position=pd, size=4, alpha=0.8) +
        
        ggthe_bw+
        
        geom_hline(yintercept = 0, linetype=3)+
      
        scale_x_continuous(name="Days in the experiment", 
                         breaks = seq(0, 115, by=15)) +
        #scale_y_continuous(name="Estimated growth (mg / g d) ", 
         #                breaks = seq(-1, 4, by=1)) +
    
        theme(text=element_text(size=14),
          legend.position="right",
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +
    
      annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
                colour = "gray90")+
      annotate("text", x = -16, y = -1.2, label = "Baseline", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray90")+
      annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 91, y = -1.4, yend = -1,
                colour = "gray90")+
    
      annotate("segment", x = 91, xend = 110, y = -1, yend = -1,
                colour = "gray90")+
      annotate("text", x = 99, y = -1.2, label = "Heat", size=3)

Gen_heat
```

## Only Treatment

```{r}
fit2 <- gls(dAW.gd~Treatment * DayF, data=subset(BW.Tall),
    correlation=corSymm(form=~TimePoint|Fra),
    weights=varIdent(form=~1|TimePoint),
    na.action=na.exclude,
    control=glsControl(opt="optim"))

```

Only treatment summary model 

```{r}
summary(fit2)
  intervals(fit2)
  anova(fit2, type="marginal")
  getVarCov(fit2)
  #residuals(fit2, type="pearson")
  
  par(mfrow=c(1,2))
  plot(fitted(fit2), residuals(fit2, type="pearson"))
  abline(h=0)
  qqnorm(residuals(fit2, type="pearson"))
  abline(0,1)
```

Predictions 

```{r}
clda_Gls_2 <- Gls(dAW.gd~Treatment * DayF, data=BW.Tall,
  correlation=corSymm(form=~TimePoint|Fra),
  weights=varIdent(form=~1|TimePoint),
  na.action=na.exclude,
  control=glsControl(opt="optim"))

data2<-expand.grid(DayF=unique(BW.Tall$DayF),
                   Treatment=unique(BW.Tall$Treatment))

predictions_2 <- cbind(data2, 
predict (clda_Gls_2, data2, conf.int=0.95))

predictions_2$Days<-as.numeric(as.character(predictions_2$DayF))
```

Model prediction Ambient (heat)
```{r}
pd <- position_dodge(2)
limits <- aes(ymax = upper , ymin=lower, shape=Treatment)

Model_Tratement <- ggplot(predictions_2, aes(y=linear.predictors, x=Days, 
                                fill=Treatment)) + 
        geom_errorbar(limits, width= 2 , position=pd) + 
        geom_line(aes(group=Treatment, y=linear.predictors), position=pd, size=0.1) + 
        geom_point(aes(fill=Treatment), shape=21, position=pd, size=4, alpha=0.8) +
        
        ggthe_bw+
        geom_hline(yintercept = 0, linetype=3)+
      
        scale_x_continuous(name="Days in the experiment", 
                         breaks = seq(0, 115, by=15)) +
        scale_y_continuous(name="Estimated growth (mg / g d) ", 
                         breaks = seq(-1, 4, by=1)) +
    
        theme(text=element_text(size=14),
          legend.position="right",
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +
    
      annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
                colour = "gray90")+
      annotate("text", x = -16, y = -1.2, label = "Baseline", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray90")+
      annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 91, y = -1.4, yend = -1,
                colour = "gray90")+
    
      annotate("segment", x = 91, xend = 110, y = -1, yend = -1,
                colour = "gray90")+
      annotate("text", x = 99, y = -1.2, label = "Heat", size=3)
 
Model_Tratement
```


## Treatment and Genotype

```{r}
BW.nutrients<-subset(BW.Tall, Days<91)
fit3 <- gls(dAW.gd ~ Treatment * DayF * Genotype, data=BW.nutrients,
     correlation=corSymm(form=~TimePoint|Fra),
      weights=varIdent(form=~1|TimePoint),
      na.action=na.exclude,
      control=glsControl(opt="optim"))

```

Summary model 

```{r}
summary(fit3)

intervals(fit3)
anova(fit3, type="marginal")
getVarCov(fit3)
#residuals(fit3, type="pearson")

par(mfrow=c(1,2))
plot(fitted(fit3), residuals(fit3, type="pearson"))
abline(h=0)
qqnorm(residuals(fit3, type="pearson"))
abline(0,1)
```

Predictions 

```{r}
clda_Gls_3 <- Gls(dAW.gd~ DayF* Treatment * MoteGen, data=BW.nutrients,
  correlation=corSymm(form=~TimePoint|Fra),
  weights=varIdent(form=~1|TimePoint),
  na.action=na.exclude,
  control=glsControl(opt="optim"))


data3<-expand.grid(DayF=unique(BW.nutrients$DayF),
                   Treatment=unique(BW.nutrients$Treatment),
                   MoteGen=unique(BW.nutrients$MoteGen))

predictions_3 <- cbind(data3,
                       predict (clda_Gls_3, data3, conf.int=0.95))

predictions_3$Days<-as.numeric(as.character(predictions_3$Day))
```

Model prediction Ambient (heat)

* This model does not control for baseline!!! 

```{r}
pd <- position_dodge(2)
limits <- aes(ymax = upper , ymin=lower, shape=Treatment)

Model_Tratement <- ggplot(predictions_3, aes(y=linear.predictors, x=Days, 
                                fill=Treatment)) + 
        geom_errorbar(limits, width= 2 , position=pd) + 
        geom_line(aes(group=Treatment, y=linear.predictors), position=pd, size=0.1) + 
        geom_point(aes(fill=Treatment), shape=21, position=pd, size=4, alpha=0.8) +
        
        ggthe_bw+
        
        geom_hline(yintercept = 0, linetype=3)+
      
        scale_x_continuous(name="Days in the experiment", 
                         breaks = seq(0, 115, by=15)) +
        scale_y_continuous(name="Estimated growth (mg / g d) ", 
                         breaks = seq(-1, 4, by=1)) +
    
        theme(text=element_text(size=14),
          legend.position="right",
          legend.title = element_blank(), 
          strip.background =element_rect(fill=NA)) +
    
      annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
                colour = "gray90")+
      annotate("text", x = -16, y = -1.2, label = "Baseline", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray90")+
      annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 91, y = -1.4, yend = -1,
                colour = "gray90")+
    
      annotate("segment", x = 91, xend = 110, y = -1, yend = -1,
                colour = "gray90")+
      annotate("text", x = 99, y = -1.2, label = "Heat", size=3)
 
Model_Tratement + facet_wrap(~MoteGen)
```


