---
title: "Growth rates in A. cervicornis under elevated N and N+P and subsequent heat stress"
author: "Ana Palacio"
date: "Feb 13, 2020"
output:
  html_document:
    fig_height: 3.5
    fig_width: 6
    df_print: paged
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

# General project set-up 

```{r libraries, results="hide"}

# Load all libraries and sources required to run the script
    library(tidyverse)
    library(ggthemes)
    library(lmerTest)
    library(emmeans)
    library(multcomp)

# Default ggplot settings

    Fill.colour<-scale_colour_manual(values = c("black", "gray70", "gray35"))

    ggthe_bw<-theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black")
          )+
    theme_bw()
```

# Import and clean growth data

```{r}
# Import data: 

  ## Growth long
    BW.Tall<-read.csv("Growth_corrected.csv", header = TRUE)
    
  ## Genotype information
    MOTE<-read.csv("Genotype_Info.csv", header = TRUE)
    BW.Tall<-merge(BW.Tall, MOTE, by="Gen", all.x=TRUE)
    
  ## Data type  
    BW.Tall$Initial.Date<-as.Date(BW.Tall$Initial.Date, "%m/%d/%y")
    BW.Tall$Final.Date<-as.Date(BW.Tall$Final.Date, "%m/%d/%y")
    # BW.Tall$Initial.Date<-as.Date(BW.Tall$Initial.Date, "%Y-%m-%d")
    # BW.Tall$Final.Date<-as.Date(BW.Tall$Final.Date, "%Y-%m-%d")
    BW.Tall$Days<-(as.numeric(as.Date(BW.Tall$Final.Date))-17485)
    BW.Tall$Day<-(as.factor(BW.Tall$Days))
    BW.Tall$TimePoint[BW.Tall$Day=="-28"]<-"3"
    BW.Tall$TimePoint[BW.Tall$Day=="-7"]<-"4"
    BW.Tall$TimePoint[BW.Tall$Day=="28"]<-"9"
    BW.Tall$TimePoint[BW.Tall$Day=="62"]<-"11"
    BW.Tall$TimePoint[BW.Tall$Day=="75"]<-"13"
    BW.Tall$TimePoint[BW.Tall$Day=="91"]<-"16"
    BW.Tall$TimePoint[BW.Tall$Day=="100"]<-"17"
    BW.Tall$TimePoint[BW.Tall$Day=="113"]<-"22"
    
    BW.Tall$Treatment <- as.character(BW.Tall$Treatment)
    BW.Tall$Treatment[BW.Tall$Treatment == "Control"] <- "A"
    BW.Tall$Treatment[BW.Tall$Treatment == "NP"] <- "N+P"
    BW.Tall$Treatment <- as.factor(BW.Tall$Treatment)
    
    BW.Tall$Colony <- as.factor(BW.Tall$Gen)
    BW.Tall$MoteGen<-factor(BW.Tall$MoteGen, 
                                   levels=c("G_48", "G_62","G_31", "G_08","G_07", "G_50"))
    BW.Tall$SampleID <- paste("Ac", BW.Tall$Fra, BW.Tall$TimePoint, sep = "_")
  
  ## Data subsets  
    BW.Initial<-subset(BW.Tall, Initial.Date=="2017-08-30") # Only baseline
   
    BW.Control<-subset(BW.Tall, Treatment=="A") # Only Ambient
    BW.Control<-subset(BW.Control, Days<80)
    BW.Control<-subset(BW.Control, Initial.Date!="2017-10-18")
    
    BW.nutrients<-subset(BW.Tall, Days>-10) # Remove baseline
    BW.nutrients<-subset(BW.nutrients, Days<113)
    
  ## Remove recovery data points
    BW.Tall<-subset(BW.Tall, Initial.Date!="2017-10-18")
    BW.Tall<-subset(BW.Tall, Initial.Date!="2018-02-23") # After heat stress
    
  
```


# Growth over time (during Control and Heat stress) by nutrient treatment

## Figure 3a

```{r, fig.height=3.5, fig.width=3.5}
# Treatment effect over time
    BW_Treat<- ggplot(BW.Tall, aes (Days, dAW.gd, shape=factor(Treatment),
                                    colour=factor(Treatment))) + 
      ggthe_bw + Fill.colour + ggtitle("a")+
      stat_summary(fun.data = "mean_cl_boot", geom = "errorbar",
                   position=position_dodge(width=5))+
      stat_summary(fun.y=mean, geom="line", 
                   position=position_dodge(width=5), linetype=2) +
      stat_summary(fun.y=mean, geom="point", size =2,
                   position=position_dodge(width=5))  + 
  
      geom_hline(yintercept = 0, linetype=3)+
      
      scale_x_continuous(name="Days in the experiment", 
                         breaks = seq(0, 115, by=15)) +
      scale_y_continuous(name="Growth (mg / g d)", 
                         breaks = seq(-1, 4, by=1)) +
    
    theme(legend.position=c(0.2, 0.5),
        legend.title = element_blank(), 
        strip.background =element_rect(fill=NA)) +

      annotate("segment", x = -30, xend = -2, y = -1.5, yend = -1.5,
                colour = "gray90")+
      annotate("text", x = -16, y = -1.2, label = "Baseline", size=3)+
    
      annotate("segment", x = 2, xend = 91, y = -1.5, yend = -1.5,
                colour = "gray90")+
      annotate("text", x = 45, y = -1.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 91, y = -1.4, yend = -1,
                colour = "gray90")+
    
      annotate("segment", x = 91, xend = 110, y = -1, yend = -1,
                colour = "gray90")+
      annotate("text", x = 99, y = -1.2, label = "Heat", size=3)
  BW_Treat
  
# ggsave(file="Outputs/Figure3_BW_corrected.svg", plot=BW_Treat, dpi = 300, units="in", width=3.5, height=3.0)
```

## Figure S2a: All genotypes by nutrient treatment over time


```{r, echo =FALSE}
BW_Col <- ggplot(BW.Tall, aes(Days, dAW.gd, colour=factor(Treatment),
                              shape=factor(Treatment))) +
           stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                        position=position_dodge(width=5), width = 10)+
           stat_summary(fun.y=mean, geom="point", size =2,
                        position=position_dodge(width=5), alpha=0.5) +
           stat_summary(fun.y=mean, geom="line", 
                        position=position_dodge(width=5), linetype=1) + 
           ggthe_bw + Fill.colour + ggtitle("a") +
   scale_x_continuous(name="Days in the experiment",
                           limits = c(-35,113),
                           breaks = seq(0, 113, 30),  
                           expand = c(0, 0))+
  
    ylab("Growth (mg/ g d) ") + 
    theme(axis.title.y=element_text(size=12), 
           legend.position="bottom",
           legend.title = element_blank()) +
     
     annotate("segment", x = 2, xend = 91, y = -1, yend = -1,
                   colour = "gray90", linetype=1)+
     annotate("segment", x = 79, xend = 91, y = -1, yend = -0.5,
                   colour = "gray90", linetype=1)+
     annotate("segment", x = 91, xend = 110, y = -0.5, yend = -0.5,
                   colour = "gray90", linetype=1)+
     annotate("text", x = 45, y = -1.5, label = "Nutrients", size=3)+
     annotate("text", x = 99, y = -1.5, label = "H", size=3) +
     facet_grid(~MoteGen)
BW_Col

#ggsave(file="Outputs/S2a_Growth_genotype.svg", plot=BW_Col, width=6.0, height=3.5)

```

## Other interesting figures

Compare individual genotypes inside each nutrient treatment
* Growth declined in G50, G07 and G08 in A, but increased in G48, G62 and G31

```{r}
BW_ColonyT<- ggplot(BW.Tall, aes (Days, dAW.gd, colour=MoteGen)) +   
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.8)+
  stat_summary(fun.y=mean, geom="point", size =2, alpha=0.5) +
   ylab("Growth (mg/ g d)") +
  
     annotate("segment", x = 2, xend = 91, y = -1, yend = -1,
                   colour = "gray90", linetype=1)+
     annotate("segment", x = 79, xend = 91, y = -1, yend = -0.5,
                   colour = "gray90", linetype=1)+
     annotate("segment", x = 91, xend = 110, y = -0.5, yend = -0.5,
                   colour = "gray90", linetype=1)+
     annotate("text", x = 45, y = -1.5, label = "Nutrients", size=3)+
     annotate("text", x = 99, y = -1.5, label = "H", size=3)+
  stat_summary(fun.y=mean, geom="line") + ggthe_bw + facet_grid (~Treatment)  
BW_ColonyT
```

Compare individual fragments inside each nutrient treatment

```{R}
BW_ColonyTF<- ggplot(BW.Tall, aes (Days, dAW.gd, colour=factor(Fra), group=Fra)) +    stat_summary(fun.y=mean, geom="line") + ggthe_bw + facet_grid (MoteGen~Treatment)+  geom_point()+ theme(legend.position = "none")
BW_ColonyTF

```

Initial performance vs ambient per genotype: some genotypes declined in growth even without nutrients

```{r, , fig.height=4, fig.width=6}

library(gridExtra)
BW_Init<- ggplot(BW.Initial, aes (MoteGen, dAW.gd, colour=MoteGen)) +
   ggtitle("a. All fragments Baseline")+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2) +
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) + ggthe_bw +
  scale_y_continuous(name=("Growth (mg/ g d) "),
                     limits = c(0,6),
                     breaks = seq(1, 6, by=1))+
   ylab("Growth (mg/ g d) ")+
  theme(legend.position=c(0.7, 0.3),
        legend.title = element_blank(), 
        strip.background =element_rect(fill=NA))

BW_Colony_Control<- ggplot(BW.Control, aes (Days, dAW.gd, colour=MoteGen)) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               width = 0.2, position=position_dodge(width=5)) +
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5,
               position=position_dodge(width=5)) +
  stat_summary(fun.y=mean, geom="line") + ggthe_bw + # ggthe_bw + geom_jitter()
   ggtitle("b. All fragments in Ambient overtime") +
  scale_y_continuous(name=("Growth (mg/ g d) "),
                     limits = c(0,6),
                     breaks = seq(1, 6, by=1))+
  theme(legend.position="none")

Captivityeffect<-grid.arrange(BW_Init,BW_Colony_Control, nrow=1)


```

```{r}
BW_Colony_Control<-ggplot(BW.Control, aes (Days, dAW.gd, colour=factor(Fra), group=Fra)) +   
  #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.8)+
  #stat_summary(fun.y=mean, geom="point", size =2, alpha=0.5) +
  stat_summary(fun.y=mean, geom="line") + ggthe_bw + 
  facet_wrap (~MoteGen)+  geom_point()+ theme(legend.position = "none")
BW_Colony_Control
```


# LMER model selection and pairwise comparisons

```{r}
# Complex to simple models 
  
  LM_1 <- lmer(dAW.gd ~ Treatment*Day +
                               (1 + Treatment|Colony), REML=TRUE, data= BW.Tall)
  
  LM_2 <- lmer(dAW.gd ~ Treatment * Day +
                               (Treatment|Colony), REML=TRUE,  data= BW.Tall)
   
  LM_3 <- lmer(dAW.gd ~ Treatment  * Day +
                               (1|Colony), REML=TRUE, data= BW.Tall)
 

# Select model
  AIC(LM_1, LM_2, LM_3) # 1=2, but 3 has lower AIC
  
  anova(LM_1, LM_2, refit=FALSE)
  anova(LM_2, LM_3, refit=FALSE)
  anova(LM_1, LM_3, refit=FALSE)
 
# Final model 
  LM_Treatment_Days<-lmer(dAW.gd ~ Treatment * Day +
                             (1|Colony),  data= BW.Tall)
  isSingular(LM_Treatment_Days)
  
  anova(LM_Treatment_Days)
  summary(LM_Treatment_Days)
  
# Pairwise comparisons
  BW.emmc<-emmeans(LM_Treatment_Days, ~Treatment*Day)
  contrast(BW.emmc, "tukey")
  BW_groups<-cld(BW.emmc)
  
    #BW_groups<-as.data.frame(BW_groups[complete.cases(BW_groups),])
    BW_groups<-BW_groups[order(BW_groups$Day,BW_groups$Treatment),]
  BW_groups
  
  write.csv(BW_groups, "Outputs/BW_groups_corrected.csv", row.names = F)

```

