---
title: "qPCR ratio calculations for Acer"
output: html_notebook
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```


# General project set-up 

```{r libraries , results="hide"}

    getwd()

    # Get all libraries and sources required to run the script
        library(steponeR)
        library(plyr)
        library(dplyr)
        library(reshape2)
        library(ggplot2)
        library(ggthemes)
        library(skimr)
```

## 1. Calculate qPCR RATIOS (Symbiont/Coral) 

Get the raw data for Acer R.Cunning steponeR function:

* Get list of plate files to read

* Calculate the ratios

* Extract the results

 
```{r CalculateRatios}

  Acer.plates <- list.files(path="qPCR-Raw", pattern=".csv", 
                           full.names=TRUE, recursive = TRUE)
  # Acer.plates

  # Run stepone function to get Ratios
  
  Acer.Out <- steponeR(files=Acer.plates, target.ratios=c("A.Acer"), 
                       fluor.norm=list(A=0, Acer=0),
                       copy.number=list(A=9, Acer=1),
                       ploidy=list(A=1, Acer=2),
                       extract=list(A=0.813, Acer=0.982))
  
  
  
  # Target ratio results
  Acer<-Acer.Out$result
```

### 2. Data CLEANING part A: Remove NTC and +

```{r RemoveNTCandControls}
    # 1. Check and remove NTC wells
    
    ntc <- Acer[which(Acer$Sample.Name=="NTC" | Acer$Sample.Name=="-"), ]
    Acer <- droplevels(Acer[!rownames(Acer) %in% rownames(ntc), ])
    
    # 2. Check and remove + Control wells
    
    Positive <- Acer[which(Acer$Sample.Name=="+"), ]
    Acer <- droplevels(Acer[!rownames(Acer) %in% rownames(Positive), ])
```

### 3. Labeling and sample information

```{r GetLabelsAndSampleInfo}

# Get the sample information 
  SampleName<-read.csv("Sample_Plates.csv") 

# Create unique sample ID+FileName to relabel samples  
   Acer$Sample.Plate<-paste(Acer$Sample.Name,Acer$File.Name, sep="_")
   
# Replace Sample.Names in qPCR data 

  #  Plates.Typo <- SampleName[duplicated(SampleName$Sample.Plate),]
rownames(SampleName) <- SampleName$Sample.Plate
    Acer$Treatment<-SampleName[as.character(Acer$Sample.Plate), "Treatment"]
    Acer$Replicate<-SampleName[as.character(Acer$Sample.Plate), "Rep"]
    Acer$Fragment<-SampleName[as.character(Acer$Sample.Plate), "Frag"]
    Acer$Genotype<-SampleName[as.character(Acer$Sample.Plate), "Genotype"]
    Acer$Date<-SampleName[as.character(Acer$Sample.Plate), "Date"]
        Acer$Date<-as.Date(Acer$Date, format="%Y/%m/%d")
        Acer$Days<-as.numeric(Acer$Date -17485)

    Acer$qPCR_Date<-SampleName[as.character(Acer$Sample.Plate), "qPCR"]
        Acer$qPCR_Date<-as.Date(Acer$qPCR_Date, format="%Y/%m/%d")
    
# Creates a unique ID for a core-sampling time 

Acer$Sample<-paste(Acer$Fragment, Acer$Date, sep='_') 

  
# Correct blastate samples for extraction efficiency of 95.5%
  
  Acer.Blast<-subset(Acer, Acer$Type=="Slice/Blastate")
  Acer.Blast$A.Acer2<-(Acer.Blast$A.Acer)*0.828/0.97
  Acer$A.Acer[which(rownames(Acer) %in% rownames(Acer.Blast))] <-Acer.Blast$A.Acer2
  
```

### 4. Calculate total S/H ratio, clade specific ratios and clade (D) proportion

```{r}
# Get the ratios and log 10

# A ratio

Acer$logA.SH <- log10(Acer$A.Acer)
   
# # Total ratio
#   Acer$tot.SH <- Acer$A.SH + Acer$C.SH
#   Acer$logTot.SH <- log10(Acer$tot.SH ) 
#   
#   # C ratio
#   Acer$logC.SH <- log10(Acer$C.SH)
#     
#   Acer$logTot.SH[which(Acer$tot.SH==0)] <- NA
#   Acer$logC.SH[which(Acer$C.SH==0)] <- NA
#   Acer$logD.SH[which(Acer$D.SH==0)] <- NA
#     
# # Clade Proportion
#   # D Proportion
#   Acer$D.Prp<-(Acer$D.SH/Acer$tot.SH)

```

### 5. Data CLEANING part B: Remove samples with one coral amplification as well as data from symbionts with 1 rep

```{r CleaningB}

# 1.If Clade only detected in one technical replicate, set its ratio to NA (becomes zero)
  Rerun.A<- Acer[which(Acer$A.reps==1),]
  Acer$A.Acer[which(Acer$A.reps==1)] <- NA

# 2. Make NA=0
  # colnames(Acer)[which(colnames(Acer) %in% "A.Acer")] <- "A.SH"  
  Acer$A.Acer[is.na(Acer$A.Acer)] <- 0
    
# 3.If coral detected in one technical replicate, remove the sample
  ReRun.Coral <- Acer[which(Acer$Acer.reps==1), ]
  Acer <- droplevels(Acer[!rownames(Acer) %in% rownames(ReRun.Coral), ])
   
  NoHSratio <- Acer[which(Acer$A.Acer==0), ]
  Acer <- droplevels(Acer[!rownames(Acer) %in% rownames(NoHSratio), ])

  StDe1.5 <- Acer[which((Acer$Acer.CT.sd>1.5)|(Acer$A.CT.sd>1.5)), ]
  Acer <- droplevels(Acer[!rownames(Acer) %in% rownames(StDe1.5), ])
   # ToRe_Run2<-anti_join (StDe1.5, Acer, by=c("Sample.Name", "Time"))
  
  #Histo_Acer_CT<-qplot(Acer.CT.mean, data=Acer, binwidth=0.15)
  #Histo_Acer_CT + facet_wrap(~Date)
  
  LateCoral<-Acer[which(Acer$Acer.CT.mean>27), ]
  Acer <- droplevels(Acer[!rownames(Acer) %in% rownames(LateCoral), ])
  
  HighSH<-Acer[which(Acer$A.Acer>0.9), ]
  Acer <- droplevels(Acer[!rownames(Acer) %in% rownames(HighSH), ])

  # Samples to Re-run    
  ToRe_Run1<-rbind(NoHSratio, Rerun.A)
  ToRe_Run1<-rbind(ToRe_Run1, ReRun.Coral)   
  ToRe_Run1<-rbind(ToRe_Run1, StDe1.5)
  ToRe_Run1<-rbind(ToRe_Run1, LateCoral)
  ToRe_Run1<-rbind(ToRe_Run1, HighSH) 
  ToRe_Run1<-anti_join (ToRe_Run1, Acer, by=c("Sample"))
  
```
    

### 6. Quality control: Check CTs in plates, sampling points, etc...

```{R check quality}

library(skimr)
skim(Acer)
head(Acer)

Coral_CTs <- ggplot (Acer, aes(Treatment, Acer.CT.mean, colour=factor(Replicate))) +
       geom_jitter(aes(colour=factor(Replicate))) +
       stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
       stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
       # facet_grid(~Replicate) +
       theme_gdocs() 
  Coral_CTs + facet_wrap(~Date)
  
 Coral_CTs<-ggplot (Acer, aes(Treatment, Acer.CT.mean, colour=factor(File.Name))) +
       geom_jitter(aes(colour=factor(File.Name))) +
       stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
       stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
       # facet_grid(~Replicate) +
       theme_gdocs() 
  Coral_CTs + facet_wrap(~qPCR_Date)
  
  A_CTs<-ggplot (Acer, aes(Treatment, A.CT.mean, colour=factor(File.Name))) +
       geom_jitter(aes(colour=factor(Replicate))) +
       stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
       stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
       # facet_grid(~Replicate) +
       theme_gdocs() 
  A_CTs + facet_wrap(~qPCR_Date)
  
  logSHTreatment <- ggplot(Acer, aes(Treatment, logA.SH, colour=factor(Treatment))) +
       # geom_jitter(aes(colour=factor(Replicate))) +
       stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
       stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
       facet_grid(~Replicate) +
       theme_gdocs() 
  logSHTreatment + facet_wrap(~Date)
  
  
  logSHTreatment <- ggplot(Acer, aes(Date, logA.SH, colour=factor(Treatment))) +
       geom_jitter(aes(colour=factor(qPCR_Date))) +
       stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
       stat_summary(fun.y=mean, geom="line", size =1) +
       theme_gdocs() 
logSHTreatment + facet_grid(Genotype~.)

```    

## 7. Chose bw samples ran more than once

```{r remove duplicates}

 ReRunA <- Acer[duplicated(Acer$Sample),] 
 n_RunA <- data.frame(table(Acer$Sample))
 colnames(n_RunA)<-c("Sample","RanA")
 Acer<-join(Acer, n_RunA, type = "left")

DuplicatesA <- Acer[(Acer$RanA>1),]

Duplicates<-ggplot(DuplicatesA, aes(Date, logA.SH, colour=factor(File.Name))) +
  facet_wrap(~Fragment) + stat_summary(fun.y=mean, geom="line") +   theme_gdocs() +
  geom_point() 
Duplicates
#  write.csv(DuplicatesA, file = 'DuplicatesA.csv')
```

## 8. Remove duplicates

```{r remove duplicates2}
ToRem1<-read.csv("ToRemove1.csv")
#     # 05/04/2018
   Acer<-Acer[!(Acer$Sample.Plate %in% ToRem1$Sample.Plate),]

# # Check for replicates again--should have none

  n_RunB <- data.frame(table(Acer$Sample))
  colnames(n_RunB)<-c("Sample","RanB")
  Acer<-join(Acer, n_RunB, type = "left")


# # List of duplicated samples, should have 0 rows now -->
   DuplicatesB <- Acer[(Acer$RanB>1),]
# # write.csv(DuplicatesB, file = 'DuplicatesB.csv')
```

## 9. Check and export S/H cell ratio data!

```{r} 
qPCRsummary<-summary(Acer)
capture.output(qPCRsummary, file = "Outputs/qPCRsummary.txt")

Acer %>%
  group_by(Treatment) %>%
  summarise(meanA = mean(A.CT.mean), meanAcer = mean(Acer.CT.mean), 
          SDA = mean(A.CT.sd), SdAcer = mean(Acer.CT.sd), 
          maxA = max(A.CT.mean), maxAcer = max(Acer.CT.mean), 
          minA = min(A.CT.mean), minAcer = min(Acer.CT.mean), n = n())

write.csv(Acer, "Outputs/SH_cell_ratio.csv", row.names = F)

```
