---
title: "Acer SH Nutrients"
author: "Ana Palacio"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
editor_options:
  chunk_output_type: console
bibliography: packages.bib
nocite: '@*'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```


# General project set-up 

```{r libraries , results="hide"}

# Get all libraries and sources required to run the script
        library(plyr)
        library(dplyr)
        library(reshape2)
        library(ggplot2)
        library(ggthemes)
        library(lme4)
        library(lmerTest)
        library(emmeans)
        library(scales)
        library(skimr)

# Default ggplot settings
Fill.colour<-scale_colour_manual(values = c("black", "gray70", "gray35"))

    ggthe_bw<-theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black")
          )+
    theme_bw()
```


## 1. DATA Exploration

Transform variables 

```{r VariablesToUse}

# Import S/H cell ratio data
qPCR.variables<-read.csv("Outputs/Acer_SH_cell_ratio.csv")

# Variable types 
str(qPCR.variables)
  qPCR.variables$Colony<-as.factor(qPCR.variables$Genotype)
  qPCR.variables$DaysF<-as.factor(qPCR.variables$Days)

  summary(qPCR.variables)
  #skim(qPCR.variables)

```
  

### 1.2. Exploratory graphs

```{r}
logSHTreatment <- ggplot(qPCR.variables, aes(Date, logA.SH, colour=factor(Treatment))) +
       # geom_jitter(aes(colour=factor(Treatment))) +
       stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
       stat_summary(fun.y=mean, geom="line", size =1) +
       theme_bw() 
logSHTreatment + facet_wrap(~Genotype)

# Removing weird points (whole fragment samples, between bleaching) and colonies not used (F)
    qPCR.variables_2<-subset(qPCR.variables, Date!="2018-02-05")
    qPCR.variables_2<-subset(qPCR.variables_2, Date!="2017-12-14")
    qPCR.variables_2<-subset(qPCR.variables_2, Date!="2018-03-01")
    qPCR.variables_2<-subset(qPCR.variables_2, Date!="2018-03-02")
    qPCR.variables_2<-subset(qPCR.variables_2, Date!="2018-03-03")
    qPCR.variables_2<-subset(qPCR.variables_2, Colony!="F")
    qPCR.variables_2<-subset(qPCR.variables_2, Sample!="145_T5")
    #qPCR.variables_2<-subset(qPCR.variables_2, Colony!="Yellow")
    
## Genotype information
    MOTE<-read.csv("Genotype_Info.csv", header = TRUE)
    qPCR.variables_2<-merge(qPCR.variables_2, MOTE, 
                            by="Genotype", all.x=TRUE)
    
    qPCR.variables_2$MoteGen<-factor(as.character(
      qPCR.variables_2$MoteGen), 
                             levels=c("G_48", "G_62","G_31", 
                                      "G_08","G_07", "G_50"))  # Resistance order
    

logSH_Colony<- ggplot(qPCR.variables_2, aes (Date, logA.SH, colour=factor(Treatment))) +
  geom_jitter(alpha=0.3)+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) +
  stat_summary(fun.y=mean, geom="line") +   theme_bw()
logSH_Colony + facet_grid (MoteGen~.)

logSH_Colony<- ggplot(qPCR.variables_2, aes (Date, logA.SH, colour=factor(Colony))) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) +
  stat_summary(fun.y=mean, geom="line") +   theme_bw()
logSH_Colony + facet_grid (Treatment~Replicate) +
  theme(legend.position = "none")
```

Add survivorship categories 

```{r}
qPCR.variables_2$Survivorship[qPCR.variables_2$MoteGen=="G_48"|
                              qPCR.variables_2$MoteGen=="G_62"|
                              qPCR.variables_2$MoteGen=="G_31"]<-"Resistant"

qPCR.variables_2$Survivorship[qPCR.variables_2$MoteGen=="G_08"|
                              qPCR.variables_2$MoteGen=="G_07"|
                              qPCR.variables_2$MoteGen=="G_50"]<-"Suceptible"
```

### Subset data for models

```{r}
SH.0<-subset(qPCR.variables_2, Days<2)
  SH.0<-droplevels(SH.0)

SH.C<-subset(qPCR.variables_2, Days<77)
  SH.C<-subset(SH.C, Days>2)
  SH.C<-droplevels(SH.C)

SH.H<-subset(qPCR.variables_2, Days>76)
  SH.H<-droplevels(SH.H)
```

# Figure 4a

## Raw data

```{r}
Summary_GenetTreatment<-qPCR.variables_2 %>%
        group_by(DaysF, MoteGen, Treatment) %>%
        dplyr::summarise(total.count=n()) 
Summary_GenetTreatment
```

* Raw data - Treatments (All genotypes pooled)

```{r}

Figure4 <- ggplot (qPCR.variables_2, aes(Days, A.Acer, colour=Treatment,
                                          shape=Treatment)) + 
    ggthe_bw + Fill.colour+ ggtitle("a.")+
    theme(legend.position=c(0.2, 0.3),
        legend.title = element_blank()) +
       #geom_jitter(aes(colour=factor(Replicate))) +
     
        
      annotate("segment", x = 2, xend = 91, y = 0.01, yend = 0.01,
                  colour = "gray90", linetype=2)+
      annotate("segment", x = 79, xend = 91, y = 0.01, yend = 0.04,
                  colour = "gray90", linetype=4)+
      annotate("segment", x = 91, xend = 110, y = 0.04, yend = 0.04,
                  colour = "gray90", linetype=3)+
      annotate("text", x = 3, y = 0.02, label = "BL", size=3, colour="gray")+
      annotate("text", x = 45, y = 0.02, label = "Nutrients", size=3, colour="gray")+
      annotate("text", x = 99, y = 0.02, label = "H", size=3, colour="gray")+
  
    scale_y_continuous(breaks = seq(0, 0.4, 0.05),
                       #limits = c(0,0.5),
                       expand = c(0.01,0.01),
                   name=("Symbiont to host cell ratio  (S/H)")) +
    scale_x_continuous(name="Days in the experiment",
                         limits = c(-2,113),
                         breaks = seq(0, 110, 15),  
                         expand = c(0, 0)) +
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 4), width = 2 )+
    stat_summary(fun.y=mean, geom="point", size =2, alpha=0.8, 
                   position = position_dodge(width = 4)) +
    stat_summary(fun.y=mean, geom="line", 
                    position = position_dodge(width = 4))

Figure4
Figure4+facet_wrap(~Genotype)

Figure4 <- ggplot (qPCR.variables_2, aes(Days, A.Acer, colour=Treatment,
                                          shape=Treatment)) + 
    ggthe_bw + Fill.colour+ ggtitle("a.")+
    theme(legend.position=c(0.2, 0.3),
        legend.title = element_blank()) +
       #geom_jitter(aes(colour=factor(Replicate))) +
     
        
      annotate("segment", x = 73, xend = 91, y = 0.01, yend = 0.01,
                  colour = "gray90", linetype=2)+
      annotate("segment", x = 79, xend = 91, y = 0.01, yend = 0.03,
                  colour = "gray90", linetype=3)+
      annotate("segment", x = 91, xend = 110, y = 0.03, yend = 0.03,
                  colour = "gray90", linetype=3)+
      #annotate("text", x = 3, y = 0.02, label = "BL", size=3, colour="gray")+
      annotate("text", x = 45, y = 0.02, label = "Nutrients", size=3, colour="gray")+
      annotate("text", x = 99, y = 0.02, label = "Heat", size=3, colour="gray")+
  
     scale_y_log10(breaks = seq(-0.05, 0.4, 0.05),
                       #limits = c(0,0.5),
                       expand = c(0.01,0.01),
                   name=("Symbiont to host cell ratio  (S/H)")) +
     scale_x_continuous(name="Days in the experiment",
                         limits = c(73,116),
                         breaks = seq(0, 110, 15),  
                         expand = c(0, 0)) +
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 2), width = 2 )+
    stat_summary(fun.y=mean, geom="point", size =2, alpha=0.8, 
                   position = position_dodge(width = 2)) +
    stat_summary(fun.y=mean, geom="line", 
                    position = position_dodge(width = 2))

Figure4
Figure4+facet_wrap(~Genotype)


Figure4 <- ggplot (qPCR.variables_2, aes(Days, logA.SH, colour=Treatment,
                                          shape=Treatment)) + 
    ggthe_bw + Fill.colour+ ggtitle("a.")+
    theme(legend.position=c(0.2, 0.3),
        legend.title = element_blank()) +
       #geom_jitter(aes(colour=factor(Replicate))) +
     
        
      annotate("segment", x = 73, xend = 91, y = 0.01, yend = 0.01,
                  colour = "gray90", linetype=2)+
      annotate("segment", x = 79, xend = 91, y = 0.01, yend = 0.04,
                  colour = "gray90", linetype=3)+
      annotate("segment", x = 91, xend = 110, y = 0.04, yend = 0.04,
                  colour = "gray90", linetype=3)+
      annotate("text", x = 3, y = 0.02, label = "BL", size=3, colour="gray")+
      annotate("text", x = 45, y = 0.02, label = "Nutrients", size=3, colour="gray")+
      annotate("text", x = 99, y = 0.02, label = "H", size=3, colour="gray")+
  
    #scale_y_continuous(breaks = seq(0, 0.4, 0.05),
     #                  #limits = c(0,0.5),
      #                 expand = c(0.01,0.01),
       #            name=("Symbiont to host cell ratio  (S/H)")) +
    scale_x_continuous(name="Days in the experiment",
                         limits = c(-2,116),
                         breaks = seq(0, 110, 15),  
                         expand = c(0, 0)) +
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 4), width = 2 )+
    stat_summary(fun.y=mean, geom="point", size =2, alpha=0.8, 
                   position = position_dodge(width = 4)) +
    stat_summary(fun.y=mean, geom="line", 
                    position = position_dodge(width = 4))

Figure4
Figure4+facet_wrap(~Genotype)


#ggsave(file="Outputs/Fig_4_SH_Acer.svg", plot=Figure4, width=3.3, height=3.5)
```

* Raw data - Treatments (Genotypes pooled by survivorship)

```{r}

Figure4b <- ggplot (subset(qPCR.variables_2, Days!=0), aes(Days, A.Acer, colour=Treatment,
                                          shape=Treatment)) + 
    ggthe_bw + Fill.colour+ ggtitle("a.")+
    theme(legend.position=c(0.2, 0.3),
        legend.title = element_blank()) +
       #geom_jitter() +
     
      annotate("segment", x = 2, xend = 91, y = 0.01, yend = 0.01,
                  colour = "gray90", linetype=1)+
      annotate("segment", x = 79, xend = 91, y = 0.01, yend = 0.04,
                  colour = "gray90", linetype=1)+
      annotate("segment", x = 91, xend = 110, y = 0.04, yend = 0.04,
                  colour = "gray90", linetype=1)+
      annotate("text", x = 45, y = 0.02, label = "Nutrients", size=3)+
      annotate("text", x = 98, y = 0.02, label = "Heat", size=3)+
  
    scale_y_continuous(breaks = seq(0, 0.4, 0.05),
                       #limits = c(0,0.5),
                       expand = c(0.01,0.01),
                   name=("Symbiont to host cell ratio  (S/H)")) +
    # scale_x_continuous(name="Days in the experiment",
    #                      limits = c(-2,113),
    #                      breaks = seq(0, 110, 15),  
    #                      expand = c(0, 0)) +
    scale_x_continuous(name="Days in the experiment",
                         limits = c(73,113),
                         breaks = seq(75, 110, 15),  
                         expand = c(0, 0)) +
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 2), width = 2 )+
    stat_summary(fun.y=mean, geom="point", size =2, alpha=0.8, 
                   position = position_dodge(width = 2)) +
    stat_summary(fun.y=mean, geom="line", 
                    position = position_dodge(width = 2))

Figure4b + facet_grid(~Survivorship)

#ggsave(file="Outputs/Fig_4_SH_Acer.svg", plot=Figure4, width=3.5, height=3)
```

* Raw data - Genotypes (Treatment pooled)

```{r}
 # NOT log 10
Figure4_g <- ggplot (qPCR.variables_2, aes(Days, A.Acer, colour=MoteGen)) + 
    ggthe_bw + ggtitle("(c)")+
    theme(legend.position="none",
        legend.title = element_blank()) +
       #geom_jitter(aes(colour=factor(Replicate))) +
     
        
      annotate("segment", x = 2, xend = 91, y = 0.01, yend = 0.01,
                  colour = "gray90", linetype=1)+
      annotate("segment", x = 79, xend = 91, y = 0.01, yend = 0.04,
                  colour = "gray90", linetype=1)+
      annotate("segment", x = 91, xend = 110, y = 0.04, yend = 0.04,
                  colour = "gray90", linetype=1)+
      annotate("text", x = 40, y = 0.02, label = "Nutrients", size=3)+
      annotate("text", x = 98, y = 0.02, label = "H", size=3)+
  
    scale_y_continuous(breaks = seq(0, 0.4, 0.1),
                       #limits = c(0,0.5),
                       expand = c(0.01,0.01),
                   name=("Symbiont to host cell ratio  (S/H)")) +
    scale_x_continuous(name="Days in the experiment",
                         limits = c(-2,113),
                         breaks = seq(0, 110, 30),  
                         expand = c(0.01, 0.01)) +
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 2), width = 2 )+
    stat_summary(fun.y=mean, geom="point", size =2, alpha=0.8, 
                   position = position_dodge(width = 2)) +
    stat_summary(fun.y=mean, geom="line", 
                    position = position_dodge(width = 2)) + facet_grid(~MoteGen)
Figure4_g

#ggsave(file="Outputs/Fig_S3_SH_Acer_Genet.svg", plot=Figure4_g, width=6.1, height=3.2)
```

* Raw data - by Treatment and genotype

```{r}
Figure4_gen<- ggplot (qPCR.variables_2, aes(Days, A.Acer , colour=Treatment,
                                          shape=Treatment)) + 
    ggthe_bw + Fill.colour+ 
    theme(legend.position="bottom",
       legend.title = element_blank()) +
        
      annotate("segment", x = 2, xend = 91, y = 0.01, yend = 0.01,
                  colour = "gray90", linetype=1)+
      annotate("segment", x = 79, xend = 91, y = 0.01, yend = 0.04,
                  colour = "gray90", linetype=1)+
      annotate("segment", x = 91, xend = 110, y = 0.04, yend = 0.04,
                  colour = "gray90", linetype=1)+
      annotate("text", x = 45, y = 0.02, label = "Nutrients", size=3)+
      annotate("text", x = 99, y = 0.02, label = "H", size=3)+
  
    # scale_y_continuous(breaks = seq(-2, -0.1, 0.25),
    #                    limits = c(-2, -0.1),
    #                    expand = c(0,0),
    #               name=("Symbiont to host cell ratio  - log 10(S/H)")) +
    scale_x_continuous(name="Days in the experiment",
                         limits = c(-2,113),
                         breaks = seq(0, 110, 30),  
                         expand = c(0, 0)) +
    stat_summary(fun.data = "mean_cl_boot", geom = "errorbar", width = 20, 
                    position = position_dodge(width = 2))+
    stat_summary(fun.y=mean, geom="point", size =2, alpha=0.5, 
                   position = position_dodge(width = 2)) +
    stat_summary(fun.y=mean, geom="line", 
                    position = position_dodge(width = 2))+
  facet_wrap(~MoteGen+Replicate)

Figure4_gen
#ggsave(file="Outputs/Fig_S3_SH_Acer_Genotype.svg", plot=Figure4_gen, width=6.1, height=3.5)
```

# 2. LMER models

## Baseline 

```{r}
LME_BaseLine<-lmer(logA.SH ~ Treatment + MoteGen + 
                     (1|Replicate) + (1|Survivorship), 
                     data=SH.0)
     step (LME_BaseLine) #  Treatement is not significant
     anova(LME_BaseLine)         
     ranova(LME_BaseLine) # Replicate is mariginally significant       
     
LME_BaseLine1<-lmer(logA.SH ~ MoteGen + (1|Replicate), 
                     data=SH.0)
    step (LME_BaseLine1) #  Treatement is not significant
    anova(LME_BaseLine1)         
    ranova(LME_BaseLine1) # Replicate is mariginally significant       
     

# Multicomp
    Acer.SH.0.emm<-emmeans(LME_BaseLine1, ~MoteGen)
      #contrast(Acer.SH.0.emm, "tukey")
    Acer.SH.0_groups<-cld(Acer.SH.0.emm, by=NULL) # compact-letter display
    Acer.SH.0_groups
  #write.csv(Acer.SH.0_groups, "Outputs/Multicomp_AcerSH_0.csv", row.names = F)
    
# Effect plot
  plot(emmeans(LME_BaseLine1, ~MoteGen), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + theme_bw()
```

* No differences among fragments asigned to each tratment. 
* Significant differences among genets

## C: Effect of nutrient treatments at control temperature 

```{r}
LME_Acer.C<-lmer(logA.SH ~ Treatment * Survivorship +
                   (1|Replicate) + (1|MoteGen), 
                     data=SH.C)
     step (LME_Acer.C) #  Treatement is ... almost significant?
     anova(LME_Acer.C)         
     ranova(LME_Acer.C) # Replicate is not       
```

* No differences among fragments asigned to replicate
* Sifferences among Treatments
* Significant differences among survivorship/genets

```{r}
# Treatment Model          
  LME_Acer.C1<-lmer(logA.SH ~ Treatment * Survivorship + (1|MoteGen), 
                       data=SH.C)
      anova(LME_Acer.C1)         
      ranova(LME_Acer.C1)
      
  # Multicomp
      Acer.SH.C.emm<-emmeans(LME_Acer.C1, ~Treatment* Survivorship)
        #contrast(Acer.SH.0.emm, "tukey")
      Acer.SH.C_groups<-cld(Acer.SH.C.emm, by=NULL) # compact-letter display
      Acer.SH.C_groups
    #write.csv(Acer.SH.C_groups, "Outputs/Multicomp_AcerSH_C.csv", row.names = F)
      
  # Effect plot
    plot(emmeans(LME_Acer.C1, ~Treatment* Survivorship), comparisons = TRUE) +
        coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + theme_bw()

```


```{r}
# Only Treatment    RAW DATA, NOT FOR STATS!

  LME_Acer.C1<-lmer(A.Acer ~ Treatment * Survivorship + (1|MoteGen), 
                       data=SH.C)
      anova(LME_Acer.C1)         
      ranova(LME_Acer.C1)
      
  # Multicomp
      Acer.SH.C.emm<-emmeans(LME_Acer.C1, ~Treatment)
        #contrast(Acer.SH.0.emm, "tukey")
      Acer.SH.C_groups<-cld(Acer.SH.C.emm, by=NULL) # compact-letter display
      Acer.SH.C_groups
    #write.csv(Acer.SH.C_groups, "Outputs/Multicomp_AcerSH_C.csv", row.names = F)
      
  # Effect plot
    plot(emmeans(LME_Acer.C1, ~Treatment), comparisons = TRUE) +
        coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + theme_bw()

```


```{r}
# Genet Model
  LME_Acer.C2<-lm(logA.SH ~ Treatment + MoteGen, 
                     data=SH.C)
    anova(LME_Acer.C2)         

    # Multicomp
    Acer.SH.C2.emm<-emmeans(LME_Acer.C2, ~MoteGen)
      #contrast(Acer.SH.0.emm, "tukey")
    Acer.SH.C2_groups<-cld(Acer.SH.C2.emm, by=NULL) # compact-letter display
    Acer.SH.C2_groups
    #write.csv(Acer.SH.C_groups, "Outputs/Multicomp_AcerSH_C.csv", row.names = F)
    
  # Effect plot
    plot(emmeans(LME_Acer.C2, ~MoteGen), comparisons = TRUE) +
        coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + theme_bw()

```

## H: Effect of pre-exposure to nutrient treatments during heat challenge
```{r}
LME_Acer.H<-lmer(logA.SH ~ Treatment * Survivorship + DaysF +
                   (1|Replicate) + (1|MoteGen), 
                     data=SH.H)
     step (LME_Acer.H) #  Treatement is ... almost significant?
     anova(LME_Acer.H)         
     ranova(LME_Acer.H) # Replicate is not   
```

```{r}
# Treatment model          
  LME_Acer.H<-lmer(A.Acer ~ Treatment * DaysF + (1|MoteGen), 
                       data=SH.H)
      step (LME_Acer.H)
      anova(LME_Acer.H)         
      ranova(LME_Acer.H)
  
  # Multicomp
    Acer.SH.H.emm<-emmeans(LME_Acer.H, ~Treatment* DaysF)
        #contrast(Acer.SH.0.emm, "tukey")
      Acer.SH.H_groups<-cld(Acer.SH.H.emm, by=NULL) # compact-letter display
      Acer.SH.H_groups<-Acer.SH.H_groups[order(
          Acer.SH.H_groups$DaysF,
          Acer.SH.H_groups$Treatment),]
      Acer.SH.H_groups
    #write.csv(Acer.SH.H_groups, "Outputs/Multicomp_AcerSH_H.csv", row.names = F)
      
  # Effect plot
    #plot(emmeans(LME_Acer.H, ~Treatment|DaysF), comparisons = TRUE) +
     #   coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + theme_bw()

```

```{r}
# Genet model          
  LME_Acer.H2<-lmer(logA.SH ~ Treatment * DaysF * Survivorship + (1|MoteGen), 
                       data=SH.H)
  
  LME_Acer.H2<-lm(logA.SH ~ Treatment + DaysF + MoteGen + Treatment:DaysF, 
                       data=SH.H)
      step (LME_Acer.H2)
      anova(LME_Acer.H2)         
  
  
  # Multicomp
  Acer.SH.H2.emm<-emmeans(LME_Acer.H2, ~ Treatment + DaysF + MoteGen + Treatment:DaysF)
        #contrast(Acer.SH.0.emm, "tukey")
      Acer.SH.H2_groups<-cld(Acer.SH.H2.emm, by=NULL) # compact-letter display
      Acer.SH.H2_groups<-Acer.SH.H2_groups[order(
          Acer.SH.H2_groups$Treatment,
          Acer.SH.H2_groups$DaysF,
          Acer.SH.H2_groups$MoteGen),]
      Acer.SH.H2_groups
    #write.csv(Acer.SH.H_groups, "Outputs/Multicomp_AcerSH_H.csv", row.names = F)
      
  # Effect plot
    #plot(emmeans(LME_Acer.H, ~Treatment|DaysF), comparisons = TRUE) +
     #   coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + theme_bw()

```

## All phases

* Day as factor

```{r}
LM_Acer.qpCR<-lmer (logA.SH ~ Treatment * DaysF +
                  (1|Replicate) + (1|Fragment/MoteGen), data= qPCR.variables_2)
  step(LM_Acer.qpCR)
  anova(LM_Acer.qpCR)
  ranova(LM_Acer.qpCR)

LM_Acer.qPCR2<-lmer(logA.SH ~Treatment * DaysF + (1|MoteGen),
                      data= qPCR.variables_2)
  step(LM_Acer.qPCR2)
  anova(LM_Acer.qPCR2)
  ranova(LM_Acer.qPCR2)

# Multicomp
Acer.SH.emm<-emmeans(LM_Acer.qPCR2, ~Treatment * DaysF)
      #contrast(Acer.SH.emm, "tukey")
      #pairs(Acer.SH.emm) # same than contrast(Acer.YII.emm, "tukey")
    Acer.SH_groups<-cld(Acer.SH.emm, by=NULL) # compact-letter display
    Acer.SH_groups<-Acer.SH_groups[order(Acer.SH_groups$Day, Acer.SH_groups$Treatment), ]
    Acer.SH_groups
#write.csv(Acer.SH_groups, "Outputs/Multicomp_AcerSH.csv", row.names = F)
      
      
# Effect plot options
emmip(LM_Acer.qPCR2, ~DaysF|Treatment, 
      CIs = TRUE, aes(Colony=factor(Treatment))) + theme_bw() # interaction plot of predictions
```

* By genotype

```{r}
LM_Acer.qpCR<-lmer (logA.SH ~ Treatment * MoteGen * DaysF +
                  (1|Replicate) + (1|Fragment), data= qPCR.variables_2)
step(LM_Acer.qpCR)
anova(LM_Acer.qpCR)
ranova(LM_Acer.qpCR)

LM_Acer.qPCR2<-lm(logA.SH ~Treatment * MoteGen * DaysF,
                      data= qPCR.variables_2)
step(LM_Acer.qPCR2)
anova(LM_Acer.qPCR2)

# Multicomp
Acer.SH.emm<-emmeans(LM_Acer.qPCR2, ~Treatment + DaysF)
      #contrast(Acer.SH.emm, "tukey")
      #pairs(Acer.SH.emm) # same than contrast(Acer.YII.emm, "tukey")
    Acer.SH_groups<-cld(Acer.SH.emm, by=NULL) # compact-letter display
    Acer.SH_groups<-Acer.SH_groups[order(Acer.SH_groups$Day, Acer.SH_groups$Treatment), ]
    Acer.SH_groups
#write.csv(Acer.SH_groups, "Outputs/Multicomp_AcerSH.csv", row.names = F)
      
      
# Effect plot options
emmip(LM_Acer.qPCR2, ~DaysF|Treatment|MoteGen, CIs = TRUE,  aes(colour=factor(Treatment))) + theme_bw() + facet_grid(MoteGen~Treatment)

```

# 3. Packages used

```{r}
# Creates bibliography 
#knitr::write_bib(c(.packages()), "packages.bib")
```
