---
title: "Changes in Symbiodiniaceae/cm2 and Chl-a/cm2 in elevated nutrients and heat stress"
author: "Ana Palacio"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    df_print: paged
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

# General project set-up 

```{r libraries, results="hide"}

# Load libraries and sources required to run the script
    library(tidyverse)
    library(plyr)
    library(ggthemes)
    library(gridExtra)
    library(lmerTest)
    library(emmeans)
    library(multcomp)
    library(multcompView)
    library(emmeans)
    library(effects)

# Default ggplot settings

    Fill.colour<-scale_colour_manual(values = c("black", "gray70", "gray35"))

    ggthe_bw<-theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black"),
          legend.title = element_blank()
          )+
    theme_bw()
```

# Read data and organize factors

```{r cars}
# Read data
  data<-read.csv("Data/data.csv")
  summary (data$Genotype)
  
# Organize factors  
  data$Rep <- as.factor(data$Rep)
  data$Date<-as.Date(data$Date, "%Y-%m-%d")
  data$Days<-(as.numeric(data$Date) -17485)
  data$DaysF<-(as.factor(data$Days))
  data$Treatment <- as.factor(data$Treatment)
  
  data$Community <- factor(data$Community, levels = c("A", "B", "C3", "C1", "D"))
  
  data$Days2<-data$Days-82
  data$Days2[data$Days2 == 31] <- "15"
  data$Days2<-as.numeric(data$Days2)
  
  summary (data)

# Remove the sick guy
  data <- data[!(data$Date == "2018-02-15"), ]

# Remove unbalanced genotypes
  data <- data[!(data$Genotype == "A.cer_Red and Yellow"), ]
  data <- data[!(data$Genotype == "A.cer_Yellow"), ]
  data <-droplevels(data)

# Chl by Symbiont
  data$Chl.Sym<-((data$Chl_a)/(data$Sym.cm2))
  summary(data$Genotype)

```


# All coral species

## Explore/Plots(s)

### Symbiodiniaceae areal densities 

```{r}
# Graphs to initially explore data
SymDen<- ggplot(data, aes(DaysF, Sym.cm2, colour=Treatment)) +
    #geom_jitter(aes(colour=factor(Treatment))) +
    geom_boxplot()+ Fill.colour+
    #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position = position_dodge(0.8))+
    ggthe_bw + facet_grid(Spp~., scales = "free_y" )
SymDen

Sym_Genotype<- ggplot(data, aes (Days, Sym.cm2, colour=Genotype)) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 1), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line") +   theme_gdocs()+
  geom_point(alpha=0.5) + facet_grid (Spp~Treatment, scales="free")
Sym_Genotype

Sym_Community<- ggplot(data, aes (Days, Sym.cm2, colour=Community)) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 1), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line") +   theme_gdocs()+
  geom_point(alpha=0.5) + facet_grid (Spp~Treatment, scales="free")
Sym_Community
```

```{r}

Sym_Treatment<- ggplot(data, aes (Days2, Sym.cm2, colour=Treatment,
                                   shape=Treatment)) + ggthe_bw +
  #geom_point(position = position_dodge(width = 8), shape=21)+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 8), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line", linetype=1, 
               position = position_dodge(width = 8)) + 
  stat_summary(fun.y=mean, geom="point", size=2,
               position = position_dodge(width = 8)) + 
  scale_x_continuous(breaks=c(82, 113)) + Fill.colour +
  scale_y_continuous(limits = c(0, 2.4),
                     breaks=seq(0, 2, by=0.5), 
   name="Symbiodiniaceae (106 cells / cm2)") 
  
#Sym_Treatment
Sym_CommunityB<-Sym_Treatment  +  facet_wrap (Spp~Community, scales="free_y")
Sym_CommunityB
Sym_Community<-Sym_Treatment  +  facet_wrap (Spp~Community)

# ggsave(file="Outputs/AllB_Acer_Ofav_Ssid_Blastateb.svg", Sym_CommunityB, width=6, height=5)


Sy.Summary <- plyr::ddply (data, . (Spp, Treatment, Days, Community),
              summarise,
              Sy_mean = mean (Sym.cm2, na.rm = T),
              Sy_sd = sd (Sym.cm2, na.rm = T))
Sy.Summary

```

### Chlorophyll-a

```{r}
Chl<-ggplot(data, aes(DaysF, Chl_a, colour=Treatment)) +
  #geom_jitter(aes(colour=factor(Treatment))) +
  geom_boxplot()+ Fill.colour+
  #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position = position_dodge(0.8))+
  ggthe_bw + facet_grid(Spp~., scales = "free_y" )
Chl

Chl_Treatment<- ggplot(data, aes (Days2, Chl_a, colour=Treatment,
                                  shape=Treatment)) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 8), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line", 
               position = position_dodge(width = 8)) + 
  stat_summary(fun.y=mean, geom="point", 
               position = position_dodge(width = 8)) + ggthe_bw + ylab("Chlorophyll-a (ug / cm2)") + 
  scale_x_continuous(breaks=c(82, 113)) + Fill.colour +
    facet_wrap (~Spp)
Chl_Treatment

Chl_TreatmentB<-Chl_Treatment  +  facet_wrap (Spp~Community)
Chl_TreatmentB

#ggsave(file="Outputs/AllB_Acer_Ofav_Ssid_Chla.svg", Chl_TreatmentB, width=6, height=5)

Chl.Summary <- plyr::ddply (data, . (Spp, Treatment, Days),
              summarise,
              Chl_mean = mean (Chl_a, na.rm = T),
              Chl_sd = sd (Chl_a, na.rm = T))
Chl.Summary

```

* Chlorophyll-a/Symbiodiniaceae cell

```{r}
Chl_Sym<-ggplot(data, aes(DaysF, Chl.Sym, colour=Treatment)) +
  #geom_jitter(aes(colour=factor(Treatment))) +
  geom_boxplot()+ Fill.colour+
  #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position = position_dodge(0.8))+
  ggthe_bw + facet_grid(Spp~., scales = "free_y" )
Chl_Sym

Chl_Sym_Treatment<- ggplot(data, aes (Days,Chl.Sym, colour=Treatment,
                                  shape=Treatment)) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 3), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line", 
               position = position_dodge(width = 3)) + 
  stat_summary(fun.y=mean, geom="point", 
               position = position_dodge(width = 3)) + ggthe_bw + ylab("Chlorophyll-a  / Symbiodiniaceae cell)") + 
  scale_x_continuous(breaks=c(82, 113)) + Fill.colour +
    facet_wrap (Spp~Community)
Chl_Sym_Treatment

Chl_Sym.Summary <- plyr::ddply (data, . (Spp, Treatment, Days),
              summarise,
              Chl_mean = mean (Chl_a, na.rm = T),
              Chl_sd = sd (Chl_a, na.rm = T))
Chl_Sym.Summary

```

## Test normality and transformation

```{r, fig.width=4, fig.height=4}
# Zoox.cm2
  shapiro.test(data$Sym.cm2) # Not normal
  ggplot() + geom_histogram(aes(x=Sym.cm2), data=data)
    shapiro.test(data$Sym.cm2) # Not normal

# Chl-a.cm2 
  shapiro.test(data$Chl_a) # Not normal
  ggplot() + geom_histogram(aes(x=Chl_a), data=data)
  
# Chl-a.Sym   
  shapiro.test(data$Chl.Sym) # Not normal
  ggplot() + geom_histogram(aes(x=Chl.Sym), data=data)

# Transformations 
    data$Zoox.sq<-sqrt(data$Sym.cm2)
    data$lnSym<- log(data$Sym.cm2)
    data$Chl.sq<-sqrt(data$Chl_a)
    data$Chl.Sym.sq<-sqrt(data$Chl.Sym)

# Normality again
  shapiro.test(data$Zoox.sq)# Still not Normal
  ggplot() + geom_histogram(aes(x=Zoox.sq), data=data)
  
  shapiro.test(data$lnSym)# Better, but still not Normal
  ggplot() + geom_histogram(aes(x=lnSym), data=data)
  
  
  shapiro.test(data$Chl.sq)# Normal
  ggplot() + geom_histogram(aes(x=Chl.sq), data=data)
  
  shapiro.test(data$Chl.Sym.sq) # Not normal
  ggplot() + geom_histogram(aes(x=Chl.Sym.sq), data=data)
```

## Models

### Symbionts

```{r}
LMER_Sym0<-lmer(Sym.cm2 ~ Treatment * Spp * DaysF + 
               (1|Rep) + (1|Spp/Genotype), REML=TRUE,
               data=data, na.action=na.omit)
  anova(LMER_Sym0)
  ranova(LMER_Sym0)
  step(LMER_Sym0)
  summary(LMER_Sym0)

LMER_Sym<-lmer(Sym.cm2 ~ Treatment * Spp * DaysF + 
               (1|Spp/Genotype), REML=TRUE,
               data=data, na.action=na.omit)
  anova(LMER_Sym)
  ranova(LMER_Sym)
  step((LMER_Sym))
  summary(LMER_Sym)

LMER_Sym2<-lmer(lnSym ~ Treatment * Spp * DaysF + 
                 (1|Spp/Genotype),REML=TRUE,
                data=data, na.action=na.omit)
  anova(LMER_Sym2)
  ranova(LMER_Sym2)
  step((LMER_Sym2))
  summary(LMER_Sym2)
```

* Spp have different sym/cm2 and interactions. Split data    

```{r}
Sym_All.Summary <- plyr::ddply (data, . (Spp, Community, Days, Treatment),
              summarise,
              Sym_mean = mean (Sym.cm2, na.rm = T),
              Sym_sd = sd (Sym.cm2, na.rm = T))
Sym_All.Summary

```

### Chla

```{r}

LMER_Chla0<-lmer(Chl.sq ~ Treatment * Spp * DaysF + 
                 (1|Rep) + (1|Spp/Genotype), 
                data=data, na.action=na.omit)
    anova(LMER_Chla0)
    ranova(LMER_Chla0)
    step(LMER_Chla0)
    summary(LMER_Chla0)

LMER_Chla<-lmer(Chl.sq ~ Treatment * Spp * DaysF + 
                + (1|Spp/Genotype), 
                data=data, na.action=na.omit)
    anova(LMER_Chla)
    ranova(LMER_Chla)
    step(LMER_Chla)
    summary(LMER_Chla)

```

```{r}
  Chl_a.Summary <- plyr::ddply (data, . (Spp, Days, Treatment),
              summarise,
              Chl_mean = mean (Chl_a, na.rm = T),
              Chl_sd = sd (Chl_a, na.rm = T))
  Chl_a.Summary
```

# Individual Spp

```{r}
# Subset data by species 

  Acer.data<-subset(data, Spp=="A.cer")
  Ofav.data<-subset(data, Spp=="O.fav")
  Ssid.data<-subset(data, Spp=="S.sid")
  Ofav_Ssid.data<-subset(data, Spp!="A.cer")
```


## 1. Acer

```{r}
  # Acer.data$Survivorship[Acer.data$Genotype=="G_48"|
  #                     Acer.data$Genotype=="G_62"|
  #                     Acer.data$Genotype=="G_31"]<-"Resistant"
  #     
  # Acer.data$Survivorship[Acer.data$Genotype=="G_08"|
  #                     Acer.data$Genotype=="G_07"|
  #                     Acer.data$Genotype=="G_50"]<-"Susceptible"
Acer.data<-droplevels(Acer.data)
summary(Acer.data)    


  Acer_Sy.Summary <- plyr::ddply (Acer.data, . (Treatment, Days),
              summarise,
              Sy_mean = mean (Sym.cm2, na.rm = T),
              Sy_sd = sd (Sym.cm2, na.rm = T))
  Acer_Sy.Summary
    
  Acer_Ch.Summary <- plyr::ddply (Acer.data, . (Treatment, Days),
              summarise,
              Sy_mean = mean (Chl_a, na.rm = T),
              Sy_sd = sd (Chl_a, na.rm = T))
  Acer_Ch.Summary
```

### Normality

* Symbiodiniaceae/ cm2 

```{r, fig.width=4, fig.height=4}
# Zoox.cm2
  shapiro.test(Acer.data$Sym.cm2) # Almost, but not normal
  #ggplot() + geom_histogram(aes(x=Sym.cm2), data=Acer.data)

  shapiro.test(Acer.data$Zoox.sq)# less Normal!!
  #ggplot() + geom_histogram(aes(x=Zoox.sq), data=Acer.data)

  shapiro.test(Acer.data$lnSym)# less Normal!!
  #ggplot() + geom_histogram(aes(x=lnSym), data=Acer.data)

```

Use raw Symbiodiniaceae/ cm2 data in models?

* Chl-a / cm2  

```{r, fig.width=4, fig.height=4}

# Chl-a.cm2 
  shapiro.test(Acer.data$Chl_a) # Normal
  #ggplot() + geom_histogram(aes(x=Chl_a), data=Acer.data)
  
  shapiro.test(Acer.data$Chl.sq)# Normal
  #ggplot() + geom_histogram(aes(x=Chl.sq), data=Acer.data)
```

### Graphs

* Symbiodiniaceae/ cm2 
```{r}
Acer_Genotype<- ggplot(Acer.data, aes (Days, Sym.cm2, colour=factor(Genotype))) +
  ggthe_bw +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 1), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line") +   theme_gdocs()+
  geom_point(alpha=0.5) + facet_grid (Spp~Treatment, scales="free")
Acer_Genotype + facet_grid(~Treatment)

```


```{r}
AcerSym_Treatment<- ggplot(Acer.data, aes (Days, Sym.cm2, colour=Treatment,
                                   shape=Treatment)) + ggthe_bw +
    theme(legend.position = c(0.7, 0.8))+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 3), width = 2 )+
  stat_summary(fun.y=mean, geom="line", 
               position = position_dodge(width = 3)) + 
  stat_summary(fun.y=mean, geom="point",
               position = position_dodge(width = 3)) + 
    scale_x_continuous(breaks=c(82, 113)) + Fill.colour +   
    ylab("Symbiodiniaceae (106 cells / cm2)") +
  ggtitle("(a)")
AcerSym_Treatment
```

* Chl-a/ cm2 

```{r}
AcerChl_Treatment<- ggplot(Acer.data, aes (Days, Chl_a, colour=Treatment,
                                   shape=Treatment)) + ggthe_bw +
  theme(legend.position = c(0.7, 0.8))+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 3), width = 2 )+
  stat_summary(fun.y=mean, geom="line", 
               position = position_dodge(width = 3)) + 
  stat_summary(fun.y=mean, geom="point",
               position = position_dodge(width = 3)) + 
    scale_x_continuous(breaks=c(82, 113)) + Fill.colour +   
    ylab("Chlorophyll-a (ug / cm2)")+
  ggtitle("(b)")
AcerChl_Treatment
```


```{r}
#grid.arrange(AcerSym_Treatment, AcerChl_Treatment, ncol=2, nrow=1)

#ggsave(file="Outputs/Acer_Blastate.svg", plot=grid.arrange(AcerSym_Treatment,AcerChl_Treatment,ncol=2,nrow=1), width=3.5, height=3)

#ggsave(file="Outputs/Fig_4_SH_Acer.svg", plot=Figure4, width=3.5, height=3)
```


### Models

#### Before and after heat stress

* Symbiodiniaceae/ cm2 

```{r}
# Sym
LMER_Sym_Acer<-lmer(Sym.cm2 ~ Treatment * DaysF + 
                 (1|Rep) + (1|Genotype), data=Acer.data, 
                 na.action = na.omit)
    anova(LMER_Sym_Acer)
    ranova(LMER_Sym_Acer)
    step(LMER_Sym_Acer)

LMER_Sym_Acer2<-lmer(Sym.cm2 ~ Treatment * DaysF + 
                 (1|Genotype), data=Acer.data, na.action = na.omit)
    anova(LMER_Sym_Acer2)
    ranova(LMER_Sym_Acer2)
    step(LMER_Sym_Acer2)
    
LMER_Sym_Acer3<-lm(Sym.cm2 ~ Treatment * DaysF,
                 data=Acer.data,  na.action = na.omit)
    anova(LMER_Sym_Acer3)
    step(LMER_Sym_Acer3)
    summary(LMER_Sym_Acer3)
```

```{r}
# Multicomp
    Acer.Sym.emm<-emmeans(LMER_Sym_Acer3, ~Treatment | DaysF)
     contrast(Acer.Sym.emm, "tukey")
    Acer.Sym.Group<-cld(Acer.Sym.emm, by=NULL) # compact-letter display
    
    Acer.Sym.Group<-Acer.Sym.Group[order(
          Acer.Sym.Group$DaysF,
          Acer.Sym.Group$Treatment),]
    Acer.Sym.Group

  # write.csv(Acer.Sym.Group, "Outputs/Multicomp_AcerSymCm2.csv", row.names = F)
    
```

* Chl a 

```{r}
# Chl-a
    
LMER_Chla_Acer<-lmer(Chl_a ~ Treatment * DaysF + 
                 (1|Rep) + (1|Genotype), data=Acer.data)
    anova(LMER_Chla_Acer)
    ranova(LMER_Chla_Acer)
    #step(LMER_Chla_Acer)

LMER_Chla_Acer3<-lm(Chl_a ~ DaysF * Treatment, data=Acer.data)
    anova(LMER_Chla_Acer3)
    #ranova(LMER_Chla_Acer3)
    step(LMER_Chla_Acer3)
    summary(LMER_Chla_Acer3)
# Nutrient treatment is not significant, temperature treatment is. However, data is not balanced (there is not N_Day113 data). Evaluate Day82 alone for nutrient effect?
```

```{r}
# Multicomp
    Acer.Chla.emm<-emmeans(LMER_Chla_Acer3, ~Treatment | DaysF)
    contrast(Acer.Chla.emm, "tukey")
    contrast(Acer.Chla.emm,by=c("Treatment"),method='pairwise')
    #pairs(Acer.Chla.emm)
    pwpp(Acer.Chla.emm)
    
    Acer.Chla.Groups<-cld(Acer.Chla.emm, by=NULL) # compact-letter display
    Acer.Chla.Groups<-Acer.Chla.Groups[order(
          Acer.Chla.Groups$DaysF,
          Acer.Chla.Groups$Treatment),]
    Acer.Chla.Groups
    #write.csv(Acer.Chla.Groups, "Outputs/Multicomp_AcerChla.csv", row.names = F)
    
```

#### Before heat 

```{r}
Acer.nutrients<-subset(Acer.data, DaysF=="82")
Acer.nutrients<-droplevels(Acer.nutrients)
summary(Acer.nutrients)
```

* Data summary 

```{r}
  Sym_82.Summary <- plyr::ddply (Acer.nutrients, . (Treatment),
              summarise,
              Sym_mean = mean (Sym.cm2, na.rm = T),
              Sym_sd = sd (Sym.cm2, na.rm = T))
  Sym_82.Summary

  Chl_a.Summary <- plyr::ddply (Acer.nutrients, . (Treatment),
              summarise,
              Chl_mean = mean (Chl_a, na.rm = T),
              Chl_sd = sd (Chl_a, na.rm = T))
  Sym_82.Summary
```

* Variable distribution 

```{r, fig.width=4, fig.height=4}

# Zoox.cm2
  shapiro.test(Acer.nutrients$Sym.cm2) # Not normal
  ggplot() + geom_histogram(aes(x=Sym.cm2), data=Acer.nutrients)

  shapiro.test(Acer.nutrients$Zoox.sq)# more Normal
  ggplot() + geom_histogram(aes(x=Zoox.sq), data=Acer.nutrients)

  shapiro.test(Acer.nutrients$lnSym)# best option
  ggplot() + geom_histogram(aes(x=lnSym), data=Acer.nutrients)
  
# Chl-a.cm2 
  shapiro.test(Acer.nutrients$Chl_a) # Not normal
  ggplot() + geom_histogram(aes(x=Chl_a), data=Acer.nutrients)
  
  shapiro.test(Acer.nutrients$Chl.sq)# Normal
  ggplot() + geom_histogram(aes(x=Chl.sq), data=Acer.nutrients)

```

* Symbiont models

```{r}
# Sym
LMER_Sym_Acer4<-lmer(Sym.cm2 ~ Treatment +
                 (1|Rep) + (1|Genotype), data=Acer.nutrients)
    anova(LMER_Sym_Acer4)
    ranova(LMER_Sym_Acer4)
    #step(LMER_Sym_Acer4)

LMER_Sym_Acer5<-lmer(Sym.cm2 ~ Treatment + 
                 (1|Genotype), data=Acer.nutrients)
    anova(LMER_Sym_Acer5)
    ranova(LMER_Sym_Acer5)
    #step(LMER_Sym_Acer5)
    
LMER_Sym_Acer6<-lmer(lnSym ~ Treatment + 
                  (1|Rep) + (1|Genotype), data=Acer.nutrients,
                  na.action=na.omit)
    anova(LMER_Sym_Acer6)
    ranova(LMER_Sym_Acer6)
    #step(LMER_Sym_Acer6)
    summary(LMER_Sym_Acer6)

LMER_Sym_Acer6<-lm(lnSym ~ Treatment, data=Acer.nutrients,
                  na.action=na.omit)
    anova(LMER_Sym_Acer6)
    step(LMER_Sym_Acer6)
    summary(LMER_Sym_Acer6)
    
    Sym.emm<-emmeans(LMER_Sym_Acer6, ~Treatment)
    contrast(Sym.emm, "tukey")
    # Effect plot options
    emmip(LMER_Sym_Acer6, ~Treatment, CIs = TRUE) + theme_bw() 

    LMER_Sym_Acer7<-lm(Sym.cm2 ~ Treatment,
                data=Acer.nutrients, na.action=na.omit)
    anova(LMER_Sym_Acer7)
    summary(LMER_Sym_Acer7)
   
    Sym.emm<-emmeans(LMER_Sym_Acer7, ~Treatment)
    contrast(Sym.emm, "tukey")
    # Effect plot options
    emmip(LMER_Sym_Acer7, ~Treatment, CIs = TRUE) + theme_bw() 

```

There are no treatment differences during C

* Chl-a

```{r}
# Chl-a
    
LMER_Chla_Acer<-lmer(Chl_a ~ Treatment + 
                 (1|Rep) + (1|Genotype), data=Acer.nutrients)
    anova(LMER_Chla_Acer)
    ranova(LMER_Chla_Acer)
    #step(LMER_Chla_Acer)

LMER_Chla_Acer2<-lm(Chl_a ~ Treatment, data=Acer.nutrients)
    anova(LMER_Chla_Acer2)
    step(LMER_Chla_Acer2)
    summary(LMER_Sym_Acer7)
   
    Chl.emm<-emmeans(LMER_Chla_Acer2, ~Treatment)
    contrast(Chl.emm, "tukey")
    # Effect plot options
    emmip(LMER_Chla_Acer2, ~Treatment, CIs = TRUE) + theme_bw() 
    Acer.Chl.Group<-cld(Chl.emm, by=NULL) # compact-letter display
    
    
LMER_Chla_Acer3<-lmer(Chl.sq ~ Treatment + 
                 (1|Rep) + (1|Genotype), data=Acer.nutrients)
    anova(LMER_Chla_Acer3)
    ranova(LMER_Chla_Acer3)
    #step(LMER_Chla_Acer3)

LMER_Chla_Acer4<-lm(Chl.sq ~ Treatment, data=Acer.nutrients)
    anova(LMER_Chla_Acer4)
    summary(LMER_Chla_Acer4)
   
    Chl.emm<-emmeans(LMER_Chla_Acer4, ~Treatment)
    contrast(Chl.emm, "tukey")
    # Effect plot options
    emmip(LMER_Chla_Acer4, ~Treatment, CIs = TRUE) + theme_bw() 
```

There are treatment differences during C between  A and N. Not very strong between A and N+P

## 2. Ofav - Ssid 

### Plots(s)

* Symbiodiniaceae

```{r}
# Graphs to initially explore data

Sym_Treatment2<- ggplot(Ofav_Ssid.data, aes (Days, Sym.cm2, colour=Treatment,
                                   shape=Treatment)) + ggthe_bw +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 3), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line", 
               position = position_dodge(width = 3)) + 
  stat_summary(fun.y=mean, geom="point",
               position = position_dodge(width = 3)) + 
    scale_x_continuous(breaks=c(82, 113)) + Fill.colour +   
  facet_wrap (~Spp, scales="free_y") +  ggtitle("(a)")+
  ylab("Symbiodiniaceae (106 cells / cm2)")+
  theme(legend.position = c(.85, .78))+
   annotate("text", x = 84, y = 0.08, label = "(C)", size=3, colour="gray")+
   annotate("text", x = 110, y = 0.08, label = "(H)", size=3, colour="gray")
Sym_Treatment2
Sym_Treatment2+facet_wrap(Spp~Community)

```

* Chlorophyll-a

```{r}

Chl_Treatment2<- ggplot(Ofav_Ssid.data, aes (Days, Chl_a, colour=Treatment,
                                  shape=Treatment)) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 3), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line", 
               position = position_dodge(width = 3)) + 
  stat_summary(fun.y=mean, geom="point", 
               position = position_dodge(width = 3)) + ggthe_bw + ylab("Chlorophyll-a (ug / cm2)") + 
  scale_x_continuous(breaks=c(82, 113)) + Fill.colour +
    facet_wrap (~Spp) +  ggtitle("(b)") +
  theme(legend.position = c(.85, .78))+
  annotate("text", x = 84, y = 0.08, label = "(C)", size=3, colour="gray")+
   annotate("text", x = 110, y = 0.08, label = "(H)", size=3, colour="gray")
Chl_Treatment2
Chl_Treatment2 + facet_wrap(Spp~Community)
```


```{r}
#ggsave(file="Outputs/Ofav_Ssid_Blastate.svg", plot=grid.arrange(Sym_Treatment2,Chl_Treatment2,ncol=1, nrow=2), 
      # width=4, height=5.5)
```


### 2.1 Ofav 

```{r}
Ofav.data<-droplevels(Ofav.data)
summary(Ofav.data) 
  
Ofav_Sy.Summary <- plyr::ddply (Ofav.data, . (Community, Treatment, Days),
              summarise,
              Sy_mean = mean (Sym.cm2, na.rm = T),
              Sy_sd = sd (Sym.cm2, na.rm = T))
  Ofav_Sy.Summary
    
Ofav_Ch.Summary <- plyr::ddply (Ofav.data, . (Treatment, Community, Days),
              summarise,
              Sy_mean = mean (Chl_a, na.rm = T),
              Sy_sd = sd (Chl_a, na.rm = T))
  Ofav_Ch.Summary
```

#### Normality

* Symbiodiniaceae/ cm2 

```{r, fig.width=4, fig.height=4}
# Zoox.cm2
  shapiro.test(Ofav.data$Sym.cm2) # Normal
  #ggplot() + geom_histogram(aes(x=Sym.cm2), data=Ofav.data)

  shapiro.test(Ofav.data$Zoox.sq)# Normal!!> Better option?
  #ggplot() + geom_histogram(aes(x=Zoox.sq), data=Ofav.data)

  shapiro.test(Ofav.data$lnSym)# Good!!
  #ggplot() + geom_histogram(aes(x=lnSym), data=Ofav.data)

```

Use Zoox.sq in models

* Chl-a / cm2  

```{r, fig.width=4, fig.height=4}

# Chl-a.cm2 
  shapiro.test(Ofav.data$Chl_a) # Normal
  #ggplot() + geom_histogram(aes(x=Chl_a), data=Ofav.data)
  
  shapiro.test(Ofav.data$Chl.sq)# Normal
  #ggplot() + geom_histogram(aes(x=Chl.sq), data=Ofav.data)
```

#### Models

##### Before and after heat stress

* Symbiodiniaceae/ cm2 

```{r}
# Sym
LMER_Sym_Ofav<-lmer(Zoox.sq ~ Treatment * DaysF * Community + 
                 (1|Rep) + (1|Genotype), data=Ofav.data, 
                 na.action = na.omit)
    anova(LMER_Sym_Ofav)
    ranova(LMER_Sym_Ofav)
    step(LMER_Sym_Ofav)

LMER_Sym_Ofav2<-lmer(Zoox.sq ~ Treatment * DaysF + 
                 (1|Genotype), data=Ofav.data, na.action = na.omit)
    anova(LMER_Sym_Ofav2)
    ranova(LMER_Sym_Ofav2)
    step(LMER_Sym_Ofav2)
    
LMER_Sym_Ofav3<-lm(Zoox.sq ~ Treatment * DaysF,
                 data=Ofav.data,  na.action = na.omit)
    anova(LMER_Sym_Ofav3)
    step(LMER_Sym_Ofav3)
    summary(LMER_Sym_Ofav3)
```

```{r}
# Multicomp
    Ofav.Sym.emm<-emmeans(LMER_Sym_Ofav2, ~Treatment|DaysF)
      contrast(Ofav.Sym.emm, "tukey")
    Ofav.Sym.Group<-cld(Ofav.Sym.emm, by=NULL) # compact-letter display
    
    Ofav.Sym.Group<-Ofav.Sym.Group[order(
          Ofav.Sym.Group$DaysF,
          Ofav.Sym.Group$Treatment),]
    Ofav.Sym.Group

  # write.csv(Ofav.Sym.Group, "Outputs/Multicomp_OfavSymCm2.csv", row.names = F)
```

* Chl a 

```{r}
LMER_Chla_Ofav<-lmer(Chl_a ~ Treatment * DaysF * Community + 
                 (1|Rep) + (1|Genotype), data=Ofav.data)
    anova(LMER_Chla_Ofav)
    ranova(LMER_Chla_Ofav)
    step(LMER_Chla_Ofav)

LMER_Chla_Ofav2<-lmer(Chl_a ~ Treatment * DaysF + 
                 (1|Genotype), data=Ofav.data)
    anova(LMER_Chla_Ofav2)
    ranova(LMER_Chla_Ofav2)
    step(LMER_Chla_Ofav2)
```

```{r}
# Multicomp
  Ofav.Chla.emm<-emmeans(LMER_Chla_Ofav2, ~Treatment | DaysF)
    contrast(Ofav.Chla.emm, "tukey")
  
    Ofav.Chla.Groups<-cld(Ofav.Chla.emm, by=NULL) # compact-letter display
    Ofav.Chla.Groups<-Ofav.Chla.Groups[order(
          Ofav.Chla.Groups$DaysF,
          Ofav.Chla.Groups$Treatment),]
      Ofav.Chla.Groups
#write.csv(Ofav.Chla.Groups, "Outputs/Multicomp_OfavChla.csv", row.names = F)
    
```


##### Before heat stress

```{r}
Ofav.nutrients<-subset(Ofav.data, DaysF=="82")
Ofav.nutrients<-droplevels(Ofav.nutrients)
summary(Ofav.nutrients)

```

* Symbiodiniaceae/ cm2 

```{r}
# Sym
LMER_Sym_Ofav<-lmer(Zoox.sq ~ Treatment * Genotype + 
                 (1|Rep), data=Ofav.nutrients, 
                 na.action = na.omit)
    anova(LMER_Sym_Ofav)
    ranova(LMER_Sym_Ofav)
   # step(LMER_Sym_Ofav)

LMER_Sym_Ofav2.1<-lm(Zoox.sq ~ Genotype,
                    data=Ofav.nutrients, na.action = na.omit)
    anova(LMER_Sym_Ofav2.1)
    step(LMER_Sym_Ofav2.1)
    
```

No treatment differences, but these are the genotype differences: 

```{r}
# Multicomp
    Ofav.Sym.emm<-emmeans(LMER_Sym_Ofav2.1, ~Genotype)
      #contrast(Ofav.Sym.emm, "tukey")
    Ofav.Sym.Group<-cld(Ofav.Sym.emm, by=NULL) # compact-letter display
    
    # Ofav.Sym.Group<-Ofav.Sym.Group[order(
    #       Ofav.Sym.Group$Treatment),]
    Ofav.Sym.Group

  # write.csv(Ofav.Sym.Group, "Outputs/Multicomp_OfavSymCm2.csv", row.names = F)
```

* Chl a 

```{r}
LMER_Chla_Ofav<-lmer(Chl_a ~ Treatment * Community+ 
                 (1|Rep) + (1|Genotype), data=Ofav.nutrients)
    anova(LMER_Chla_Ofav)
    ranova(LMER_Chla_Ofav)
    step(LMER_Chla_Ofav)

LMER_Chla_Ofav2<-lmer(Chl_a ~ Treatment + 
                 (1|Genotype), data=Ofav.nutrients)
    anova(LMER_Chla_Ofav2)
    ranova(LMER_Chla_Ofav2)
    step(LMER_Chla_Ofav2)
```

```{r}
# Multicomp
  Ofav.Chla.emm<-emmeans(LMER_Chla_Ofav2, ~Treatment)
    contrast(Ofav.Chla.emm, "tukey")
  
    Ofav.Chla.Groups<-cld(Ofav.Chla.emm, by=NULL) # compact-letter display
    Ofav.Chla.Groups<-Ofav.Chla.Groups[order(
         Ofav.Chla.Groups$Treatment),]
      Ofav.Chla.Groups
  #write.csv(Ofav.Chla.Groups, "Outputs/Multicomp_OfavChla.csv", row.names = F)
```

### 2.2 Ssid 

```{r}
Ssid.data<-droplevels(Ssid.data)
summary(Ssid.data) 

Ssid_Sy.Summary <- plyr::ddply (Ssid.data, . (Days, Community, Treatment),
              summarise,
              Sy_mean = mean (Sym.cm2, na.rm = T),
              Sy_sd = sd (Sym.cm2, na.rm = T))
Ssid_Sy.Summary
    
Ssid_Ch.Summary <- plyr::ddply (Ssid.data, . (Days, Community, Treatment),
              summarise,
              Sy_mean = mean (Chl_a, na.rm = T),
              Sy_sd = sd (Chl_a, na.rm = T))
Ssid_Ch.Summary
```


**Community and nutrients**

* Symbiodiniaceae

```{r}
# Graphs to initially explore data

Sym_Treatment3<- ggplot(Ssid.data, aes (Days, Sym.cm2, colour=Treatment,
                                   shape=Treatment)) + ggthe_bw +
  # geom_jitter()+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 3), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line", 
               position = position_dodge(width = 3)) + 
  stat_summary(fun.y=mean, geom="point",
               position = position_dodge(width = 3)) + 
    scale_x_continuous(breaks=c(82, 113)) + Fill.colour +   
  facet_wrap (~Spp, scales="free_y") +  ggtitle("(a)")+
  ylab("Symbiodiniaceae (106 cells / cm2)")+
  theme(legend.position = c(.85, .78))+
   annotate("text", x = 84, y = 0.08, label = "(C)", size=3, colour="gray")+
   annotate("text", x = 110, y = 0.08, label = "(H)", size=3, colour="gray") +
  facet_wrap(~Community)
#Sym_Treatment3

```

* Chlorophyll-a

```{r}

Chl_Treatment3<- ggplot(Ssid.data, aes (Days, Chl_a, colour=Treatment,
                                  shape=Treatment)) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 3), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line", 
               position = position_dodge(width = 3)) + 
  stat_summary(fun.y=mean, geom="point", 
               position = position_dodge(width = 3)) + ggthe_bw + ylab("Chlorophyll-a (ug / cm2)") + 
  scale_x_continuous(breaks=c(82, 113)) + Fill.colour +
    facet_wrap (~Spp) +  ggtitle("(b)") +
  theme(legend.position = c(.85, .78))+
  annotate("text", x = 84, y = 0.08, label = "(C)", size=3, colour="gray")+
   annotate("text", x = 110, y = 0.08, label = "(H)", size=3, colour="gray")+
  facet_wrap(~Community)
#Chl_Treatment3 

```

```{r}
grid.arrange(Sym_Treatment3,Chl_Treatment3,ncol=1, nrow=2)
#ggsave(file="Outputs/Ssid_Blastate_Community.svg", plot=grid.arrange(Sym_Treatment3,Chl_Treatment3,ncol=1, nrow=2), width=4.5, height=5.5)

```

**Only Community**

* Symbiodiniaceae

```{r}
# Graphs to initially explore data

Sym_Treatment4<- ggplot(Ssid.data, aes (Days, Sym.cm2, colour=Community,
                                   shape=Community)) + ggthe_bw +
  # geom_jitter()+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 3), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line", 
               position = position_dodge(width = 3)) + 
  stat_summary(fun.y=mean, geom="point",
               position = position_dodge(width = 3)) + 
    scale_x_continuous(breaks=c(82, 113)) + ggtitle("(a)")+
  ylab("Symbiodiniaceae (106 cells / cm2)")+
  theme(legend.position = c(.85, .78))+
   annotate("text", x = 84, y = 0.08, label = "(C)", size=3, colour="gray")+
   annotate("text", x = 110, y = 0.08, label = "(H)", size=3, colour="gray")
#Sym_Treatment4

```

* Chlorophyll-a

```{r}

Chl_Treatment4<- ggplot(Ssid.data, aes (Days, Chl_a, colour=Community,
                                   shape=Community)) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
               position = position_dodge(width = 3), width = 0.2 )+
  stat_summary(fun.y=mean, geom="line", 
               position = position_dodge(width = 3)) + 
  stat_summary(fun.y=mean, geom="point", 
               position = position_dodge(width = 3)) + ggthe_bw + ylab("Chlorophyll-a (ug / cm2)") + 
  scale_x_continuous(breaks=c(82, 113)) + ggtitle("(b)") +
  theme(legend.position = c(.85, .78))+
  annotate("text", x = 84, y = 0.08, label = "(C)", size=3, colour="gray")+
   annotate("text", x = 110, y = 0.08, label = "(H)", size=3, colour="gray")
#Chl_Treatment4

```

```{r}
grid.arrange(Sym_Treatment4,Chl_Treatment4, ncol=2, nrow=1)
#ggsave(file="Outputs/Ssid_Blastate_OnlyCommunity.svg", plot=grid.arrange(Sym_Treatment4,Chl_Treatment4, ncol=2, nrow=1), width=5.0, height=3)

```

#### Normality

* Symbiodiniaceae/ cm2 

```{r}
# Zoox.cm2
  shapiro.test(Ssid.data$Sym.cm2) # Not normal
  #ggplot() + geom_histogram(aes(x=Sym.cm2), data=Ssid.data)

  shapiro.test(Ssid.data$Zoox.sq)# Better option?
  #ggplot() + geom_histogram(aes(x=Zoox.sq), data=Ssid.data)

  shapiro.test(Ssid.data$lnSym)# less Normal!!
  #ggplot() + geom_histogram(aes(x=lnSym), data=Ssid.data)

```

Use Zoox.sq in models

* Chl-a / cm2  

```{r}
# Chl-a.cm2 
  shapiro.test(Ssid.data$Chl_a) # Not normal
  #ggplot() + geom_histogram(aes(x=Chl_a), data=Ssid.data)
  
  shapiro.test(Ssid.data$Chl.sq)# Normal
  #ggplot() + geom_histogram(aes(x=Chl.sq), data=Ssid.data)
```

#### Models

##### Before and after heat stress

* Symbiodiniaceae/ cm2 

```{r}
# Sym
LMER_Sym_Ssid<-lmer(Zoox.sq ~ Treatment * DaysF * Community + 
                 (1|Rep) + (1|Genotype), data=Ssid.data, 
                 na.action = na.omit)
    anova(LMER_Sym_Ssid)
    ranova(LMER_Sym_Ssid)
    step(LMER_Sym_Ssid)

LMER_Sym_Ssid2<-lmer(Sym.cm2 ~ Treatment + DaysF + Community +
                       (1 | Genotype) + DaysF:Community,
                     data=Ssid.data, na.action = na.omit)
    anova(LMER_Sym_Ssid2)
    ranova(LMER_Sym_Ssid2)
    #step(LMER_Sym_Ssid2)
    
LMER_Sym_Ssid3<-lmer(Zoox.sq ~ Treatment + DaysF +
                       (1 | Genotype) + DaysF:Community,
                     data=Ssid.data, na.action = na.omit)
    anova(LMER_Sym_Ssid3)
    ranova(LMER_Sym_Ssid3)
    step(LMER_Sym_Ssid3)
    
```

```{r}
# Multicomp
    Ssid.Sym.emm<-emmeans(LMER_Sym_Ssid3, ~Community | Treatment|DaysF)
    #Ssid.Sym.emm<-emmeans(LMER_Sym_Ssid3, ~Treatment | Community | DaysF)
      contrast(Ssid.Sym.emm, "tukey")
    Ssid.Sym.Group<-cld(Ssid.Sym.emm, by=NULL) # compact-letter display
    
    Ssid.Sym.Group<-Ssid.Sym.Group[order(
          Ssid.Sym.Group$DaysF),]
    Ssid.Sym.Group

  # write.csv(Ssid.Sym.Group, "Outputs/Multicomp_SsidSymCm2_Only_Clade.csv", row.names = F)
    
```

* Chl a 

```{r}
# Chl-a
    
LMER_Chla_Ssid<-lmer(Chl.sq ~ Treatment * DaysF * Community + 
                       (1|Rep) + 
                       (1|Genotype), data=Ssid.data)
    anova(LMER_Chla_Ssid)
    ranova(LMER_Chla_Ssid)
    step(LMER_Chla_Ssid)

LMER_Chla_Ssid2<-lmer(Chl_a ~ Treatment + DaysF + Community + 
                        (1 |Genotype) + 
                        (1|Rep) +
                        DaysF:Community, data=Ssid.data)
    anova(LMER_Chla_Ssid2)
    ranova(LMER_Chla_Ssid2)
    step(LMER_Chla_Ssid2)
    
```

```{r}
# Multicomp
  Ssid.Chla.emm<-emmeans(LMER_Chla_Ssid2, ~Treatment|Community|DaysF)
    contrast(Ssid.Chla.emm, "tukey")
    pwpp(Ssid.Chla.emm)+facet_wrap
    
  Ssid.Chla.emm<-emmeans(LMER_Chla_Ssid2, ~Community|Treatment|DaysF)
    contrast(Ssid.Chla.emm, "tukey")
    pwpp(Ssid.Chla.emm)
  
    Ssid.Chla.Groups<-cld(Ssid.Chla.emm, by=NULL) # compact-letter display
    Ssid.Chla.Groups<-Ssid.Chla.Groups[order(
          Ssid.Chla.Groups$DaysF,
          Ssid.Chla.Groups$Treatment,
          Ssid.Chla.Groups$Community),]
    Ssid.Chla.Groups
    
    Ssid.Chla.Groups<-Ssid.Chla.Groups[order(
          Ssid.Chla.Groups$DaysF,
          Ssid.Chla.Groups$Community),]
    Ssid.Chla.Groups
  #write.csv(Ssid.Chla.Groups, "Outputs/Multicomp_SsidChla_clade.csv", row.names = F)
    
```

##### Before heat stress

```{r}
Ssid.nutrients<-subset(Ssid.data, DaysF=="82")
Ssid.nutrients<-(droplevels(Ssid.nutrients))
#summary(Ssid.nutrients)
```


```{r}
# Sym Model
LMER_Sym_Ssid.1<-lmer(Zoox.sq ~ Treatment * Community + 
                 (1|Rep) + (1|Genotype), data=Ssid.nutrients, 
                 na.action = na.omit)
    anova(LMER_Sym_Ssid.1)
    ranova(LMER_Sym_Ssid.1)
    #step(LMER_Sym_Ssid.1)

LMER_Sym_Ssid2.1<-lm(Zoox.sq ~ Community,
                     data=Ssid.nutrients, na.action = na.omit)
    anova(LMER_Sym_Ssid2.1)

```

```{r}
# Multicomp
    Ssid.Sym.emm<-emmeans(LMER_Sym_Ssid2.1, ~Community)
      #contrast(Ssid.Sym.emm, "tukey")
    Ssid.Sym.Group<-cld(Ssid.Sym.emm, by=NULL) # compact-letter display
    
    Ssid.Sym.Group<-Ssid.Sym.Group[order(
          Ssid.Sym.Group$Community),]
    Ssid.Sym.Group

  # write.csv(Ssid.Sym.Group, "Outputs/Multicomp_SsidSymCm2_Clade.csv", row.names = F)
    
```

* Chl a 

```{r}
# Chl-a
    
LMER_Chla_Ssid.C<-lmer(Chl_a ~ Treatment * Community + 
                 (1|Rep) + (1|Genotype), data=Ssid.nutrients)
    anova(LMER_Chla_Ssid.C)
    ranova(LMER_Chla_Ssid.C)
    step(LMER_Chla_Ssid.C)

LMER_Chla_Ssid.C2<-lmer(Chl_a ~ Treatment + Community +
                      (1 | Genotype), data=Ssid.nutrients)
    anova(LMER_Chla_Ssid.C2)
    ranova(LMER_Chla_Ssid.C2)
    step(LMER_Chla_Ssid.C2)
    
```

```{r}
# Multicomp
  Ssid.ChlaC.emm<-emmeans(LMER_Chla_Ssid.C2, ~Treatment|Community)
    contrast(Ssid.ChlaC.emm, "tukey")
  
    Ssid.ChlaC.Groups<-cld(Ssid.ChlaC.emm, by=NULL) # compact-letter display
    Ssid.ChlaC.Groups<-Ssid.ChlaC.Groups[order(
          Ssid.ChlaC.Groups$Treatment),]
    Ssid.ChlaC.Groups
  #write.csv(Ssid.Chla.Groups, "Outputs/Multicomp_SsidChla_clade.csv", row.names = F)
    
```


