---
title: "SH cell ratio Ssid_Nutrients"
author: "Ana Palacio"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    df_print: paged
    theme: united
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE,}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

General project set-up 

```{r libraries , results="hide"}
# Get all libraries and sources required to run the script
        library(steponeR)
        library(plyr)
        library(dplyr)
        library(reshape2)
        library(ggplot2)
        library(lme4)
        library(ggthemes)
      
```

## 1. Calculate qPCR RATIOS (Symbiont/Coral) 

Get the raw data for Ssid R.Cunning steponeR function:

* Get list of plate files to read
* Calculate the ratios
* Extract the results

```{r CalculateRatios}

  Ssid.plates <- list.files(path="qPCR-Raw", pattern=".csv", 
                           full.names=TRUE, recursive = TRUE)
  # Ssid.plates

  # Run stepone function to get Ratios
  
  Ssid.Out <- steponeR(files=Ssid.plates, target.ratios=c("C.Ssid", "D.Ssid"), 
                       fluor.norm=list(C=7.1, D=3, Ssid=0),
                       copy.number=list(C=23, D=2, Ssid=1),
                       ploidy=list(C=1, D=1, Ssid=2),
                       extract=list(C=0.813, D=0.813, Ssid=0.982))
  
  # Target ratio results
  Ssid<-Ssid.Out$result
  
```

## 2. Data CLEANING A

```{r DataCleaning}
  # 1. Check and remove NTC wells
    ntc <- Ssid[which(Ssid$Sample.Name=="NTC"|Ssid$Sample.Name=="-"), ]
    Ssid <- droplevels(Ssid[!rownames(Ssid) %in% rownames(ntc), ])
    
  # 2. Check and remove + Control wells
    Positive <- Ssid[which(Ssid$Sample.Name=="+"), ]
    Ssid <- droplevels(Ssid[!rownames(Ssid) %in% rownames(Positive), ])
    
  # 3. Create unique sample ID+FileName to relabel samples  
    Ssid$Sample.Plate<-paste(Ssid$Sample.Name,Ssid$File.Name, sep="_")

  # 4.If Clade only detected in one technical replicate, set its ratio to NA ann make them =0
    One.C<- Ssid[which(Ssid$C.reps==1),]
    Ssid$C.Ssid[which(Ssid$C.reps==1)] <- NA
    
    One.D<- Ssid[which(Ssid$D.reps==1),]
    Ssid$D.Ssid[which(Ssid$D.reps==1)] <- NA
    
    Ssid$C.Ssid[is.na(Ssid$C.Ssid)] <- 0
    Ssid$D.Ssid[is.na(Ssid$D.Ssid)] <- 0

```
    
## 3. Get the cell ratios and log 10 transformations

```{r}
    # Total SH
    Ssid$TotalSH<-(Ssid$C.Ssid + Ssid$D.Ssid)
    
    # Log 10
        Ssid$logC.SH <- log10(Ssid$C.Ssid)
        Ssid$logD.SH <- log10(Ssid$D.Ssid)
        Ssid$logSH<-log10(Ssid$TotalSH)
        
        Ssid$logC.SH[which(Ssid$C.Ssid==0)] <- NA
        Ssid$logD.SH[which(Ssid$D.Ssid==0)] <- NA
  
```    

## 4. Import the sample information

```{r Samples}
# Get the sample informaton 
  SampleName<-read.csv("Sample_Plates.csv") 

# Create unique sample ID+FileName to relabel samples  
   Ssid$Sample.Plate<-paste(Ssid$Sample.Name, Ssid$File.Name, sep="_")
   
# Replace Sample.Names in qPCR data 

rownames(SampleName) <- SampleName$Sample.Plate
    Ssid$Treatment<-SampleName[as.character(Ssid$Sample.Plate), "Treatment"]
    Ssid$Replicate<-SampleName[as.character(Ssid$Sample.Plate), "Rep"]
    Ssid$Colony<-SampleName[as.character(Ssid$Sample.Plate), "Colony"]
      Ssid$Genotype<-paste("Ss", Ssid$Colony, sep = "_" )    
    Ssid$Core<-SampleName[as.character(Ssid$Sample.Plate), "Core"]
      Ssid$Fragment<-paste("Ss", Ssid$Core, sep = "_" )
    Ssid$Date<-SampleName[as.character(Ssid$Sample.Plate), "Date"]
          Ssid$Date<-as.Date(Ssid$Date, format="%Y/%m/%d")
          Ssid$Days<-as.numeric(Ssid$Date -17485)
          
# Get timePoint inf
  TimePoints<-read.csv("Time_Points.csv") 
  TimePoints$Date<-as.Date(TimePoints$Date, format="%m/%d/%y")
  Ssid<-left_join(Ssid, TimePoints, by = "Date")

# Creates a unique ID for a core-sampling time 
  Ssid$Sample<-paste(Ssid$Fragment, Ssid$Time_Point, sep='_') 
```

## 5. Data CLEANING B

* Fucked up samples

```{r DataCleaningB}

# 5. Remove (-) control
    NegControl <- Ssid[which(Ssid$Sample=="Ss_NA_NA"|Ssid$Sample=="Ss_-_T9"), ]
    Ssid <- droplevels(Ssid[!rownames(Ssid) %in% rownames(NegControl), ])

# 6.If coral detected in one technical replicate, remove the sample
    ReRun.Coral <- Ssid[which(Ssid$Ssid.reps==1), ]
    Ssid <- droplevels(Ssid[!rownames(Ssid) %in% rownames(ReRun.Coral), ])
    
    NoHSratio <- Ssid[which(Ssid$TotalSH==0), ]
    Ssid <- droplevels(Ssid[!rownames(Ssid) %in% rownames(NoHSratio), ])
    
# 7. High ST    
    StDe1.5 <- Ssid[which((Ssid$Ssid.CT.sd>1.5)|(Ssid$C.CT.sd>1.5)|(Ssid$D.CT.sd>1.5)), ]
    Ssid <- droplevels(Ssid[!rownames(Ssid) %in% rownames(StDe1.5), ])
     # ToRe_Run2<-anti_join (StDe1.5, Acer, by=c("Sample.Name", "Time"))
  
# 8.Suspiciusly late coral
    Histo_Ssid_CT<-qplot(Ssid.CT.mean, data=Ssid, binwidth=0.15)
    Histo_Ssid_CT 
  
  LateCoral<-Ssid[which(Ssid$Ssid.CT.mean>25), ]
  Ssid <- droplevels(Ssid[!rownames(Ssid) %in% rownames(LateCoral), ])
  
    
# Samples to Re-run    
  ToRe_Run1<-rbind(ReRun.Coral, NoHSratio)
  ToRe_Run1<-rbind(ToRe_Run1, ReRun.Coral)   
  ToRe_Run1<-rbind(ToRe_Run1, StDe1.5)
  ToRe_Run1<-rbind(ToRe_Run1, LateCoral)
  ToRe_Run1<-anti_join (ToRe_Run1, Ssid, by=c("Sample"))
```
  
* Chose bw samples ran more than once

```{r remove duplicates}
 ReRunA <- Ssid[duplicated(Ssid$Sample),] 
  n_RunA <- data.frame(table(Ssid$Sample))
  colnames(n_RunA)<-c("Sample","RanA")
  Ssid<-join(Ssid, n_RunA, type = "left")
# 
  DuplicatesA <- Ssid[(Ssid$RanA>1),]
  #write.csv(DuplicatesA, "DuplicatesA.csv")
```

* Remove duplicates

```{r remove duplicates2}
  ToRem1<-read.csv("ToRemove.csv")
    # 10/24/2018
   Ssid<-Ssid[!(Ssid$Sample.Plate %in% ToRem1$Sample.Plate),]
 
# Check for replicates again--should have none
 
  n_RunB <- data.frame(table(Ssid$Sample))
  colnames(n_RunB)<-c("Sample","RanB")
  Ssid<-join(Ssid, n_RunB, type = "left")


# List of dupplicated samples, should have 0 rows now -->
   DuplicatesB <- Ssid[(Ssid$RanB>1),]
#  write.csv(DuplicatesB, file = 'DuplicatesB.csv')
```

## 6. Calculate genus proportions
    
```{R Proportions}

# D Proportion
    Ssid$D.Prp<-(Ssid$D.Ssid/Ssid$TotalSH)
  
    
 # Core clasification by clade Proportion 
    Ssid[,Ssid$Community]<-NULL
    
    Ssid$Community[which(Ssid$D.Prp>=0.5)] <- "D"
    Ssid$Community[which(Ssid$D.Prp<0.5)] <- "C"
    
  Ssid$Community<-factor(as.character(Ssid$Community), levels=c("C","D"))
  
  Ssid<-subset(Ssid, File.Name!="Plate26.csv")
  summary(Ssid)
  
```

## 7. Check and export S/H cell ratio data!

```{r}
qPCRsummary<-summary(Ssid)
#capture.output(qPCRsummary, file = "Outputs/qPCRsummary.txt")

# ITS2
  Ssid$Community2[Ssid$Genotype == "Ss_20" & Ssid$Community== "C"] <- "C1"
  Ssid$Community2[Ssid$Genotype == "Ss_28" & Ssid$Community== "C"] <- "C1"
  Ssid$Community2[Ssid$Genotype == "Ss_22" & Ssid$Community== "C"] <- "C1"
  # Ssid$Community2[Ssid$Genotype == "Ss_23" & Ssid$Community== "C"] <- "C1"
  Ssid$Community2[Ssid$Genotype == "Ss_24" & Ssid$Community== "C"] <- "C3"
  Ssid$Community2[Ssid$Genotype == "Ss_30" & Ssid$Community== "C"] <- "C3"
  Ssid$Community2[Ssid$Community== "D"] <- "D"


Ssid.export<-Ssid %>% select(Treatment, Replicate, Fragment, Genotype,
                             Date, Days, Time_Point, Phase, Sample, 
                             C.Ssid, D.Ssid, TotalSH, 
                             logC.SH, logD.SH, logSH, 
                             D.Prp, Community2)

Ssid.export$Treatment <- as.character(Ssid.export$Treatment)
      Ssid.export$Treatment[Ssid$Treatment == "Control"] <- "A"
      Ssid.export$Treatment[Ssid$Treatment == "NP"] <- "N+P"

Ssid.export$Genotype<-factor(Ssid.export$Genotype, 
                                   levels=c( "Ss_22", "Ss_23", "Ss_27", "Ss_28",
                                             "Ss_24", "Ss_30", "Ss_20"))

Ssid.export<-Ssid.export[order(
        Ssid.export$Date, Ssid.export$Treatment, Ssid.export$Replicate,
        Ssid.export$Genotype, Ssid.export$Fragment),]

# write.csv(Ssid.export, "Outputs/Ssid_SH_cell_ratio.csv", row.names = F)
```

```{r}
Ssid.metadata<-Ssid %>% select(Sample, TotalSH, D.Prp, Community2)

# write.csv(Ssid.metadata, "Outputs/Ssid_SH_metadata.csv", row.names = F)
```

## 8. Data Exploration

* Select qPCR info

```{r}
qPCR.variables<-Ssid.export
qPCR.variables$Community<-qPCR.variables$Community2

library("ggthemes")
library("scales")   

```

```{r}
   HistoL_SH<-qplot(logSH, data=qPCR.variables, binwidth=0.15)
   HistoL_SH + facet_grid(Treatment~Genotype)
   
   HistoL_CH<-qplot(logC.SH, data=qPCR.variables, binwidth=0.15)
   HistoL_CH + facet_grid(Treatment~Genotype)

   HistoL_DH<-qplot(logD.SH, data=qPCR.variables, binwidth=0.15)
   HistoL_DH + facet_grid(Genotype~Replicate)
```

* Log SH by fragment

```{r}
logSHTreatment <- ggplot(qPCR.variables, aes(Days, logSH)) +
        geom_line(aes(colour=Fragment))+ 
        geom_point(aes(shape=factor(Community), colour=factor(Community)))+
        stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
        stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) +
        stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
       theme_gdocs() 

logSHTreatment + ylab("Relative log10 (S:H)") + xlab("Treatment") +  
  theme(axis.title.y=element_text(size=12), legend.position="none") +
  facet_wrap(~Genotype)

logSHTreatment <- ggplot(qPCR.variables, aes(Days, logSH)) +
  geom_line(aes(colour=Fragment))+geom_point(aes(shape=factor(Community)))+
  # geom_jitter(aes(colour=factor(Replicate))) +
      # stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
      #stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) +
      # stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
      facet_grid(Genotype~Treatment) +
      theme_bw() +
      theme(legend.position = "none" )

logSHTreatment + ylab("Relative log10 (S:H)") + xlab("Treatment") +  
      theme(axis.title.y=element_text(size=12), legend.position="none")

logSHTreatment <- ggplot(qPCR.variables, aes(Days, logSH, colour=Treatment)) +
        stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
        stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) +
        stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
       theme_gdocs() 
logSHTreatment
logSHTreatment + ylab("Relative log10 (S:H)") + xlab("Treatment") +  
  theme(axis.title.y=element_text(size=12), legend.position="none") +
  facet_wrap(~Genotype)

```

* Log C

```{r}
logC_Treatment <- ggplot(qPCR.variables, aes(Days, logC.SH, colour=factor(Treatment))) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(~Community) +
         theme_bw() 
  logC_Treatment
   
logC_Frag <- ggplot(qPCR.variables, aes(Days, logC.SH, goup=Fragment,
                                        colour=Treatment)) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Genotype~Community) +
         theme_bw() + theme(legend.position = "none")
  logC_Frag

```

* Log D

```{r}
logD_Treatment <- ggplot(qPCR.variables, aes(Days, logD.SH, colour=factor(Treatment))) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(~Community) +
         theme_bw() 
  logD_Treatment
  
  logD_Frag <- ggplot(qPCR.variables, aes(Days, logD.SH, goup=Fragment,
                                        colour=Treatment)) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Genotype~Community) +
         theme_bw() + theme(legend.position = "none")
  logD_Frag

```

```{r}
  
DPrp <- ggplot(qPCR.variables, aes(Days, D.Prp ,
                colour=factor(Treatment))) +
  #geom_line(aes(colour=Core)) +
  geom_jitter(aes(colour=Replicate))+
   stat_summary(fun.data = "mean_cl_boot",geom = "line", width = 0.2)+
         #stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Genotype~.) +
         theme_gdocs() +
  theme(legend.position = "none")
DPrp

#Checks<-subset(Ssid, Core=c("20-36"))

```
