---
title: "Ssid SH Nutrients"
author: "Ana Palacio"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    df_print: paged
    theme: united
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```


# General project set-up 

```{r libraries , results="hide"}

# Get all libraries and sources required to run the script
        library(plyr)
        library(dplyr)
        library(reshape2)

        library(ggplot2)
        library(ggthemes)
        library(scales)

        library(lme4)
        library(lmerTest)
        library(emmeans)
    
        library(skimr)

# Default ggplot settings

    Fill.colour<-scale_colour_manual(values = c("black", "gray70", "gray35"))

    ggthe_bw<-theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black")
          )+
    theme_bw()
```

## 1. DATA Exploration

### 1. Select qPCR info and define factors
 
```{r VariablesToUse}

# Import the data
  qPCR.variables  <- read.csv("Outputs/Ssid_SH_cell_ratio.csv", header = T)

# Remove blastate samples
  qPCR.blastate<-qPCR.variables[((qPCR.variables$Date=="2018-02-05") |
                                   (qPCR.variables$Date=="2018-03-08")), ]
  qPCR.variables <- droplevels(qPCR.variables[!rownames(qPCR.variables) %in% rownames(qPCR.blastate), ])  
  
 
# Variable types 
str(qPCR.variables)
  qPCR.variables$Genotype<-factor(qPCR.variables$Genotype, 
                                   levels=c("Ss_22","Ss_23","Ss_27", "Ss_28",
                                          "Ss_20", "Ss_24","Ss_30"))
  qPCR.variables$DaysF<-as.factor(qPCR.variables$Days)
  
  summary(qPCR.variables)
  skim(qPCR.variables)

```  

### 2. Exploratory graphs

* Histograms

```{r }
  HistoL_SH<-qplot(logSH, data=qPCR.variables, binwidth=0.15)
   HistoL_SH + facet_grid(Treatment~Date)
   
  ggplot(qPCR.variables, aes(logSH, fill = Treatment , colour = Treatment)) +
   geom_density(alpha = 0.1) + facet_wrap(~Date) + ggthe_bw

```

* Log SH

```{r}

logSHGenotype <- ggplot(qPCR.variables, aes(Days, logSH)) +
  geom_line(aes(colour=Fragment))+geom_point(aes(shape=factor(Community), colour=factor(Community)))+
  # geom_jitter(aes(colour=factor(Replicate))) +
      # stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
      #stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) +
      # stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
      facet_grid(Treatment~Genotype) +
      ggthe_bw +theme(legend.position = "none" )

logSHGenotype + ylab("Relative log10 (S:H)") + xlab("Treatment") +  
      theme(axis.title.y=element_text(size=12), legend.position="none")


logSHTreatment <- ggplot(qPCR.variables, aes(Date, logSH, colour=factor(Treatment))) +
       # geom_jitter(aes(colour=factor(Treatment))) +
       stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
       stat_summary(fun.y=mean, geom="line", size =1) +
       theme_bw() 
logSHTreatment + facet_wrap(~Genotype)

logSH_Replicate<- ggplot(qPCR.variables, aes (Days, logSH, 
                                             colour=factor(Replicate))) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) +
  stat_summary(fun.y=mean, geom="line") + facet_grid (~Treatment) + ggthe_bw
logSH_Replicate 
logSH_Replicate+ facet_grid(~Community)

logSHTreatment <- ggplot (qPCR.variables, aes(Days, logSH, colour=Treatment)) + 
  ggtitle("A.") +  # geom_point(alpha=0.3) +
  ggthe_bw +  theme(legend.position="bottom") +
  
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
  #stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
       #            position = position_dodge(width = 1)) +
  stat_summary(fun.y=mean, geom="line", position = position_dodge(width = 5)) + 

  scale_y_continuous(breaks = seq(-5, 0.5, 0.5),
                    expand = c(0,0),
                  name=("log 10 (Total S/H cell ratio")) +
  scale_x_continuous(name="Days in the experiment",
                         limits = c(-2,113),
                         breaks = seq(0, 110, 15),  
                         expand = c(0, 0)) +  
 
      annotate("segment", x = 2, xend = 91, y = -3.5, yend = -3.5,
                colour = "gray90")+
      annotate("segment", x = 79, xend = 90, y = -3.5, yend = -3,
                colour = "gray90")+
      annotate("segment", x = 91, xend = 110, y = -3, yend = -3,
                colour = "gray90")
logSHTreatment

#logSHTreatment + facet_wrap(~Genotype)
logSHTreatment + facet_wrap(~Community)
```

* Log C

```{r}
logC_Treatment <- ggplot(qPCR.variables,
                         aes(Days, logC.SH, colour=factor(Fragment))) +
     geom_line()+ 
     #geom_jitter(aes(colour=factor(Replicate))) +
         #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         #stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         ggthe_bw +  theme(legend.position = "none" )
logC_Treatment
logC_Treatment + facet_grid(Genotype~Treatment)
logC_Treatment + facet_grid(Community~Treatment)
```


* Log D

```{r}
logD_genotype <- ggplot(qPCR.variables,
                         aes(Days, logD.SH, colour=factor(Fragment))) +
     geom_line()+ 
     #geom_jitter(aes(colour=factor(Replicate))) +
         #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         #stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         ggthe_bw +  theme(legend.position = "none" )
logD_genotype
logD_genotype + facet_grid(Genotype~Treatment)

logD_Treat <- ggplot(qPCR.variables,
                         aes(Days, logD.SH, colour=factor(Treatment))) +
     #geom_jitter(aes(colour=factor(Replicate))) +
        stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
        stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
        ggthe_bw +  theme(legend.position = "none" )
logD_Treat
logD_Treat + facet_grid(Community~Treatment)

```

*D proportion

```{r}

qPCR.variables$D.Prp[qPCR.variables$Sample=="Ss_22-18_T22"]<-NA
qPCR.variables$Community[qPCR.variables$Sample=="Ss_22-18_T22"]<-"D"

qPCR.variables$D.Prp[qPCR.variables$Sample=="Ss_23-80_T19"]<-NA
qPCR.variables$Community[qPCR.variables$Sample=="Ss_23-80_T19"]<-"D"

D.PTreatment <- ggplot(qPCR.variables, aes(Days, D.Prp, colour=Fragment)) +
        ggthe_bw +  theme(legend.position="none") +  
        geom_jitter(aes(colour=factor(Fragment)), alpha=0.5, size=1) +
        geom_line() + facet_grid (Genotype~Treatment) +
  
   annotate("segment", x = 2, xend = 91, y = -0.03, yend = -0.03,
                colour = "gray90", linetype=2)+
        
      annotate("segment", x = 79, xend = 90, y = -0.03, yend = 0.3,
                colour = "gray90",linetype=3)+
    
      annotate("segment", x = 91, xend = 110, y = 0.3, yend = 0.3,
                colour = "gray90", linetype=3)+
      #annotate("text", x = 8, y = 0.08, label = "(BL)", size=3, colour="gray")+
      annotate("text", x = 45, y = 0.1, label = "Nutrients", size=3, colour="gray")+
      annotate("text", x = 99, y = 0.4, label = "Heat", size=3, colour="gray")+  
  

      scale_y_continuous(breaks = seq(0, 1, 0.3),
                         limits = c(-0.035,1),
                     name=("Durusdinium proportion (D/H)/(S/H)")) +
      scale_x_continuous(name="Days in the experiment",
                           limits = c(-2,113),
                         breaks = seq(0, 110, 30),  
                         expand = c(0, 0))
D.PTreatment
#ggsave(file="Outputs/D.P_Treatment_Genotype.svg", plot=D.PTreatment, width=4.5, height=8)
```

# 2. Subset data

```{r}
# Removing weird points and colonies not used

  qPCR.variables_2<-subset(qPCR.variables, Date!="2017-12-14")
  qPCR.variables_2<-subset(qPCR.variables_2, TotalSH<0.8)
  
  SH.0<-subset(qPCR.variables_2, Days<2)
  SH.C<-subset(qPCR.variables_2, Days<79)
    SH.C<-subset(SH.C, Days>77)
  SH.H<-subset(qPCR.variables_2, Days>80)
 
  
logSH_Genotype<- ggplot(qPCR.variables_2, aes (Days, logSH, 
                     colour=factor(Fragment))) +
  theme_bw() + geom_line()+ facet_grid (Genotype~Treatment)#+
logSH_Genotype + theme(legend.position = "none" ) + geom_point()

```

## Log S/H graph with treatment

```{r}
qPCR.variables_2$Community<-factor(qPCR.variables_2$Community, levels = c("C3", "C1", "D"))

logSHTreatment <- ggplot (qPCR.variables_2, aes(Days, logSH, colour=Treatment, shape=Treatment)) + 
    # ggtitle("(b)") +
    Fill.colour + ggthe_bw+
    theme(plot.background=element_blank(), 
            #panel.border = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position=c(0.1, 0.25),
            strip.background = element_rect(fill="white"),
            legend.title = element_blank()) +
       #geom_jitter(aes(colour=factor(Replicate))) +
       stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 6), width = 2 )+
      stat_summary(fun.y=mean, geom="point", size =2, alpha=0.8, 
                   position = position_dodge(width = 6)) +
       stat_summary(fun.y=mean, geom="line", position = position_dodge(width = 6)) + 
      
        annotate("segment", x = 73, xend = 91, y = -4.5, yend = -4.5,
                  colour = "gray90", linetype=2)+
        annotate("segment", x = 79, xend = 91, y = -4.5, yend = -4,
                  colour = "gray90", linetype=3)+
        annotate("segment", x = 91, xend = 110, y = -4, yend = -4,
                  colour = "gray90", linetype=3)+
        annotate("text", x = 80, y = -4.4, label = "Nutrients", size=3, colour="gray")+
        #annotate("text", x = 3, y = -4.4, label = "BL", size=3,  colour="gray")+
        annotate("text", x = 100, y = -4.3, label = "Heat", size=3, colour="gray") +

      scale_y_continuous(limits = c(-4.6,0),
        breaks = seq(-5, 0.3, 0.5),
                    expand = c(0,0),
                   name=("Relative (S/H) cell ratio")) +
      scale_x_continuous(name="Days in the experiment",
                         limits = c(73, 114),
                         breaks = seq(0, 110, 15),  
                         expand = c(0.01, 0.01))
  logSHTreatment 
  logSHTreatmentb<-logSHTreatment  + facet_grid(~Community)
  logSHTreatmentb
  # ggsave(file="5.3A_AH.svg", plot=logSHTreatmentb, width=3.0, height=6)
  # ggsave(file="5.3A_AH.svg", plot=logSHTreatmentb, width=6.3, height=3.5)
  #
  
```

## Log S/H graph without treatment

```{r}
logSH_Community <- ggplot (qPCR.variables_2, aes(Days, logSH, colour=Community, shape=Community)) +  
   ggtitle("(c)")+         ggthe_bw+
    theme(plot.background=element_blank(), 
            panel.border = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position=c(0.2,0.25),
            strip.background = element_rect(fill="white")) +
       #geom_jitter(aes(colour=factor(Replicate))) +
       stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
      stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
                   position = position_dodge(width = 5)) +
       stat_summary(fun.y=mean, geom="line", position = position_dodge(width = 5)) + 
      
  annotate("segment", x = 2, xend = 91, y = -4.5, yend = -4.5,
                  colour = "gray90", linetype=2)+
        annotate("segment", x = 79, xend = 91, y = -4.5, yend = -4,
                  colour = "gray90", linetype=4)+
        annotate("segment", x = 91, xend = 110, y = -4, yend = -4,
                  colour = "gray90", linetype=3)+
        annotate("text", x = 2, y = -4.4, label = "BL", size=3)+
        annotate("text", x = 45, y = -4.4, label = "Nutrients", size=3)+
        annotate("text", x = 100, y = -3.9, label = "H", size=3) +

      scale_y_continuous(limits = c(-4.6, -0.3),
                        breaks = seq(-4.5, 0.3, 0.5),
                        expand = c(0,0),
                        name=("Relative (S/H) cell ratio")) +
      scale_x_continuous(name="Days in the experiment",
                         limits = c(-2,113),
                         breaks = seq(0, 110, 15),  
                         expand = c(0, 0))
  logSH_Community
  
  #ggsave(file="S6_SH.svg", plot=logSH_Community, width=4.0, height=3.5)

```

## Log C/H graph

```{r}
  
CHTreatment_2 <- ggplot (qPCR.variables_2, aes(Days, logC.SH, colour=Treatment)) +  theme_bw() + ggtitle("C.")+ Fill.colour+ ggthe_bw+
  annotate("segment", x = 2, xend = 91, y = -4.5, yend = -4.5,
                  colour = "gray90", linetype=1)+
        annotate("segment", x = 79, xend = 91, y = -4.5, yend = -4,
                  colour = "gray90", linetype=1)+
        annotate("segment", x = 91, xend = 110, y = -4, yend = -4,
                  colour = "gray90", linetype=1)+
        annotate("text", x = 45, y = -4.4, label = "Nutrients", size=3)+
        annotate("text", x = 99, y = -3.9, label = "Heat", size=3) +
       
       #geom_jitter(aes(colour=factor(Replicate))) +
       stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
      #stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
       #            position = position_dodge(width = 5)) +
       stat_summary(fun.y=mean, geom="line") +
      scale_x_continuous(name="Days in the experiment",
                         limits = c(-2,113),
                         breaks = seq(0, 110, 15),  
                         expand = c(0, 0))
  CHTreatment_2  
  #CHTreatment_2 + facet_grid (Genotype~Community)

  CHTreatment_2 + facet_grid(~Community)
  
  #ggsave(file="5.3A_AH_2.svg", plot=SHTreatment_2, width=3.0, height=6)
  #ggsave(file="5.3C_SH_NoGenotype_2.svg", plot=SHTreatment_2, width=3.0, height=3)
```
  
## Log D/H graph

```{r}
  
DHTreatment_2 <- ggplot (qPCR.variables_2, aes(Days, logD.SH, colour=Treatment)) +  theme_bw() + ggtitle("C.")+ Fill.colour+ ggthe_bw+
  annotate("segment", x = 2, xend = 91, y = -4.5, yend = -4.5,
                  colour = "gray90", linetype=1)+
        annotate("segment", x = 79, xend = 91, y = -4.5, yend = -4,
                  colour = "gray90", linetype=1)+
        annotate("segment", x = 91, xend = 110, y = -4, yend = -4,
                  colour = "gray90", linetype=1)+
        annotate("text", x = 45, y = -4.4, label = "Nutrients", size=3)+
        annotate("text", x = 99, y = -3.9, label = "Heat", size=3) +
       
       #geom_jitter(aes(colour=factor(Replicate))) +
       stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
      #stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
       #            position = position_dodge(width = 5)) +
       stat_summary(fun.y=mean, geom="line") +
      scale_x_continuous(name="Days in the experiment",
                         limits = c(-2,113),
                         breaks = seq(0, 110, 15),  
                         expand = c(0, 0))
  DHTreatment_2 + facet_grid (Genotype~Community)

  DHTreatment_2 + facet_grid(~Community)

```

##D Proportion 

```{r}
D.PTreatment <- ggplot(qPCR.variables, aes(Days, D.Prp, colour=Fragment)) +
        ggthe_bw +  theme(legend.position="none") +  
        geom_jitter(aes(shape=factor(Treatment)), alpha=0.5) +
        geom_line()+ 
      annotate("segment", x = 2, xend = 91, y = 0, yend = 0,
                colour = "gray90")+
      #annotate("text", x = 45, y = 0.2, label = "Nutrients", size=3)+
    
      annotate("segment", x = 79, xend = 90, y = 0, yend = 0.3,
                colour = "gray90")+
    
      annotate("segment", x = 91, xend = 110, y = 0.3, yend = 0.3,
                colour = "gray90")+
      #annotate("text", x = 99, y = 0.3, label = "Heat", size=3)+

      scale_y_continuous(breaks = seq(0, 1, 0.3),
                     name=("Durusdinium proportion (D/H)/(S/H)")) +
      scale_x_continuous(name="Days in the experiment",
                           limits = c(-2,113),
                         breaks = seq(0, 110, 45),  
                         expand = c(0, 0))
      D.PTreatment + facet_grid (~Genotype)
D.PTreatment
```

# 3. GLM models

## Baseline

```{r}
LME_BaseLine<-lmer(logSH ~ Treatment + Community + (1|Genotype) + (1|Replicate), 
                     data=SH.0)
   step(LME_BaseLine)
   anova(LME_BaseLine) # Treatments is not significant
   ranova(LME_BaseLine) # Treatments is significant!
   
   LME_BaseLine<-lmer(logSH ~ Genotype + (1|Replicate), 
                     data=SH.0)
   step(LME_BaseLine)
   anova(LME_BaseLine) # Treatments is not significant
   ranova(LME_BaseLine) # Treatments is significant!

```

```{r}

# Multicomp
Ssid.SH.C.emm<-emmeans(LME_BaseLine, ~Genotype)
      #contrast(Ofav.SH.C.emm, "tukey")
    Ssid.SH.C_groups<-cld(Ssid.SH.C.emm, by=NULL) # compact-letter display
    Ssid.SH.C_groups
    
# Effect plot
  plot(emmeans(LME_BaseLine, ~Genotype), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + theme_bw()
```

```{r}
logSHTreatmentBL <- ggplot (SH.0, aes(Genotype, logSH, colour=Genotype)) + 
  #ggtitle("A.") + 
  ggthe_bw +  theme(legend.position="bottom") +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
                  position = position_dodge(width = 1)) +
  
  scale_y_continuous(breaks = seq(-2.5, 0, 0.5),
                    expand = c(0.1,0.1),
                  name=("log 10 (Total S/H cell ratio"))
    
logSHTreatmentBL

logSHTreatmentBL + facet_grid(~Community)
```

## C: Effect of nutrient treatments at control temperature

```{r}
LME_Ssid.C<-lmer(logSH ~ Treatment + Community + (1|Replicate) + (1|Genotype), 
                     data=SH.C)
     step (LME_Ssid.C) #  Remove Genotype
     anova (LME_Ssid.C)
     ranova (LME_Ssid.C)
     
LME_Ssid.C<-lmer(logSH ~ Treatment + Community + (1|Replicate),
                     data=SH.C)
     step (LME_Ssid.C) #  Remove replicate
     anova (LME_Ssid.C)
     ranova (LME_Ssid.C)

```

```{r}
# Multicomp
Ssid.SH.C.emm<-emmeans(LME_Ssid.C, ~Community|Treatment)
      #contrast(Ssid.SH.C.emm, "tukey")
    Ssid.SH.C_groups<-cld(Ssid.SH.C.emm, by=NULL) # compact-letter display
    Ssid.SH.C_groups
    
# Effect plot
  plot(emmeans(LME_Ssid.C, ~Treatment), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + theme_bw()
```


```{r}
logSHTreatmentC <- ggplot (SH.C, aes(Treatment, logSH, colour=Treatment, shape=Treatment)) + 
  ggtitle("A.")+ Fill.colour +
  ggthe_bw +  theme(legend.position="bottom") +
  
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
                  position = position_dodge(width = 1)) +
  
  scale_y_continuous(breaks = seq(-2.5, 0, 0.5),
                    expand = c(0.1,0.1),
                  name=("log 10 (Total S/H cell ratio"))
    
logSHTreatmentC

logSHGenotypeC <- ggplot (SH.C, aes(Genotype, logSH, colour=Genotype)) + 
  ggthe_bw +  theme(legend.position="bottom") +
  
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
                  position = position_dodge(width = 1)) +
  
  scale_y_continuous(breaks = seq(-2.5, 0, 0.5),
                    expand = c(0.1,0.1),
                  name=("log 10 (C/H) cell ratio"))
    
logSHGenotypeC

```

## H: Effect of pre-exposure to nutrient treatments during heat challenge


```{r}
LME_Ssid.H<-lmer(logSH ~ Treatment * Community * DaysF+ (1|Replicate) + (1|Genotype), 
                     data=SH.H)
     step (LME_Ssid.H) #  Remove Replicate
     anova (LME_Ssid.H)
     ranova (LME_Ssid.H)
     
LME_Ssid.H<-lmer(logSH ~ Treatment * Community * DaysF+ (1|Genotype),
                     data=SH.H)
     step (LME_Ssid.H) #  Remove replicate
     anova (LME_Ssid.H)
     ranova (LME_Ssid.H)

```

```{r}
# Multicomp
Ssid.SH.H.emm<-emmeans(LME_Ssid.H, ~Treatment|Community|DaysF)
    contrast(Ssid.SH.H.emm, "tukey")
    Ssid.SH.H_groups<-cld(Ssid.SH.H.emm, by=NULL) # compact-letter display
    Ssid.SH.H_groups<-Ssid.SH.H_groups[order(Ssid.SH.H_groups$Day,
                           Ssid.SH.H_groups$Community, 
                           Ssid.SH.H_groups$Treatment), ]
    
    Ssid.SH.H_groups
    
# Effect plot
  plot(emmeans(LME_Ssid.H, ~DaysF*Community|Treatment), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + theme_bw()
```


```{r}
logSHTreatmentH <- ggplot (SH.H, aes(Treatment, logSH, colour=Treatment, shape=Treatment)) + 
  ggtitle("A.")+ Fill.colour +
  ggthe_bw +  theme(legend.position="bottom") +
  
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
                  position = position_dodge(width = 1)) +
  
  scale_y_continuous(breaks = seq(-3, 0, 0.5),
                    expand = c(0.1,0.1),
                  name=("log 10 (Total S/H cell ratio"))
    
logSHTreatmentH
logSHTreatmentH + facet_grid(~Community)
logSHTreatmentH + facet_grid(DaysF~Community) #+  geom_jitter()


logSHTreatmentH <- ggplot (SH.H, aes(DaysF, logSH)) + 
  ggtitle("A.")+ Fill.colour +
  ggthe_bw +  theme(legend.position="bottom") +
  
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
                  position = position_dodge(width = 1)) +
  
  scale_y_continuous(breaks = seq(-3, 0, 0.5),
                    expand = c(0.1,0.1),
                  name=("log 10 (Total S/H cell ratio"))
    
logSHTreatmentH
logSHTreatmentH + facet_grid(~Community)
logSHTreatmentH + facet_grid(Treatment~Community) #+  geom_jitter()



logSHGenotypeH <- ggplot (SH.H, aes(Community, logSH, colour=Genotype)) + 
  ggthe_bw +  theme(legend.position="bottom") +
  
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) +
  
  scale_y_continuous(breaks = seq(-2.5, 0, 0.5),
                    expand = c(0.1,0.1),
                  name=("log 10 (Total S/H cell ratio"))
    
logSHGenotypeH
logSHGenotypeH + facet_grid(~DaysF)

```

## All phases

* Dasys as a factor

```{r}
    
LM_Ssid.qpCR<-lmer(logSH ~ Treatment * DaysF * Community + (1|Replicate) + (1|Genotype/Fragment), 
                   data= qPCR.variables_2)
    step(LM_Ssid.qpCR)
    anova(LM_Ssid.qpCR)
    ranova(LM_Ssid.qpCR)

LM_Ssid.qpCR<-lmer(logSH ~ Treatment + DaysF + Community + 
                     (1 | Genotype) + 
                     Treatment:DaysF +  DaysF:Community,
                   data= qPCR.variables_2)
      step(LM_Ssid.qpCR)
      anova(LM_Ssid.qpCR)
      ranova(LM_Ssid.qpCR)
      summary(LM_Ssid.qpCR)
    
```

```{r}
# Emmeans
Ssid.YII.emm<-emmeans(LM_Ssid.qpCR, ~Treatment|Community|DaysF)
#Ssid.YII.emm<-emmeans(LM_Ssid.qpCR, ~Community|DaysF)
     #contrast(Ssid.YII.emm, "tukey")

# Pairwise comparisons
    #pairs(Ssid.YII.emm) # same than contrast(Ssid.YII.emm, "tukey")
  plot(emmeans(LM_Ssid.qpCR, ~Treatment|DaysF), comparisons = TRUE) +
        theme_bw() # Tukey comparission (do not trust CI to compare EMMs)
    
    plot(emmeans(LM_Ssid.qpCR, ~Treatment|DaysF|Community), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + facet_grid(Community~DaysF) +
      theme_bw()
  
  #CLD  
  SH_Multicomp<-cld(Ssid.YII.emm, by=NULL) # compact-letter display
      SH_Multicomp<-SH_Multicomp[order(SH_Multicomp$DaysF, 
                                       SH_Multicomp$Community,
                                       SH_Multicomp$Treatment), ]
    #write.csv(SH_Multicomp, "Outputs/Ssid_SH_Multicomp.csv")  

```


```{r}
 # 2. Predict values:
    pred_Ssid1 <- predict(LM_Ssid.qpCR, re.form = NA)

  #3. Bootstrap CI:
    Ss.boot1 <- bootMer(LM_Ssid.qpCR, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(Ss.boot1$t, 2, sd)
    CI.lo_1 <- pred_Ssid1 - std.err*1.96
    CI.hi_1 <- pred_Ssid1 + std.err*1.96

  #Plot
  Model_Ss_1b_plot<- ggplot(
    qPCR.variables_2, aes(x = Days, y = logSH, colour = Treatment)) +
    geom_line(aes(y = pred_Ssid1),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_1, ymax = CI.hi_1),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    #scale_y_continuous(name=expression(~italic("Fv / Fm")),
    #                   limits = c(0.5, 0.61), 
    #                   breaks = seq(0.4, 0.6, by=0.1), expand = c(0,0))+
    #scale_x_continuous("Days in the experiment", limits = c(0, 78),
    #                 breaks = seq(0, 76, by=7), expand = c(0,0))+
    
     stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="line", position = position_dodge(1), 
                  linetype=1, alpha=1)
    # stat_summary(fun.y=mean, geom="point", size =1,
    #             position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw
  
  Model_Ss_1b_plot + facet_wrap(~Community)

```


* Days as continous

```{r}
    
LM_Ssid.qpCR2<-lmer(logSH ~ Treatment * Days * Community + (1|Replicate) + (1|Genotype/Fragment), 
                   data= qPCR.variables_2)
    step(LM_Ssid.qpCR2)
    anova(LM_Ssid.qpCR2)
    ranova(LM_Ssid.qpCR2)

LM_Ssid.qpCR2<-lmer(logSH ~Treatment + Days + Community + (1|Genotype) + Treatment:Days,
                   data= qPCR.variables_2)
      step(LM_Ssid.qpCR2)
      anova(LM_Ssid.qpCR2)
      ranova(LM_Ssid.qpCR2)
      summary(LM_Ssid.qpCR2)
    
```

```{r}
 # 2. Predict values:
    pred_Ssid1 <- predict(LM_Ssid.qpCR2,re.form = NA)

  #3. Bootstrap CI:
    Ss.boot1 <- bootMer(LM_Ssid.qpCR2, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(Ss.boot1$t, 2, sd)
    CI.lo_1 <- pred_Ssid1 - std.err*1.96
    CI.hi_1 <- pred_Ssid1 + std.err*1.96

  #Plot
  Model_Ss_1b_plot<- ggplot(
    qPCR.variables_2, aes(x = Days, y = logSH, colour = Treatment)) +
    geom_line(aes(y = pred_Ssid1),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_1, ymax = CI.hi_1),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    #scale_y_continuous(name=expression(~italic("Fv / Fm")),
    #                   limits = c(0.5, 0.61), 
    #                   breaks = seq(0.4, 0.6, by=0.1), expand = c(0,0))+
    #scale_x_continuous("Days in the experiment", limits = c(0, 78),
    #                 breaks = seq(0, 76, by=7), expand = c(0,0))+
    
     stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="line", position = position_dodge(1), 
                  linetype=1, alpha=1) + 
    # stat_summary(fun.y=mean, geom="point", size =1,
    #             position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw
  
  Model_Ss_1b_plot + facet_wrap(Genotype~Community)

```


## All phases, except baseline

* Dasys as a factor

```{r}
qPCR.variables_3<-qPCR.variables_2[(qPCR.variables_2$DaysF!="0"), ]  

Sy.Summary <- plyr::ddply (qPCR.variables_3, . (DaysF, Community, Treatment),
              summarise,
              Sy_mean = mean (TotalSH, na.rm = T),
              Sy_sd = sd (TotalSH, na.rm = T))
Sy.Summary
write.csv(Sy.Summary, "Outputs/meanSH.csv")
```

```{r}

Treatment<- ggplot(
    qPCR.variables_3, aes(x = Days, y = logSH, 
                          colour = Treatment, shape = Treatment)) +
  Fill.colour+
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(3) )+
    stat_summary(fun.y=mean, geom="line", position = position_dodge(3), 
                  linetype=1, alpha=1)+
     stat_summary(fun.y=mean, geom="point", size =1,
                 position=position_dodge(3), alpha=0.8)  +
    ggthe_bw + facet_grid(~Community) +
   scale_y_continuous(breaks = seq(-5.5, 0.5, 0.5),
                    expand = c(0.1,0.1),
                  name=("log 10 (Total S/H cell ratio)")) +
  scale_x_continuous(name="Days in the experiment",
                         limits = c(75,113),
                         breaks = seq(75, 110, 15),  
                         expand = c(0, 0))  +
  theme(legend.position = c(.80, 0.24))+
    annotate("text", x = 78, y = -5, label = "(C)", size=3, colour="gray")+
    annotate("text", x = 100, y = -5, label = "(H)", size=3, colour="gray")
Treatment

#ggsave(file="Outputs/TotSH_Community.svg", plot=Treatment, width=4.5, height=3.5)
```

```{r}


LM_Ssid.qpCR<-lmer(logSH ~ Treatment * DaysF * Community + (1|Replicate) + (1|Genotype/Fragment), 
                   data= qPCR.variables_3)
    step(LM_Ssid.qpCR)
    anova(LM_Ssid.qpCR)
    ranova(LM_Ssid.qpCR)

LM_Ssid.qpCR<-lmer(logSH ~ Treatment + DaysF + Community + 
                     (1 | Replicate) + (1 | Genotype) + 
                     Treatment:DaysF + DaysF:Community, data= qPCR.variables_3)
      step(LM_Ssid.qpCR)
      anova(LM_Ssid.qpCR)
      ranova(LM_Ssid.qpCR)
      summary(LM_Ssid.qpCR)
```

```{r}
# Emmeans
Ssid.YII.emm<-emmeans(LM_Ssid.qpCR, ~Treatment*DaysF*Community)
     #contrast(Ssid.YII.emm, "tukey")

# Pairwise comparisons
    #pairs(Ssid.YII.emm) # same than contrast(Ssid.YII.emm, "tukey")
  plot(emmeans(LM_Ssid.qpCR, ~Treatment|DaysF), comparisons = TRUE) +
        theme_bw() # Tukey comparission (do not trust CI to compare EMMs)
    
    plot(emmeans(LM_Ssid.qpCR, ~Treatment|DaysF|Community), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + facet_grid(Community~DaysF) +
      theme_bw()
  
  #CLD  
  SH_Multicomp<-cld(Ssid.YII.emm, by=NULL) # compact-letter display
      SH_Multicomp<-SH_Multicomp[order(SH_Multicomp$DaysF, 
                                       SH_Multicomp$Community,
                                       SH_Multicomp$Treatment), ]
    #write.csv(SH_Multicomp, "Outputs/Ssid_SH_Multicomp.csv")  

```


```{r}
 # 2. Predict values:
    pred_Ssid1 <- predict(LM_Ssid.qpCR, re.form = NA)

  #3. Bootstrap CI:
    Ss.boot1 <- bootMer(LM_Ssid.qpCR, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(Ss.boot1$t, 2, sd)
    CI.lo_1 <- pred_Ssid1 - std.err*1.96
    CI.hi_1 <- pred_Ssid1 + std.err*1.96

  #Plot
  Model_Ss_1b_plot<- ggplot(
    qPCR.variables_3, aes(x = Days, y = logSH, colour = Treatment)) +
    geom_line(aes(y = pred_Ssid1),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_1, ymax = CI.hi_1),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    #scale_y_continuous(name=expression(~italic("Fv / Fm")),
    #                   limits = c(0.5, 0.61), 
    #                   breaks = seq(0.4, 0.6, by=0.1), expand = c(0,0))+
    #scale_x_continuous("Days in the experiment", limits = c(0, 78),
    #                 breaks = seq(0, 76, by=7), expand = c(0,0))+
    
     stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="line", position = position_dodge(1), 
                  linetype=1, alpha=1)+
    # stat_summary(fun.y=mean, geom="point", size =1,
    #             position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw
  
  Model_Ss_1b_plot + facet_wrap(~Community)

```


* Days as continous

```{r}
    
LM_Ssid.qpCR2<-lmer(logSH ~ Treatment * Days * Community + (1|Replicate) + (1|Genotype/Fragment), 
                   data= qPCR.variables_2)
    step(LM_Ssid.qpCR2)
    anova(LM_Ssid.qpCR2)
    ranova(LM_Ssid.qpCR2)

LM_Ssid.qpCR2<-lmer(logSH ~Treatment + Days + Community + (1|Genotype) + Treatment:Days,
                   data= qPCR.variables_2)
      step(LM_Ssid.qpCR2)
      anova(LM_Ssid.qpCR2)
      ranova(LM_Ssid.qpCR2)
      summary(LM_Ssid.qpCR2)
    
```

```{r}
 # 2. Predict values:
    pred_Ssid1 <- predict(LM_Ssid.qpCR2,re.form = NA)

  #3. Bootstrap CI:
    Ss.boot1 <- bootMer(LM_Ssid.qpCR2, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(Ss.boot1$t, 2, sd)
    CI.lo_1 <- pred_Ssid1 - std.err*1.96
    CI.hi_1 <- pred_Ssid1 + std.err*1.96

  #Plot
  Model_Ss_1b_plot<- ggplot(
    qPCR.variables_2, aes(x = Days, y = logSH, colour = Treatment)) +
    geom_line(aes(y = pred_Ssid1),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_1, ymax = CI.hi_1),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    #scale_y_continuous(name=expression(~italic("Fv / Fm")),
    #                   limits = c(0.5, 0.61), 
    #                   breaks = seq(0.4, 0.6, by=0.1), expand = c(0,0))+
    #scale_x_continuous("Days in the experiment", limits = c(0, 78),
    #                 breaks = seq(0, 76, by=7), expand = c(0,0))+
    
     stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="line", position = position_dodge(1), 
                  linetype=1, alpha=1) + 
    # stat_summary(fun.y=mean, geom="point", size =1,
    #             position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw
  
  Model_Ss_1b_plot + facet_wrap(Genotype~Community)

```
