---
title: "Survivorship of Acer genotypes under nutrient and heat stress"
author: "Ana Palacio"
date: "Nov 18, 2019"
output:
  html_document:
    fig_height: 7
    fig_width: 5
    df_print: paged
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

# General project set-up 

```{r libraries, results="hide"}

# Load all libraries and sources required to run the script
    library(tidyverse)
    library(ggthemes)
    library(survival)
    library(survminer)
    #library(rms)
   
# Default ggplot settings
  # Nutrient treatment colors
  Fill.colour<-c ("#4A6CAA", "#469B53", "#AA4A74")
  
  ggthe_bw<-theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black")
          )+
    theme_bw()
  
```

Try survival package

```{r}
# Data
    Survival.data<-read.csv("Data/Acer_Mortality.csv", header = TRUE)
    summary(Survival.data)
    summary(Survival.data$Genotype)
    Survival.data$Genotype<-factor(Survival.data$Genotype, 
                                   levels=c("G_48", "G_62","G_31", "G_08","G_07", "G_50"))
    #Survival.data$Treatment<-factor(Survival.data$Treatment, 
    #                               levels=c("N", "N_P","Ambient"))
    summary(Survival.data$Treatment)
```

# 1. All data models

```{r}
## Add survival object (Fit survival data using the Kaplan-Meier method)
  surv_object <- Surv(time = Survival.data$Fu.time_texp, event = Survival.data$Fu.stat_exp)
  surv_object 

```


## Treatment only: This model pools all the genotyes and replicates per treatment

```{r}
# Only treatment model

    # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit1 <- survfit(surv_object ~ Treatment, data = Survival.data)
    summary(fit1)
    #coxfit <- coxph(surv_object ~ Treatment, data = Survival.data, ties = 'exact')
    #coxfit <- coxph(surv_object ~ Treatment, data = Survival.data, singular.ok = TRUE)
    #summary(coxfit)

    # Plot the survival model
    Ac_Treatment_Only<-ggsurvplot(fit1, data = Survival.data, pval = TRUE, 
           conf.int = T, risk.table=T, palette=Fill.colour,
           break.time.by=15, xlim=c(0,115), risk.table.y.text = FALSE,
           risk.table.title="Number of fragments at risk") + ggtitle("Treatment (all genotypes)")
    Ac_Treatment_Only
```

## Genotype and treatment

Model

```{r}
# Treatment and genotype model 1 
    # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit2 <- survfit(surv_object ~ Genotype + Treatment, data = Survival.data)
    summary(fit2)
```

Cox hazards 

```{r}
 coxfit2 <- coxph(surv_object ~ Genotype + Treatment, data = Survival.data)
    summary(coxfit2)
    coxfit2

```

* “z” gives the Wald statistic value. It corresponds to the ratio of each regression coefficient to its standard error (z = coef/se(coef)). The wald statistic evaluates, whether the beta (β) coefficient of a given variable is statistically significantly different from 0.

* The regression coefficients is the the sign of the regression coefficients (coef). A positive sign means that the hazard (risk of death) is higher, and thus the prognosis worse, for subjects with higher values of that variable. The variable sex is encoded as a numeric vector. 1: male, 2: female. The R summary for the Cox model gives the hazard ratio (HR) for the second group relative to the first group.

* Hazard ratios. The exponentiated coefficients (exp(coef)), also known as hazard ratios, give the effect size of covariates. Confidence intervals of the hazard ratios. The summary output also gives upper and lower 95% confidence intervals for the hazard ratio (exp(coef))

* Global statistical significance of the model. p-values for three alternative tests for overall significance of the model: The likelihood-ratio test, Wald test, and score logrank statistics. These three methods are asymptotically equivalent. For large enough N, they will give similar results. For small N, they may differ somewhat. The Likelihood ratio test has better behavior for small sample sizes, so it is generally preferred.

```{r}

# Test for the proportional-hazards (PH) assumption
    test.ph <- cox.zph(coxfit2)
    test.ph
    # the test is not statistically significant for each of the covariates, or the global test.
    # Therefore, we can assume the proportional hazards.
    
    ggcoxzph(test.ph)
    # Systematic departures from a horizontal line are indicative of non-proportional hazard
    
# Testing influential observations
    
    ggcoxdiagnostics(coxfit2, type = "dfbeta",
                 linear.predictions = FALSE, ggtheme = theme_bw())
      #Positive values correspond to individuals that “died too soon” compared to expected survival times.
      #Negative values correspond to individual that “lived too long”.
      #Very large or small values are outliers, which are poorly predicted by the model.
    
    ggcoxdiagnostics(coxfit2, type = "deviance",
                 linear.predictions = FALSE, ggtheme = theme_bw())
    
 # Testing non linearity (for numeric variales)
    #$ggcoxfunctional(Surv(time = Survival.data$Fu.time_texp,
    #                     event = Survival.data$Fu.stat_exp) ~ Day + log(Day) + sqrt(Day),
     #               data = Survival.data)

```

Plor survival models

```{r}
    # Plot the survival model
    GenTre_1<-ggsurvplot(fit2, data = Survival.data, pval = TRUE,
           risk.table=T,  tables.height=0.5)
    #GenTre_1
    
    Ac_facet_T<-ggsurvplot_facet(fit2, data = Survival.data, facet.by="Genotype", 
                  #risk.table=T, tables.height=0.5, 
                  conf.int = T,
                  nrow = 6, alpha=1, 
                  palette=Fill.colour, linetype=1)
    Ac_facet_T
    
    #ggsave("Outputs/Ac_facet_T.svg", Ac_facet_T, width=4, height=7,dpi = 300)
      
    Ac_facet_G<-ggsurvplot_facet(fit2, data = Survival.data, 
                 facet.by="Treatment", 
                 conf.int = T,
                 # risk.table=T, tables.height=0.5, 
                 nrow = 3, alpha=0.5,
                 linetype=1)
    Ac_facet_G
    #ggsave("Outputs/Ac_facet_G.svg", Ac_facet_G, width=4, height=6,dpi = 300)

```


# 2. Only nutrients (N and N+P) data and models

* Corals in A did not experience any mortality, remove this data to compare the different genotypes under elevated nutrients.

* Filter data

```{r}
# Data
    Survival.data2<-Survival.data[(Survival.data$Treatment!="Ambient"),]
    summary(Survival.data2)
    summary(Survival.data2$Genotype)
    Survival.data2$Genotype<-factor(Survival.data2$Genotype, 
                                   levels=c("G_48", "G_62","G_31", "G_08","G_07", "G_50"))
    summary(Survival.data2$Genotype)
    summary(Survival.data2$Treatment)
    Survival.data2$Treatment<-factor(Survival.data2$Treatment, 
                                   levels=c("N", "N_P"))
```

* Object 

```{r}
## Add survival object (Fit survival data using the Kaplan-Meier method)
  surv_object2 <- Surv(time = Survival.data2$Fu.time_texp, 
                       event = Survival.data2$Fu.stat_exp)
  surv_object2 

```

## Genotype model 

* Model

```{r}
# Only genotype model
  
  # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit3 <- survfit(surv_object2 ~ Genotype, data = Survival.data2)
    summary(fit3)
    surv_pvalue(fit3)

```

 * Cox hazards 

```{r}
    coxfit3 <- coxph(surv_object2 ~ Genotype, data = Survival.data2)
    summary(coxfit3)
    coxfit3

```


```{r}

# Test for the proportional-hazards (PH) assumption
    test.ph <- cox.zph(coxfit3)
    test.ph
    # the test is not statistically significant for each of the covariates, or the global test.
    # Therefore, we can assume the proportional hazards.
    
    ggcoxzph(test.ph)
    # Systematic departures from a horizontal line are indicative of non-proportional hazard
    
# Testing influential observations
    
    ggcoxdiagnostics(coxfit3, type = "dfbeta",
                 linear.predictions = FALSE, ggtheme = theme_bw())
      #Positive values correspond to individuals that “died too soon” compared to expected survival times.
      #Negative values correspond to individual that “lived too long”.
      #Very large or small values are outliers, which are poorly predicted by the model.
    
    ggcoxdiagnostics(coxfit3, type = "deviance",
                 linear.predictions = FALSE, ggtheme = theme_bw())
    
 # Testing non linearity (for numeric variales)
    #$ggcoxfunctional(Surv(time = Survival.data$Fu.time_texp,
    #                     event = Survival.data$Fu.stat_exp) ~ Day + log(Day) + sqrt(Day),
     #               data = Survival.data)

```

Plot survival model

```{r}
# Plot the survival model
   Genotype_only2<-ggsurvplot(fit3, data = Survival.data2, pval = TRUE,
               risk.table=T, tables.height=0.4, conf.int = T, n.risk = TRUE,
               #risk.table.y.text = FALSE, 
               break.time.by=15, xlim=c(0,115), 
           risk.table.title="Number of A. cervicornis at risk")
   Genotype_only2
    
    Acer.Nut.Probabilities<-Genotype_only2$data.survplot
    
    #ggsave("Outputs/Fig_2_Surv_Genotype.svg", 
    #       Genotype_only2$plot, width=4.5, height=3.5,dpi = 300)
    #ggsave("Outputs/Fig_2_Surv_Genotype.pdf", print(Genotype_only2),
    #       width=4.5, height=4.5,dpi = 300)

```

Plot Hazard ratio

```{r}
HazardRatio3<-ggforest(fit.coxph3, data = Survival.data2)
HazardRatio3

#ggsave("Outputs/Fig_2b_HazardRatio.svg", HazardRatio3, width=5, height=4,dpi = 300)
```

## Treatment model

Non-significant

```{r}
# Only treatment model
    # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit4 <- survfit(surv_object2 ~ Treatment, data = Survival.data2)
    summary(fit4)
    surv_pvalue(fit4)
    coxfit4 <- coxph(surv_object2 ~ Treatment, data = Survival.data2)
    summary(coxfit4)

    # Plot the survival model
    Treatment_Only<-ggsurvplot(fit4, data = Survival.data2, pval = TRUE, 
           conf.int = T, risk.table=T, palette=Fill.colour)
    Treatment_Only
    
    # Plot the Hazard ratio
    fit.coxph4 <- coxph(surv_object2 ~ Treatment, data = Survival.data2)
    ggforest(fit.coxph4, data = Survival.data2)
    fit.coxph4
```

## Treatment and genotype model

* Model 

```{r}
# Treatment and genotype model 1 
    # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit5 <- survfit(surv_object2 ~ Treatment + Genotype, data = Survival.data2)
    summary(fit5)
    surv_pvalue(fit5)

```

* Cox hazards 
```{r}
coxfit5 <- coxph(surv_object2 ~ Genotype + Treatment, data = Survival.data2)
    summary(coxfit5)
    coxfit5
```

```{r}
# Test for the proportional-hazards (PH) assumption
    test.ph <- cox.zph(coxfit5)
    test.ph
    # the test is not statistically significant for each of the covariates, or the global test.
    # Therefore, we can assume the proportional hazards.
    
    ggcoxzph(test.ph)
    # Systematic departures from a horizontal line are indicative of non-proportional hazard
    
# Testing influential observations
    
    ggcoxdiagnostics(coxfit5, type = "dfbeta",
                 linear.predictions = FALSE, ggtheme = theme_bw())
      #Positive values correspond to individuals that “died too soon” compared to expected survival times.
      #Negative values correspond to individual that “lived too long”.
      #Very large or small values are outliers, which are poorly predicted by the model.
    
    ggcoxdiagnostics(coxfit2, type = "deviance",
                 linear.predictions = FALSE, ggtheme = theme_bw())
    
 # Testing non linearity (for numeric variales)
    #$ggcoxfunctional(Surv(time = Survival.data$Fu.time_texp,
    #                     event = Survival.data$Fu.stat_exp) ~ Day + log(Day) + sqrt(Day),
     #               data = Survival.data)
```

Plot the model 

```{r}
    
  # Plot the survival model
  GenTre_5<-ggsurvplot(fit5, data = Survival.data2, pval = TRUE, conf.int = T,
           risk.table=T,  tables.height=0.5)
  #GenTre_5
    
  ggsurvplot_facet(fit5, data = Survival.data2, 
                 facet.by="Genotype", risk.table=T, conf.int = T,
                 tables.height=0.5, nrow = 6, alpha=1,
                 palette=Fill.colour, linetype=1)


  ggsurvplot_facet(fit5, data = Survival.data2, 
                 facet.by="Treatment", risk.table=T, conf.int = T,
                 tables.height=0.5, nrow = 3, alpha=0.5,
                 linetype=1)

```

Plot the hazard ratios 

```{r}
ggforest(coxfit5, data = Survival.data2)

```

