---
title: "Changes in Fv/Fm in elevated nutrients and heat stress (Only *O.fav* and *S.sid*)"
author: "Ana Palacio"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    df_print: paged
    theme: united
bibliography: packages.bib
nocite: '@*'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, fig.width=7, fig.height=7)
```


# General project set-up 

```{r libraries, results="hide"}

# Load libraries and sources required to run the script
    library(tidyverse)
    library(ggthemes)
    library(lmerTest)
    library(emmeans)
    library(multcomp)
    library(effects)

# Default ggplot settings

    Fill.colour<-scale_colour_manual(values = c("black", "gray70", "gray35"))

    ggthe_bw<-theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black")
          )+
    theme_bw()
```

# Data

```{r}
# Subset data 
      YII.Ofav<-subset(YII.data, Spp=="Of")
      YII.Ssid<-subset(YII.data, Spp=="Ss")
```

# Figure S4 (Only *O.fav* and *S.sid*)

### Raw data 

```{r Figure, fig.height =6, fig.width = 8}
YII_Treat_OfSs<- ggplot(data=subset(YII.data, Spp!="Ac"), aes (Days, YII, colour=factor(Treatment), shape=factor(Treatment))) + ggtitle("b") +
        ggthe_bw + Fill.colour+
        stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                     position = position_dodge(1) )+
        stat_summary(fun.y=mean, geom="line", position = position_dodge(1), 
                     linetype=1, alpha=1) + 
         stat_summary(fun.y=mean, geom="point", size =1,
                   position=position_dodge(width=1), alpha=0.8)  +
        theme(legend.position=c(0.2, 0.5),
        legend.title = element_blank(), 
        strip.background =element_rect(fill=NA)) + # geom_smooth()+
      
    scale_y_continuous(limits = c(0.1, 0.7),
                           breaks = seq(0.1, 0.6, 0.1),  
                           expand = c(0, 0),
                           name=expression(~italic("Fv / Fm"))) +
        scale_x_continuous(name="Days in the experiment",
                           limits = c(-1,113),
                           breaks = seq(0, 113, 15),  
                           expand = c(0, 0))+
        annotate("segment", x = 2, xend = 91, y = 0.12, yend = 0.12,
                  colour = "gray90", linetype=1)+
        annotate("segment", x = 79, xend = 91, y = 0.12, yend = 0.20,
                  colour = "gray90", linetype=1)+
        annotate("segment", x = 91, xend = 110, y = 0.20, yend = 0.20,
                  colour = "gray90", linetype=1)
        
      
      FigureS4<-YII_Treat_OfSs + #facet_grid (Spp~.)+
        annotate("text", x = 45, y = 0.15, label = "Nutrients", size=3)+
        annotate("text", x = 99, y = 0.15, label = "Heat", size=3)
    FigureS4+facet_wrap(InitialCommunity~Spp)

```

### Smoothed data 

```{r}
YII_Treat_Spp_Sym<- ggplot(data=subset(YII.data), aes (Days, YII, colour=factor(Treatment))) +
         ggthe_bw + Fill.colour + geom_smooth()+
  #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
  #                  position = position_dodge(1) )+
  #stat_summary(fun.y=mean, geom="line", position = position_dodge(1), linetype=1, alpha=1) + 
  #stat_summary(fun.y=mean, geom="point", size =1,
  #                 position=position_dodge(width=1), alpha=0.8)  +
  theme(legend.position="bottom", 
              legend.title = element_blank(),
              strip.background = element_rect(fill="white"))+
  scale_y_continuous(limits = c(0.2, 0.65),
                           breaks = seq(0.1, 0.6, 0.1),  
                           expand = c(0, 0),
                           name=expression(~italic("Fv / Fm"))) +
  scale_x_continuous(name="Days in the experiment",
                           limits = c(-1,113),
                           breaks = seq(0, 113, 15),  
                           expand = c(0, 0))+
  annotate("segment", x = 2, xend = 91, y = 0.21, yend = 0.21,
                  colour = "gray90", linetype=2)+
  annotate("segment", x = 79, xend = 91, y = 0.21, yend = 0.28,
                  colour = "gray90", linetype=4)+
  annotate("segment", x = 91, xend = 110, y = 0.28, yend = 0.28,
                  colour = "gray90", linetype=3)

        
FigureS4b<-YII_Treat_Spp_Sym + facet_wrap (InitialCommunity~Spp)+
        annotate("text", x = 45, y = 0.25, label = "Nutrients", size=3)+
        annotate("text", x = 99, y = 0.25, label = "Heat", size=3)
FigureS4b

#ggsave(file="Outputs/Fig_S4_Ofav-Ssid_YII_Treatb.svg", plot=FigureS4b, width=7, height=6)
```

```{r}
YII_Treat_Sym_Spp<- ggplot(data=subset(YII.data), aes (Days, YII, colour=factor(InitialCommunity))) +
         ggthe_bw + geom_smooth()+
  #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
  #                  position = position_dodge(1) )+
  #stat_summary(fun.y=mean, geom="line", position = position_dodge(1), linetype=1, alpha=1) + 
  #stat_summary(fun.y=mean, geom="point", size =1,
  #                 position=position_dodge(width=1), alpha=0.8)  +
  theme(legend.position="bottom", 
              legend.title = element_blank(),
              strip.background = element_rect(fill="white"))+
  scale_y_continuous(limits = c(0.2, 0.7),
                           breaks = seq(0.1, 0.65, 0.1),  
                           expand = c(0, 0),
                           name=expression(~italic("Fv / Fm"))) +
  scale_x_continuous(name="Days in the experiment",
                           limits = c(-1,113),
                           breaks = seq(0, 113, 15),  
                           expand = c(0, 0))+
  annotate("segment", x = 2, xend = 91, y = 0.21, yend = 0.21,
                  colour = "gray90", linetype=2)+
  annotate("segment", x = 79, xend = 91, y = 0.21, yend = 0.28,
                  colour = "gray90", linetype=4)+
  annotate("segment", x = 91, xend = 110, y = 0.28, yend = 0.28,
                  colour = "gray90", linetype=3)

        
FigureS4c<-YII_Treat_Sym_Spp + facet_grid (Spp~Treatment)+
        annotate("text", x = 45, y = 0.25, label = "Nutrients", size=3)+
        annotate("text", x = 99, y = 0.25, label = "Heat", size=3)
FigureS4c

```

# YII GLMs

Prepare data sets: 

* Time as discrete


```{r Acer_models}
#Time as a factor, not as int
      str(YII.data)
      YII.data$DaysF<-as.factor(YII.data$Days)
```
  
* Separate coral species

* Separate phases:  
    * BaseLine
    * C (nutrients only)
    * H (Heat challenge)

Ofav: 

```{r Ofav_data}

YII.Ofav<-subset(YII.data, Spp=="Of")

YII.Ofav.0<-subset(YII.Ofav, Days<2)
YII.Ofav.C<-subset(YII.Ofav, Days<77)
YII.Ofav.C.1<-subset(YII.Ofav.C, Days>2)
YII.Ofav.H<-subset(YII.Ofav, Days>75)

```

Ssid 

```{r Ssid_data}

YII.Ssid<-subset(YII.data, Spp=="Ss")

YII.Ssid.0<-subset(YII.Ssid, Days<2)
YII.Ssid.C<-subset(YII.Ssid, Days<77)
YII.Ssid.C.1<-subset(YII.Ssid.C, Days>2)
YII.Ssid.H<-subset(YII.Ssid, Days>75)

```


## Baseline: effect of different Symbiodiniaceae taxa before treatments

### Ofav (day 0)

```{R}

LME_Ofav0<-lmer(YII ~ Treatment + InitialCommunity + (1|Replicate), 
                     data=YII.Ofav.0)
     #step (LME_Ofav0) 
     anova(LME_Ofav0) # Treatment not significant        
     ranova(LME_Ofav0) #  Replicate is not significant         
     

LME_Ofav0<-lm(YII ~ InitialCommunity, data=YII.Ofav.0)
     step (LME_Ofav0) 
     anova(LME_Ofav0)         

# EMMs
    Ofav.YII.emm0<-emmeans(LME_Ofav0, ~ InitialCommunity)
      # contrast(Ssid.YII.emm, "tukey")
      
      # Tukey comparison (do not trust CI to compare EMMs)
      plot(emmeans(LME_Ofav0, ~InitialCommunity), comparisons = TRUE) +
        coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) +
        theme_bw()
      
      Ofav.YII_groups0<-cld(Ofav.YII.emm0, by=NULL) # compact-letter display
      Ofav.YII_groups0
      # write.csv(Ofav.YII_groups0, "Outputs/Multicomp_OfavYII0.csv", row.names = F)

```


### Ssid (day 0)

```{R}

LME_Ssid0<-lmer(YII ~ Treatment + InitialCommunity + (1|Replicate), 
                     data=YII.Ssid.0)
     step (LME_Ssid0) #  Treatemnt and replicate are significant :/
     anova(LME_Ssid0)         
     ranova(LME_Ssid0)         
     

# EMMs
      Ssid.YII.emm0<-emmeans(LME_Ssid0, ~ InitialCommunity)
      # contrast(Ssid.YII.emm, "tukey")
      
      # Tukey comparison (do not trust CI to compare EMMs)
      plot(emmeans(LME_Ssid0, ~InitialCommunity), comparisons = TRUE) +
        coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) +
        theme_bw()
      
      Ssid.YII_groups0<-cld(Ssid.YII.emm0, by=NULL) # compact-letter display
      Ssid.YII_groups0
      # write.csv(Ssid.YII_groups0, "Outputs/Multicomp_SsidYII0.csv", row.names = F)

```


## C: Effect of nutrient treatments at control temperature

### Ofav

* C Days pooled (days 8-76)

```{r}
LME_Ofav1.1<-lmer(YII ~ Treatment * InitialCommunity + (1|Fragment), 
                     data=YII.Ofav.C.1)
     step (LME_Ofav1.1) #  Replicate is significant
     anova(LME_Ofav1.1)         
     ranova(LME_Ofav1.1)         
     
# EMMs
    Ofav.YII.emm1.1<-emmeans(LME_Ofav1.1, ~ InitialCommunity|Treatment)
    # contrast(Ssid.YII.emm, "tukey")
      
    # Tukey comparison (do not trust CI to compare EMMs)
      plot(emmeans(LME_Ofav1.1, ~Treatment|InitialCommunity), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + facet_grid(~InitialCommunity) +
        theme_bw()
      
      Ofav.YII.emm1.1<-cld(Ofav.YII.emm1.1, by=NULL) # compact-letter display
      Ofav.YII.emm1.1
      #write.csv(Ofav.YII.emm1.1, "Outputs/Multicomp_OfavYII1.csv", row.names = F)

```

* Model for "Days" as continous variable (days 1-76)

```{r Ofav_models}
 
# 1. Ofav- Days 
      LME_Ofav<-lmer(YII ~ Treatment * Days * InitialCommunity +
                       (1|Genotype) + (1|Fragment) +(1|Replicate), 
                        data=YII.Ofav.C, na.action=na.omit)
      lmerTest::step (LME_Ofav) # Replicate is not significant
      ranova(LME_Ofav)
      
      LME_Ofav1<-lmer(YII ~ Treatment * Days * InitialCommunity + 
                        (1 | Genotype/Fragment),
                      data=YII.Ofav.C, na.action=na.omit)
      lmerTest::step (LME_Ofav1)
      
      
# 2. Predict values:
    pred_Ofav1 <- predict(LME_Ofav1,re.form = NA)

  #3. Bootstrap CI:
    OF.boot1 <- bootMer(LME_Ofav1, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(OF.boot1$t, 2, sd)
    CI.lo_1 <- pred_Ofav1 - std.err*1.96
    CI.hi_1 <- pred_Ofav1 + std.err*1.96

  #Plot
  Model_of_1b_plot<- ggplot(
    YII.Ofav.C, aes(x = Days, y = YII, colour = Treatment)) +
    geom_line(aes(y = pred_Ofav1),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_1, ymax = CI.hi_1),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    scale_y_continuous(name=expression(~italic("Fv / Fm")),
                      limits = c(0.35, 0.61), 
                      breaks = seq(0.4, 0.6, by=0.1), expand = c(0,0))+
    scale_x_continuous("Days in the experiment", limits = c(0, 78),
                     breaks = seq(0, 76, by=7), expand = c(0,0))+
    
     stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="line", position = position_dodge(1), 
                linetype=1, alpha=0.5) + 

    # stat_summary(fun.y=mean, geom="point", size =1,
    #             position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw
  
  Model_of_1b_plot + facet_grid(~InitialCommunity)
  
```

* Model for "Days" as factor 

```{r}
# 1. Ofav- Days 
      LME_Ofav<-lmer(YII ~ Treatment * DaysF * InitialCommunity +
                       (1|Genotype) + (1|Fragment) +(1|Replicate), 
                        data=YII.Ofav.C, na.action=na.omit)
      lmerTest::step (LME_Ofav) # Replicate is not significant
      ranova(LME_Ofav)
      
      LME_Ofav1.2<-lmer(YII ~ Treatment * DaysF * InitialCommunity + 
                        (1|Fragment),
                      data=YII.Ofav.C, na.action=na.omit)
      lmerTest::step (LME_Ofav1.2)
      
      
  # 2. Predict values:
    pred_Ofav1.2 <- predict(LME_Ofav1.2,re.form = NA)

  #3. Bootstrap CI:
    OF.boot1.2 <- bootMer(LME_Ofav1.2, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(OF.boot1.2$t, 2, sd)
    CI.lo_1 <- pred_Ofav1.2 - std.err*1.96
    CI.hi_1 <- pred_Ofav1.2 + std.err*1.96

  #Plot
  Model_of_1.2_plot<- ggplot(
    YII.Ofav.C, aes(x = Days, y = YII, colour = Treatment)) +
    geom_line(aes(y = pred_Ofav1.2),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_1, ymax = CI.hi_1),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    scale_y_continuous(name=expression(~italic("Fv / Fm")),
                       limits = c(0.35, 0.61), 
                       breaks = seq(0.4, 0.6, by=0.1), expand = c(0,0))+
    scale_x_continuous("Days in the experiment", limits = c(0, 78),
                     breaks = seq(0, 76, by=7), expand = c(0,0))+
    
     stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
      stat_summary(fun.y=mean, geom="point", size =1,
                   position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw
  
  Model_of_1.2_plot + facet_grid(~InitialCommunity)
  
  # EMMs
    Ofav.YII.emmC<-emmeans(LME_Ofav1.2, ~Treatment * DaysF * InitialCommunity)
    #contrast(Ofav.YII.emm, "tukey")
      
      
      # Ofav.YII_groupsC<-cld(Ofav.YII.emmC, by=NULL) # compact-letter display
      # Ofav.YII_groupsC<-Ofav.YII_groupsC[order(
      #   Ofav.YII_groupsC$Days,
      #   Ofav.YII_groupsC$Treatment,
      #   Ofav.YII_groupsC$InitialCommunity),]
      # Ofav.YII_groupsC
      # write.csv(Ofav.YII_groupsC, "Outputs/Multicomp_OfavYIIC.csv", row.names = F)
```

### Ssid

* Days pooled (8-76 Days)

```{r}
LME_Ssid1.1<-lmer(YII ~ Treatment * InitialCommunity + (1|Fragment), 
                     data=YII.Ssid.C.1)
     step (LME_Ssid1.1) #  Replicate is significant
     anova(LME_Ssid1.1)         
     ranova(LME_Ssid1.1)         
     
# EMMs
    Ssid.YII.emm1.1<-emmeans(LME_Ssid1.1, ~ InitialCommunity|Treatment)
    # contrast(Ssid.YII.emm, "tukey")
      
    # Tukey comparison (do not trust CI to compare EMMs)
      plot(emmeans(LME_Ssid1.1, ~Treatment|InitialCommunity), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + facet_grid(~InitialCommunity)+
        theme_bw()
      
      Ssid.YII.Groups1.1<-cld(Ssid.YII.emm1.1, by=NULL) # compact-letter display
      Ssid.YII.Groups1.1<- Ssid.YII.Groups1.1[order(
        Ssid.YII.Groups1.1$InitialCommunity, 
        Ssid.YII.Groups1.1$Treatment),]
      Ssid.YII.Groups1.1
     #write.csv( Ssid.YII.Groups1.1, "Outputs/Multicomp_SsidYII1.1.csv", row.names = F)

```


* Model for "Days" as continous variable (days 1-76)

```{r}
LME_Ssid<-lmer(YII ~ Treatment * Days * InitialCommunity +
                       (1|Fragment) +(1|Replicate), 
                     data=subset(YII.Ssid.C))
     step (LME_Ssid) #  Replicate is not significant
     anova(LME_Ssid)         
     ranova(LME_Ssid)         
     
LME_Ssid1<-lmer(YII ~ Treatment * Days * InitialCommunity +
                       (1|Fragment),
                     data=YII.Ssid.C, na.action=na.omit)


# EMMs
      Ssid.YII.emm1<-emmeans(LME_Ssid1, ~Treatment * Days * InitialCommunity)
      # contrast(Ssid.YII.emm, "tukey")
      
      # Effect plot options
      emmip(LME_Ssid1, ~InitialCommunity|Treatment, CIs = TRUE) + theme_bw() # interaction plot of predictions

```

```{r}
# 2. Predict values:
    predSs1 <- predict(LME_Ssid1,re.form = NA)

# 3. Bootstrap CI:
    boot1Ss <- bootMer(LME_Ssid1, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(boot1Ss$t, 2, sd)
    CI.lo_1 <- predSs1 - std.err*1.96
    CI.hi_1 <- predSs1 + std.err*1.96
```

<<<<<<< HEAD
```{R, fig.height = 6, fig.width = 8}
# 4. Plot
  Model1Ss_plot<- ggplot(
    YII.Ssid.C, aes(x = Days, y = YII, colour = Treatment)) +
    geom_line(aes(y = predSs1),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.5) +
    geom_ribbon(aes(ymin = CI.lo_1, ymax = CI.hi_1),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    scale_y_continuous(name=expression(~italic("Fv / Fm")),
                       limits = c(0.3, 0.6), 
                       breaks = seq(0.3, 0.6, by=0.1), expand = c(0,0))+
    scale_x_continuous("Days in the experiment (C phase)", limits = c(0, 78),
                     breaks = seq(0, 76, by=7), expand = c(0,0))+
    
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="line", position = position_dodge(1), 
                   linetype=1, alpha=0.5) + 
    #stat_summary(fun.y=mean, geom="point", size =1,
    #               position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw # + Fill.colour
  
  Model1Ss_plot + facet_grid(~InitialCommunity)
```

* Model for "Days" as factor 

```{r}
# 1. Ssid- Days 
      LME_Ssid<-lmer(YII ~ Treatment * DaysF * InitialCommunity +
                       (1|Genotype) + (1|Fragment) +(1|Replicate), 
                        data=YII.Ssid.C, na.action=na.omit)
      lmerTest::step (LME_Ssid) # Replicate is not significant
      ranova(LME_Ssid)
      
      LME_Ssid1.2<-lmer(YII ~ Treatment * DaysF * InitialCommunity + 
                        (1|Fragment),
                      data=YII.Ssid.C, na.action=na.omit)
      lmerTest::step (LME_Ssid1.2)
```

```{r}
# 2. Predict values:
    pred_Ssid1.2 <- predict(LME_Ssid1.2,re.form = NA)

  #3. Bootstrap CI:
    Ss.boot1.2 <- bootMer(LME_Ssid1.2, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(Ss.boot1.2$t, 2, sd)
    CI.lo_1 <- pred_Ssid1.2 - std.err*1.96
    CI.hi_1 <- pred_Ssid1.2 + std.err*1.96
```

```{r}
# 4. Plot
  Model_Ss_1.2_plot<- ggplot(
    YII.Ssid.C, aes(x = Days, y = YII, colour = Treatment)) +
    geom_line(aes(y = pred_Ssid1.2),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_1, ymax = CI.hi_1),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    scale_y_continuous(name=expression(~italic("Fv / Fm")),
                       limits = c(0.35, 0.6), 
                       breaks = seq(0.4, 0.6, by=0.1), expand = c(0,0))+
    scale_x_continuous("Days in the experiment", limits = c(0, 78),
                     breaks = seq(0, 76, by=7), expand = c(0,0))+
    
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="point", size =1,
                   position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw
  
  Model_Ss_1.2_plot + facet_grid(~InitialCommunity)
```

```{r}
# 5. EMMs
    Ssid.YII.emmC<-emmeans(LME_Ssid1.2, ~Treatment * DaysF * InitialCommunity)
      #contrast(Ssid.YII.emm, "tukey")
      
      
       Ssid.YII_groupsC<-cld(Ssid.YII.emmC, by=NULL) # compact-letter display
       Ssid.YII_groupsC<-Ssid.YII_groupsC[order(
         Ssid.YII_groupsC$DaysF,
         Ssid.YII_groupsC$InitialCommunity,
         Ssid.YII_groupsC$Treatment),]
       Ssid.YII_groupsC
       #write.csv(Ssid.YII_groupsC, "Outputs/Multicomp_SsidYIIC.csv", row.names = F)

```


## H: Effect of pre-exposure to nutrient treatments during heat challenge

### Ofav

* Model for "Days" as continous variable (days 84-110)

```{r}
# 1. Ofav- Days 
      LME_Ofav.H<-lmer(YII ~ Treatment * Days * InitialCommunity +
                       (1|Genotype) + (1|Fragment) +(1|Replicate), 
                        data=YII.Ofav.H, na.action=na.omit)
      lmerTest::step (LME_Ofav.H) # Replicate is not significant
      ranova(LME_Ofav.H)
      
      LME_Ofav.H1<-lmer(YII ~ Treatment * Days + 
                        (1 | Genotype/Fragment),
                      data=YII.Ofav.H, na.action=na.omit)
      lmerTest::step (LME_Ofav.H1)
```

```{r}
# 2. Predict values:
    pred_Ofav.H <- predict(LME_Ofav.H1,re.form = NA)

#3. Bootstrap CI:
    OF.bootH <- bootMer(LME_Ofav.H1, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(OF.bootH$t, 2, sd)
    CI.lo_H <- pred_Ofav.H - std.err*1.96
    CI.hi_H <- pred_Ofav.H + std.err*1.96
```

```{r}
 # 4 .Plot
  Model_of_H_plot<- ggplot(
    YII.Ofav.H, aes(x = Days, y = YII, colour = Treatment)) +
    geom_line(aes(y = pred_Ofav.H),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_H, ymax = CI.hi_H),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    scale_y_continuous(name=expression(~italic("Fv / Fm")),
                       limits = c(0.25, 0.58), 
                       breaks = seq(0.3, 0.5, by=0.1), expand = c(0,0))+
    scale_x_continuous("Days in the experiment (H phase)", limits = c(80, 112),
                     breaks = seq(80, 110, by=7), expand = c(0,0))+
    
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="line", position = position_dodge(1), 
                   linetype=1, alpha=1) + 
    stat_summary(fun.y=mean, geom="point", size =1,
                   position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw
  
  Model_of_H_plot
  Model_of_H_plot+ facet_grid(InitialCommunity~.)
  
```

* Model for "Days" as factor (daysF 84-110)

```{r}
# 1. Ofav- Days 
    LME_Ofav.HF<-lmer(YII ~ Treatment * DaysF * Community +
                       (1|Genotype) + (1|Fragment) +(1|Replicate), 
                        data=YII.Ofav.H, na.action=na.omit)
      lmerTest::step (LME_Ofav.HF) # Replicate is not significant
      ranova(LME_Ofav.HF)
      
      LME_Ofav.HF.1<-lmer(YII ~ Treatment + DaysF + Community + 
                          (1 | Genotype) + (1 | Fragment) +
                          Treatment:DaysF + DaysF:Community,
                      data=YII.Ofav.H, na.action=na.omit)
      lmerTest::step (LME_Ofav.HF.1)
```

```{r}
# 2. Predict values:
    pred_OfavHF <- predict(LME_Ofav.HF.1,re.form = NA)

# 3. Bootstrap CI:
    OF.bootHF <- bootMer(LME_Ofav.HF.1, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(OF.bootHF$t, 2, sd)
    CI.lo_HF <- pred_OfavHF - std.err*1.96
    CI.hi_HF <- pred_OfavHF + std.err*1.96
```

```{r}
# 4. Plot
  Model_of_HF_plot<- ggplot(
    YII.Ofav.H, aes(x = Days, y = YII, colour = Treatment)) +
    geom_line(aes(y = pred_OfavHF),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_HF, ymax = CI.hi_HF),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    scale_y_continuous(name=expression(~italic("Fv / Fm")), 
                       limits = c(0.25, 0.55), 
                       breaks = seq(0.3, 0.5, by=0.1), expand = c(0,0))+
    scale_x_continuous("Days in the experiment (H phase)", limits = c(80, 112),
                     breaks = seq(80, 110, by=7), expand = c(0,0))+
    
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="point", size =1,
                   position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw
  
  Model_of_HF_plot
  Model_of_HF_plot + facet_grid(Community~.)
```

```{r}
# 5. EMMs
      Ofav.YII.emmH<-emmeans(LME_Ofav.HF.1, ~ Treatment:DaysF + DaysF:Community)
      #contrast(Ofav.YII.emmH, "tukey")
      
      Ofav.YII_groupsH<-cld(Ofav.YII.emmH, by=NULL) # compact-letter display
      Ofav.YII_groupsH<-Ofav.YII_groupsH[order(
        Ofav.YII_groupsH$Days,
        Ofav.YII_groupsH$Treatment,
        Ofav.YII_groupsH$Community),]
      Ofav.YII_groupsH
      #write.csv(Ofav.YII_groupsH, "Outputs/Multicomp_OfavYII_H.csv", row.names = F)
```

### Ssid

* Model for "Days" as continous variable (days 84-110)
```{r}
# 1. Ssid- Days 
      LME_Ssid.H<-lmer(YII ~ Treatment * Days * InitialCommunity +
                       (1|Genotype) + (1|Fragment) +(1|Replicate), 
                        data=YII.Ssid.H, na.action=na.omit)
      lmerTest::step (LME_Ssid.H) # Replicate is not significant
      ranova(LME_Ssid.H)
      
      LME_Ssid.H1<-lmer(YII ~ Treatment * Days * InitialCommunity + 
                        (1 | Genotype/Fragment),
                      data=YII.Ssid.H, na.action=na.omit)
      lmerTest::step (LME_Ssid.H1)
      anova(LME_Ssid.H1)
```

```{r}
# 2. Predict values:
    pred_Ssid.H <- predict(LME_Ssid.H1,re.form = NA)

#3. Bootstrap CI:
    Ss.bootH <- bootMer(LME_Ssid.H1, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.errSH <- apply(Ss.bootH$t, 2, sd)
    CI.lo_SH <- pred_Ssid.H - std.errSH*1.96
    CI.hi_SH <- pred_Ssid.H + std.errSH*1.96
```

```{r, fig.height= 6, fig.width = 8}
 # 4 .Plot
  Model_Ss_H_plot<- ggplot(
    YII.Ssid.H, aes(x = Days, y = YII, colour = Treatment)) +
    geom_line(aes(y = pred_Ssid.H),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_SH, ymax = CI.hi_SH),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    scale_y_continuous(name=expression(~italic("Fv / Fm")),
                       limits = c(0.1, 0.58), 
                       breaks = seq(0.1, 0.5, by=0.1), expand = c(0,0))+
    scale_x_continuous("Days in the experiment (H phase)", limits = c(80, 112),
                     breaks = seq(80, 110, by=7), expand = c(0,0))+
    
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    stat_summary(fun.y=mean, geom="line", position = position_dodge(1), 
                   linetype=1, alpha=0.5) + 
    #stat_summary(fun.y=mean, geom="point", size =1,
    #               position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw
  
  Model_Ss_H_plot+ facet_grid(~InitialCommunity)
```

* Model for "Days" as factor (daysF 84-110)

```{r}
# 1. Ssid- Days 
      LME_Ssid.HF<-lmer(YII ~ Treatment * DaysF * InitialCommunity +
                       (1|Genotype) + (1|Fragment) +(1|Replicate), 
                        data=YII.Ssid.H, na.action=na.omit)
      lmerTest::step (LME_Ssid.HF) # Replicate is not significant
      ranova(LME_Ssid.HF)
      
      LME_Ssid.HF.1<-lmer(YII ~ Treatment * DaysF * InitialCommunity + (1 | Fragment),
                      data=YII.Ssid.H, na.action=na.omit)
      lmerTest::step (LME_Ssid.HF.1)
      anova(LME_Ssid.HF.1)
```

```{r}
# 2. Predict values:
    pred_SsidHF <- predict(LME_Ssid.HF.1,re.form = NA)

# 3. Bootstrap CI:
    Ss.bootHF <- bootMer(LME_Ssid.HF.1, predict, nsim = 1000, re.form = NULL) # include random effects, reduce CI lot!
    std.err <- apply(Ss.bootHF$t, 2, sd)
    CI.lo_HF.S <- pred_SsidHF - std.err*1.96
    CI.hi_HF.S <- pred_SsidHF + std.err*1.96
```

```{r}
# 4. Plot
  Model_Ss_HF_plot<- ggplot(
    YII.Ssid.H, aes(x = Days, y = YII, colour = Treatment)) +
    geom_line(aes(y = pred_SsidHF),size=2) +
    #geom_point(aes(fill=factor(Treatment)),
    #         shape = 21, colour = "black", size = 2, stroke = 0.3, alpha=0.3) +
    geom_ribbon(aes(ymin = CI.lo_HF.S, ymax = CI.hi_HF.S),
                size=2, alpha = 0.1, linetype = 0) +
    #scale_color_manual(values=my_colours) +
    #scale_fill_manual(values=my_colours) +
    scale_y_continuous(name=expression(~italic("Fv / Fm")), 
                       limits = c(0.1, 0.55), 
                       breaks = seq(0.1, 0.5, by=0.1), expand = c(0,0))+
    scale_x_continuous("Days in the experiment (H phase)", limits = c(80, 112),
                     breaks = seq(80, 110, by=7), expand = c(0,0))+
    
    stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1,
                   position = position_dodge(1) )+
    #stat_summary(fun.y=mean, geom="point", size =1,
    #               position=position_dodge(width=1), alpha=0.8)  +
    ggthe_bw
  
  Model_Ss_HF_plot + facet_grid(~InitialCommunity)
```

```{r}
# 5. EMMs
    Ssid.YII.emmH<-emmeans(LME_Ssid.HF.1, ~ Treatment*DaysF*InitialCommunity)
      #contrast(Ssid.YII.emmH, "tukey")
      
      Ssid.YII_groupsH<-cld(Ssid.YII.emmH, by=NULL) # compact-letter display
      Ssid.YII_groupsH<-Ssid.YII_groupsH[order(
        Ssid.YII_groupsH$Days,
        Ssid.YII_groupsH$Treatment,
        Ssid.YII_groupsH$InitialCommunity),]
      Ssid.YII_groupsH
      #write.csv(Ssid.YII_groupsH, "Outputs/Multicomp_SsidYIIH.csv", row.names = F)
```

# Packages used

```{r}
# Creates bibliography 
#knitr::write_bib(c(.packages()), "packages.bib")
```
