---
title: "SH cell ratio Ofav_Nutrients"
author: "Ana Palacio"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    df_print: paged
    theme: united
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE,}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

General project set-up 

```{r libraries , results="hide"}
# Get all libraries and sources required to run the script
        library(steponeR)
        library(plyr)
        library(dplyr)
        library(reshape2)
        library(ggplot2)
        library(lme4)
        library(ggthemes)
      
```

## 1. Calculate qPCR RATIOS (Symbiont/Coral) 

Get the raw data for Ofav R.Cunning steponeR function:

* Get list of plate files to read
* Calculate the ratios
* Extract the results

```{r CalculateRatios}

  Ofav.plates <- list.files(path="Data", pattern=".csv", 
                           full.names=TRUE, recursive = TRUE)
  # Ofav.plates

  # Run stepone function to get Ratios
  
  Ofav.Out <- steponeR(files=Ofav.plates, target.ratios=c("B.Ofav", "C.Ofav", "D.Ofav"), 
                       fluor.norm=list(B=1, C=5.1, D=1, Ofav=0),
                       copy.number=list(B=1, C=23, D=3, Ofav=1),
                       ploidy=list(B=1, C=1, D=1, Ofav=2),
                       extract=list(B=0.813, C=0.813, D=0.813, Ofav=0.982))
  
  # Target ratio results
  Ofav<-Ofav.Out$result
  
```

## 2. Data CLEANING A

```{r DataCleaning}
  # 1. Check and remove NTC wells
    ntc <- Ofav[which(Ofav$Sample.Name=="NTC"|Ofav$Sample.Name=="-"), ]
    Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(ntc), ])
    
  # 2. Check and remove + Control wells
    Positive <- Ofav[which(Ofav$Sample.Name=="+"), ]
    Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(Positive), ])
    
  # 3. Create unique sample ID+FileName to relabel samples  
    Ofav$Sample.Plate<-paste(Ofav$Sample.Name,Ofav$File.Name, sep="_")

  # 4.If Clade only detected in one technical replicate, set its ratio to NA ann make them =0
    #One.B<- Ofav[which(Ofav$B.reps==1),]
    Ofav$B.Ofav[which(Ofav$B.reps==1)] <- NA
    
    #One.C<- Ofav[which(Ofav$C.reps==1),]
    Ofav$C.Ofav[which(Ofav$C.reps==1)] <- NA
    
    #One.D<- Ofav[which(Ofav$D.reps==1),]
    Ofav$D.Ofav[which(Ofav$D.reps==1)] <- NA
    
    Ofav$B.Ofav[is.na(Ofav$B.Ofav)] <- 0
    Ofav$C.Ofav[is.na(Ofav$C.Ofav)] <- 0
    Ofav$D.Ofav[is.na(Ofav$D.Ofav)] <- 0

```
    
## 3. Get the cell ratios and log 10 transformations

```{r}
    # Total SH
    Ofav$TotalSH<-(Ofav$B.Ofav + Ofav$C.Ofav + Ofav$D.Ofav)
    
    # Log 10
        Ofav$logB.SH <- log10(Ofav$B.Ofav)
        Ofav$logC.SH <- log10(Ofav$C.Ofav)
        Ofav$logD.SH <- log10(Ofav$D.Ofav)
        Ofav$logSH<-log10(Ofav$TotalSH)
        
        Ofav$logB.SH[which(Ofav$B.Ofav==0)] <- NA
        Ofav$logC.SH[which(Ofav$C.Ofav==0)] <- NA
        Ofav$logD.SH[which(Ofav$D.Ofav==0)] <- NA
  
```    


## 4. Import the sample information

```{r Samples}
# Get the sample informaton 
  SampleName<-read.csv("Sample_Plates.csv")

# Create unique sample ID+FileName to relabel samples  
   Ofav$Sample.Plate<-paste(Ofav$Sample.Name, Ofav$File.Name, sep="_")
   
# Replace Sample.Names in qPCR data 

rownames(SampleName) <- SampleName$Sample_Plate
    Ofav$Treatment<-SampleName[as.character(Ofav$Sample.Plate), "Treatment"]
    Ofav$Replicate<-SampleName[as.character(Ofav$Sample.Plate), "Rep"]
    Ofav$Colony<-SampleName[as.character(Ofav$Sample.Plate), "Colony"]
        Ofav$Genotype<-paste("Of", Ofav$Colony, sep = "_" )    
    Ofav$Core<-SampleName[as.character(Ofav$Sample.Plate), "Core"]
        Ofav$Fragment<-paste("Of", Ofav$Core, sep = "_" )
    Ofav$Date<-SampleName[as.character(Ofav$Sample.Plate), "Date"]
          Ofav$Date<-as.Date(Ofav$Date, format="%Y-%m-%d")
          Ofav$Days<-as.numeric(Ofav$Date -17485)

          
# Get timePoint inf
  TimePoints<-read.csv("Time_Points.csv") 
  TimePoints$Date<-as.Date(TimePoints$Date, format="%m/%d/%y")
  Ofav<-left_join(Ofav, TimePoints, by = "Date")
# Creates a unique ID for a core-sampling time 
          

Ofav$Sample<-paste(Ofav$Fragment, Ofav$Time_Point, sep='_') 
```

## 5. Data CLEANING B

* Fucked up samples

```{r DataCleaningB}

# 5. Remove (-) control
    NegControl <- Ofav[which(Ofav$Sample=="Of_NA_NA"), ]
    Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(NegControl), ])

# 6.If coral detected in one technical replicate, remove the sample
    ReRun.Coral <- Ofav[which(Ofav$Ofav.reps==1), ]
    Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(ReRun.Coral), ])
    
    NoHSratio <- Ofav[which(Ofav$TotalSH==0), ]
    Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(NoHSratio), ])
    
# 7. High ST    
    StDe1.5 <- Ofav[which((Ofav$Ofav.CT.sd>1.6)|(Ofav$B.CT.sd>3.0)|(Ofav$D.CT.sd>2.1)), ]
    Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(StDe1.5), ])
     # ToRe_Run2<-anti_join (StDe1.5, Acer, by=c("Sample.Name", "Time"))
  
# 8.Suspiciusly late coral
    Histo_Ofav_CT<-qplot(Ofav.CT.mean, data=Ofav, binwidth=0.15)
    Histo_Ofav_CT 
  
  LateCoral<-Ofav[which(Ofav$Ofav.CT.mean>28), ]
  Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(LateCoral), ])
  
  HighSH<-Ofav[which(Ofav$logSH>0), ]
  Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(HighSH), ])
  
  # Samples to Re-run    
  ToRe_Run1<-rbind(ReRun.Coral, NoHSratio)
  ToRe_Run1<-rbind(ToRe_Run1, ReRun.Coral)   
  ToRe_Run1<-rbind(ToRe_Run1, StDe1.5)
  ToRe_Run1<-rbind(ToRe_Run1, LateCoral)
  ToRe_Run1<-anti_join (ToRe_Run1, Ofav, by=c("Sample"))

  #write.csv(ToRe_Run1, "ToRe_Run1.csv" )  
```

*  Chose bw samples ran more than once

```{r remove duplicates}

  ReRunA <- Ofav[duplicated(Ofav$Sample),] 
  n_RunA <- data.frame(table(Ofav$Sample))
  colnames(n_RunA)<-c("Sample","RanA")
  Ofav<-join(Ofav, n_RunA, type = "left")
# 
  DuplicatesA <- Ofav[(Ofav$Ran>1),]
  
#write.csv(DuplicatesA, file = 'DuplicatesA.csv')

```

* Remove duplicates

```{r remove duplicates2}
  ToRem1<-read.csv("ToRemoveOldPlates.csv")
  #ToRem2<-read.csv("ToRemoveOldNewPlates.csv")
#     # 10/24/2018
  Ofav<-Ofav[!(Ofav$Sample.Plate %in% ToRem1$Sample.Plate),]
 
# Check for replicates again--should have none
  n_RunB <- data.frame(table(Ofav$Sample))
  colnames(n_RunB)<-c("Sample","RanB")
  Ofav<-join(Ofav, n_RunB, type = "left")

# List of dupplicated samples, should have 0 rows now -->
   DuplicatesB <-Ofav[(Ofav$RanB>1),]
   #write.csv(DuplicatesB, file = 'DuplicatesB.csv')
```

## 6. Calculate genus proportions

```{R Proportions}
  
  # Clade Proportion
  # D Proportion
    Ofav$D.Prp<-(Ofav$D.Ofav/Ofav$TotalSH)
    Ofav$C.Prp<-(Ofav$C.Ofav/Ofav$TotalSH)
    Ofav$B.Prp<-(Ofav$B.Ofav/Ofav$TotalSH)
    
 # Core clasification by clade Proportion 
    Ofav[,Ofav$Community]<-NULL
    
    Ofav$Community[which(Ofav$B.Prp>=0.5)] <- "B"
    Ofav$Community[which(Ofav$C.Prp>=0.5)] <- "C"
    Ofav$Community[which(Ofav$D.Prp>=0.5)] <- "D"
    
  Ofav$Community<-factor(as.character(Ofav$Community), levels=c("B","D"))
  
  summary(Ofav)
  
```

## 7. Check and export S/H cell ratio data!

```{r} 
qPCRsummary<-summary(Ofav)
#capture.output(qPCRsummary, file = "Outputs/qPCRsummary.txt")

Ofav.export<-Ofav %>% select(Treatment, Replicate, Fragment,Genotype,
                             Date, Days, Time_Point, Phase, Sample, 
                             B.Ofav, C.Ofav, D.Ofav, TotalSH, 
                             logB.SH, logC.SH, logD.SH, logSH, 
                             D.Prp, C.Prp, B.Prp, Community)

Ofav.export$Treatment <- as.character(Ofav.export$Treatment)
      Ofav.export$Treatment[Ofav$Treatment == "Control"] <- "A"
      Ofav.export$Treatment[Ofav$Treatment == "NP"] <- "N+P"

Ofav.export$Genotype<-factor(Ofav.export$Genotype, 
                                   levels=c("Of_34", "Of_20", "Of_6", "Of_31"))

Ofav.export<-Ofav.export[order(
        Ofav.export$Date, Ofav.export$Treatment, Ofav.export$Replicate,
        Ofav.export$Genotype, Ofav.export$Fragment),]



# write.csv(Ofav.export, "Outputs/Ofav_SH_cell_ratio.csv", row.names = F)

```

```{r}
Ofav.metadata<-Ofav %>% select(Sample, TotalSH, D.Prp, Community)

# write.csv(Ofav.metadata, "Outputs/Ofav_SH_metadata.csv", row.names = F)
```


## 8. DATA Exploration

* Log SH by fragment

```{r, fig.width=8, fig.height=6}
logSHTreatment <- ggplot(Ofav.export, aes(Date, logSH)) +
  geom_line(aes(colour=Fragment))+geom_point(aes(shape=factor(Community), colour=factor(Community)))+
  # geom_jitter(aes(colour=factor(Replicate))) +
      # stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
      #stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) +
      # stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
      facet_grid(Treatment~Genotype) +
      theme_bw() +
      theme(legend.position = "none" )

logSHTreatment + ylab("Relative log10 (S:H)") + xlab("Treatment") +  
      theme(axis.title.y=element_text(size=12), legend.position="none")

```

* Log B - only colony 31

```{r}
logB_Treatment <- ggplot(subset(Ofav.export, Genotype=Of_31),
                         aes(Date, logB.SH, colour=factor(Fragment))) +
     geom_line()+ 
     #geom_jitter(aes(colour=factor(Replicate))) +
         #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         #stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         theme_gdocs() +  theme(legend.position = "none" )
logB_Treatment

```


* Log D
```{r,fig.width=8, fig.height=6}
logD <- ggplot(Ofav.export, aes(Date, logD.SH, colour=factor(Fragment))) +
     geom_line()    +
     #geom_jitter(aes(colour=factor(Replicate))) +
         #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         #stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Treatment~Genotype) +
         theme_bw()+
        theme(legend.position = "none")  
logD
   
  
logD_Treatment <- ggplot(Ofav.export, aes(Treatment, logD.SH, colour=factor(Treatment))) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Genotype~Date) +
         theme_bw() 
logD_Treatment

```

```{r, }

SHTreatment <- ggplot(Ofav.export, aes(Date, logSH, colour=factor(Treatment))) +
            theme(plot.background=element_blank(), 
            panel.border = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position="bottom",
            strip.background = element_rect(fill="white")) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Genotype~Community) +
         theme_bw() 
SHTreatment


BHTreatment <- ggplot(Ofav.export, aes(Days, logB.SH, colour=factor(Treatment))) +
            theme(plot.background=element_blank(), 
            panel.border = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position="bottom",
            strip.background = element_rect(fill="white")) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar",
                      position=position_dodge(width = 1), width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(~Genotype) +
         theme_bw() 
BHTreatment


CHTreatment <- ggplot(Ofav.export, aes(Days, logC.SH, colour=factor(Treatment))) +
            theme(plot.background=element_blank(), 
            panel.border = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position="bottom",
            strip.background = element_rect(fill="white")) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Genotype~Community) +
         theme_bw() 
CHTreatment


DHTreatment <- ggplot(Ofav.export, aes(Days, logD.SH, colour=factor(Treatment))) +
            theme(plot.background=element_blank(), 
            panel.border = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position="bottom",
            strip.background = element_rect(fill="white")) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",
                      position=position_dodge(width = 1), width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(~Genotype) +
         theme_bw() 
DHTreatment
```

* D proportion

```{r}
D.PTreatment <- ggplot(Ofav.export, aes(Days, D.Prp, colour=Fragment)) + theme_bw() +
            theme(plot.background=element_blank(), 
            panel.border = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position="none",
            strip.background = element_rect(fill="white")) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         geom_line() + 
         annotate("rect", xmin= 2, xmax = 91,
                 ymin = 0, ymax = 0.2, fill="blue", alpha = 0.04)+
          annotate("rect", xmin= 79, xmax = 90,
                 ymin = 0, ymax = 1, fill="orange", alpha = 0.04)+
          annotate("rect", xmin= 90, xmax = 113,
               ymin =  0, ymax = 1, fill="red", alpha = 0.04)+
        scale_y_continuous(breaks = seq(0, 1, 0.3),
                     name=("Durusdinium proportion (D/H)/(S/H)")) +
        scale_x_continuous(name="Days in the experiment",
                           limits = c(-2,113),
                         breaks = seq(0, 110, 45),  
                         expand = c(0, 0)) +
      facet_grid (Treatment~Genotype, labeller = labeller(Colony=c(`31` = "O.fav_31", 
                                    `6` = "O.fav_6",
                                   `20` = "O.fav_20", 
                                    `34` = "O.fav_34")))
  
D.PTreatment
#ggsave(file="Outputs/D.P_Treatment_Colony.svg", plot=D.PTreatment, width=4.0, height=4)

```
