---
title: "Ofav SH Nutrients data analysis"
author: "Ana Palacio"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    df_print: paged
    theme: united
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

# General project set-up 

```{r libraries , results="hide"}

# Get all libraries and sources required to run the script
        library(plyr)
        library(dplyr)
        library(reshape2)
       
        library(ggplot2)
        library(ggthemes)
        library(scales)

        library(lme4)
        library(lmerTest)
        library(emmeans)

# Default ggplot settings

    Fill.colour<-scale_colour_manual(values = c("black", "gray70", "gray35"))

    ggthe_bw<-theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          #legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black")
          )+
    theme_bw()

```

# 1. DATA Exploration

## 1. Select qPCR info and define factors
 

```{r VariablesToUse}

qPCR.variables  <- read.csv("Outputs/Ofav_SH_cell_ratio.csv", header = T)

    qPCR.blastate<-qPCR.variables[((qPCR.variables$Date=="2018-02-05") |
                                     (qPCR.variables$Date=="2018-03-08")), ]
      
    qPCR.variables <- droplevels(qPCR.variables[!rownames(qPCR.variables) %in% rownames(qPCR.blastate), ])  

qPCR.variables<-subset(qPCR.variables, Date!="2017-12-15") # One month in nutrients

# Variable types 
str(qPCR.variables)
  qPCR.variables$Genotype<-factor(qPCR.variables$Genotype, 
                                  levels=c("Of_34", "Of_20", "Of_6", "Of_31"))
  qPCR.variables$DaysF<-as.factor(qPCR.variables$Days)
  qPCR.variables$Date<-as.Date(qPCR.variables$Date)
  
  summary(qPCR.variables)
```  

### 2. Exploratory graphs

* Histograms

```{r Histograms}

ggplot(qPCR.variables, aes(logSH, fill = Treatment , colour = Treatment)) +
 geom_density(alpha = 0.1) + facet_wrap(~Date) + ggthe_bw
  # 
  
```

* Log SH

```{r, fig.width=8, fig.height=6}
logSHColony <- ggplot(qPCR.variables, aes(Days, logSH)) +
  geom_line(aes(colour=Fragment))+geom_point(aes(shape=factor(Community), colour=factor(Community)))+
  # geom_jitter(aes(colour=factor(Replicate))) +
      # stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
      #stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) +
      # stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
      facet_grid(Treatment~Genotype) +
      ggthe_bw +theme(legend.position = "none" )

logSHColony + ylab("Relative log10 (S:H)") + xlab("Treatment") +  
      theme(axis.title.y=element_text(size=12), legend.position="none")

logSHTreatment <- ggplot(qPCR.variables, aes(Treatment, logSH, colour=factor(Treatment))) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Genotype~Date) +
         theme_bw() 
logSHTreatment

logSH_Replicate<- ggplot(qPCR.variables, aes (Days, logSH, 
                                             colour=factor(Replicate))) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5) +
  stat_summary(fun.y=mean, geom="line") + facet_grid (~Treatment) + ggthe_bw
logSH_Replicate 

logSHTreatment <- ggplot (qPCR.variables, aes(Days, logSH, colour=Treatment)) + 
  ggtitle("A.")+
  ggthe_bw +  theme(legend.position="bottom") +
  
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
  #stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
       #            position = position_dodge(width = 1)) +
  stat_summary(fun.y=mean, geom="line", position = position_dodge(width = 5)) + 

  scale_y_continuous(breaks = seq(-2.5, 0, 0.5),
                    expand = c(0,0),
                  name=("log 10 (Total S/H cell ratio")) +
  scale_x_continuous(name="Days in the experiment",
                         limits = c(-2,113),
                         breaks = seq(0, 110, 15),  
                         expand = c(0, 0)) +  
  geom_point(alpha=0.5) +
  
      annotate("segment", x = 2, xend = 91, y = -2.2, yend = -2.2,
                colour = "gray90")+
      annotate("segment", x = 79, xend = 90, y = -2.2, yend = -1.8,
                colour = "gray90")+
      annotate("segment", x = 91, xend = 110, y = -1.8, yend = -1.8,
                colour = "gray90")
    
logSHTreatment
logSHTreatment +facet_wrap (~Genotype)

```

* Log B - only Genotype 31

```{r}
logB_Treatment <- ggplot(subset(qPCR.variables, Genotype=Of_31),
                         aes(Days, logB.SH, colour=factor(Fragment))) +
     geom_line()+ 
     #geom_jitter(aes(colour=factor(Replicate))) +
         #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         #stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         ggthe_bw +  theme(legend.position = "none" )
logB_Treatment + facet_grid(~Treatment)

```


* Log D
```{r,fig.width=8, fig.height=6}
logD <- ggplot(qPCR.variables, aes(Date, logD.SH, colour=factor(Fragment))) +
     geom_line()    +
     #geom_jitter(aes(colour=factor(Replicate))) +
         #stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         #stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Treatment~Genotype) + ggthe_bw +
        theme(legend.position = "none")  
logD
   
  
logD_Treatment <- ggplot(qPCR.variables, aes(Treatment, logD.SH, colour=factor(Treatment))) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Genotype~Date) +
         ggthe_bw 
logD_Treatment

```

```{r }

SHTreatment <- ggplot(qPCR.variables, aes(Date, logSH, colour=factor(Treatment))) +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Genotype~Community) + 
         ggthe_bw + theme(legend.position="bottom")
SHTreatment


BHTreatment <- ggplot(subset(qPCR.variables, Genotype=Of_31), 
                      aes(Days, logB.SH, colour=factor(Treatment))) +
          ggthe_bw +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar",
                      position=position_dodge(width = 1), width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(~Community)
BHTreatment


CHTreatment <- ggplot(qPCR.variables, aes(Days, logC.SH, colour=factor(Treatment))) +
         ggthe_bw +  theme(legend.position="bottom") +
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Genotype~.)
CHTreatment


DHTreatment <- ggplot(qPCR.variables, aes(Days, logD.SH, colour=factor(Treatment))) +
        ggthe_bw +  theme(legend.position="bottom") +  
         #geom_jitter(aes(colour=factor(Replicate))) +
         stat_summary(fun.data = "mean_cl_boot",
                      position=position_dodge(width = 1), width = 0.2)+
         stat_summary(fun.y=mean, geom="line", size =1, alpha=0.5) + 
         facet_grid(Community~Genotype)
DHTreatment
```

* D proportion

```{r}
D.PTreatment <- ggplot(qPCR.variables, aes(Days, D.Prp, colour=Fragment)) +
        ggthe_bw +  theme(legend.position="none") +  
        geom_jitter(aes(colour=factor(Fragment)), alpha=0.5, size=1) +
        geom_line() + facet_grid (Genotype~Treatment) +
  
      annotate("segment", x = 2, xend = 91, y = -0.03, yend = -0.03,
                colour = "gray90", linetype=2)+
        
      annotate("segment", x = 79, xend = 90, y = -0.03, yend = 0.3,
                colour = "gray90",linetype=3)+
    
      annotate("segment", x = 91, xend = 110, y = 0.3, yend = 0.3,
                colour = "gray90", linetype=3)+
      #annotate("text", x = 8, y = 0.08, label = "(BL)", size=3, colour="gray")+
      annotate("text", x = 45, y = 0.1, label = "Nutrients", size=3, colour="gray")+
      annotate("text", x = 99, y = 0.4, label = "Heat", size=3, colour="gray")+  
  

      scale_y_continuous(breaks = seq(0, 1, 0.3),
                         limits = c(-0.035,1),
                     name=("Durusdinium proportion (D/H)/(S/H)")) +
      scale_x_continuous(name="Days in the experiment",
                        limits = c(-2,113),
                         breaks = seq(0, 110, 30),  
                         expand = c(0, 0))
D.PTreatment
#ggsave(file="Outputs/D.P_Treatment_Genotype.svg", plot=D.PTreatment, width=4.5, height=4.5)

```

# 2. Subset data

```{r}
qPCR.variables_2<-subset(qPCR.variables, Days<110)
qPCR.variables_2<-subset(qPCR.variables_2, Genotype!="Of_34")

SH.0<-subset(qPCR.variables_2, Days<2)
SH.C<-subset(qPCR.variables_2, Days<77)
  SH.C<-subset(SH.C, Days>2)
SH.H<-subset(qPCR.variables_2, Days>76)

#qPCR.variables<-subset(qPCR.variables, Sample!="20-30_2018-01-26")
#qPCR.variables_2<-subset(qPCR.variables_2, Sample!="31-25_2018-01-26")
#qPCR.variables_2<-subset(qPCR.variables_2, Sample!="6-81_2017-11-15")
#qPCR.variables_2<-subset(qPCR.variables_2, Sample!="20-50_2017-11-15")

```

## Log S/H graph
```{r}

logSHTreatment <- ggplot (qPCR.variables, aes(Days, logSH, colour=Treatment, shape=Treatment)) + 
  Fill.colour +
  ggthe_bw +  
   theme(plot.background=element_blank(), 
            #panel.border = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position=c(0.1, 0.25),
            #strip.background = element_rect(fill="white"),
            legend.title = element_blank()) +
  
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 2), width = 2 )+
  stat_summary(fun.y=mean, geom="point", size =2, alpha=0.8, 
                  position = position_dodge(width = 2)) +
  stat_summary(fun.y=mean, geom="line", position = position_dodge(width = 2)) + 

   scale_y_continuous(limits = c(-4.6,0),
        breaks = seq(-5, 0.3, 0.5),
                    expand = c(0,0),
                   name=("log10(Relative S/H cell ratio)")) +
      scale_x_continuous(name="Days in the experiment",
                         limits = c(70,114),
                         breaks = seq(0, 110, 15),  
                         expand = c(0.01, 0.01))+
  #geom_point(alpha=0.5) +
   annotate("segment", x = 73, xend = 91, y = -4.5, yend = -4.5,
                  colour = "gray90", linetype=2)+
        annotate("segment", x = 79, xend = 91, y = -4.5, yend = -4,
                  colour = "gray90", linetype=3)+
        annotate("segment", x = 91, xend = 110, y = -4, yend = -4,
                  colour = "gray90", linetype=3)+
        annotate("text", x = 45, y = -4.4, label = "Nutrients", size=3, colour="gray")+
        #annotate("text", x = 3, y = -4.4, label = "BL", size=3,  colour="gray")+
        annotate("text", x = 100, y = -4.4, label = "Heat", size=3, colour="gray")
    
logSHTreatment
logSHTreatmentb<-logSHTreatment +facet_wrap (~Community)
logSHTreatmentb  
  #ggsave(file="5.3A_AH.svg", plot=logSHTreatment, width=3.0, height=6)
  #ggsave(file="5.3A_AH_NoGenotype.svg", plot=logSHTreatment, width=3.2, height=3.4)

```

## S/H graph
```{r}

logSHTreatment <- ggplot (qPCR.variables_2, aes(Days, TotalSH, colour=Treatment, shape=Treatment)) + 
  Fill.colour +
  ggthe_bw +  theme(legend.position="bottom") +
  
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 6), width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
                  position = position_dodge(width = 6)) +
  stat_summary(fun.y=mean, geom="line", position = position_dodge(width = 5)) + 

  scale_y_continuous(breaks = seq(0, 1, 0.5),
                    expand = c(0.1,0.1),
                  name=("log 10 (Total S/H cell ratio")) +
  scale_x_continuous(name="Days in the experiment",
                         limits = c(-2,113),
                         breaks = seq(0, 110, 15),  
                         expand = c(0, 0)) +  
  #geom_point(alpha=0.5) +
  
      annotate("segment", x = 2, xend = 91, y = -0, yend = 0,
                colour = "gray90")+
      annotate("segment", x = 79, xend = 90, y = 0, yend = 0.2,
                colour = "gray90")+
      annotate("segment", x = 91, xend = 110, y = 0.2, yend = 0.2,
                colour = "gray90")
    
logSHTreatment
logSHTreatment +facet_wrap (~Genotype)
  
  # ggsave(file="5.3A_AH.svg", plot=logSHTreatment, width=3.0, height=6)
  # ggsave(file="5.3A_AH_NoGenotype.svg", plot=logSHTreatment, width=3.0, height=5)

```


# 3. GLM models 

## Baseline

```{r}
LME_BaseLine<-lmer(logSH ~ Treatment + Genotype + Community + (1|Replicate), 
                     data=SH.0)
   #step(LME_BaseLine)
   anova(LME_BaseLine)
   ranova(LME_BaseLine)

```

Nothing is significant for baseline S/H

## C: Effect of nutrient treatments at control temperature

```{r}

LME_Ofav.C<-lmer(logSH ~ Treatment + (1|Replicate) + (1|Genotype), 
                     data=SH.C)
     step (LME_Ofav.C) #  Remove replicate
     

LME_Ofav.C1<-lmer(logSH ~ Treatment + (1|Genotype), 
                     data=SH.C)
     step (LME_Ofav.C1)
     anova (LME_Ofav.C1)

```

```{r}

# Multicomp
Ofav.SH.C.emm<-emmeans(LME_Ofav.C1, ~Treatment)
      #contrast(Ofav.SH.C.emm, "tukey")
    Ofav.SH.C_groups<-cld(Ofav.SH.C.emm, by=NULL) # compact-letter display
    Ofav.SH.C_groups
    
# Effect plot
  plot(emmeans(LME_Ofav.C1, ~Treatment), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + theme_bw()
```


```{r}
logSHTreatmentC <- ggplot (SH.C, aes(Treatment, logSH, colour=Treatment, shape=Treatment)) + 
  ggtitle("A.")+ Fill.colour +
  ggthe_bw +  theme(legend.position="bottom") +
  
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
                  position = position_dodge(width = 1)) +
  
  scale_y_continuous(breaks = seq(-2.5, 0, 0.5),
                    expand = c(0.1,0.1),
                  name=("log 10 (Total S/H cell ratio)"))
    
logSHTreatmentC
logSHTreatmentC +facet_wrap (~Genotype)
```


```{r}
logSHTreatmentC <- ggplot (SH.C, aes(Treatment, TotalSH, colour=Treatment, shape=Treatment)) + 
  ggtitle("A.")+ Fill.colour +
  ggthe_bw +  theme(legend.position="bottom") +
  
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", 
                    position = position_dodge(width = 5), width = 0.2 )+
  stat_summary(fun.y=mean, geom="point", size =3, alpha=0.5, 
                  position = position_dodge(width = 1))
  
  #scale_y_continuous(breaks = seq(-2.5, 0, 0.5),
   #                 expand = c(0.1,0.1),
    #              name=("log 10 (Total S/H cell ratio"))
    
logSHTreatmentC
logSHTreatmentC +facet_wrap (~Genotype)
```

## H: Effect of pre-exposure to nutrient treatments during heat challenge

```{r}
LME_Ofav.H<-lmer(logSH ~ Treatment +
                   (1|Replicate) + (1|Genotype), 
                     data=SH.H)
     #step (LME_Ofav.H)
     anova(LME_Ofav.H)
     ranova(LME_Ofav.H)
```

Nothing is significant for Heat S/H

## All phases

```{r}
LM_Ofav.qpCR<-lmer (logSH ~ Treatment * DaysF +
                  (1|Replicate) + (1|Genotype/Fragment),
                  data= qPCR.variables_2)
    step(LM_Ofav.qpCR)


LM_Ofav.qpCR<-lmer(logSH ~ Treatment * DaysF + (1| Genotype),
                       data= qPCR.variables_2)
      step(LM_Ofav.qpCR)
      summary(LM_Ofav.qpCR)
      anova(LM_Ofav.qpCR)
```


```{r}
# Multicomp    
    Ofav.YII.emm<-emmeans(LM_Ofav.qpCR, ~ DaysF|Treatment)
        contrast(Ofav.YII.emm, "tukey")
        # Effect plot options
  
# Plots
emmip(LM_Ofav.qpCR, ~DaysF|Treatment, CIs = TRUE, aes(Genotype=factor(Treatment))) + theme_bw() # interaction plot of predictions

plot(emmeans(LM_Ofav.qpCR, ~Treatment|DaysF), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + facet_wrap(~DaysF) +
      theme_bw()

# CLD    
    Ofav_EMM_SH<-cld(Ofav.YII.emm, by=NULL) # compact-letter display
     Ofav_EMM_SH<-Ofav_EMM_SH[order(Ofav_EMM_SH$Day, Ofav_EMM_SH$Treatment), ]
     Ofav_EMM_SH
  #write.csv(Ofav_EMM_SH, "Outputs/Multicomp_Ofav_SH.csv")  
    
```
